### 2024-05-25 hid2-urban-building-cicd.tex
Initial Overleaf Import

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images

\begin{document}
\title{Enhancing Urban Building Simulations in HiDALGO2 through CI/CD Innovations}
\author{Vincent Chabannes \inst{1}\orcidID{0000-1111-2222-3333} and Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\ 
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\authorrunning{V. Chabannes and C. Prud'homme}

\maketitle

\begin{abstract}
The building sector in the European Union significantly impacts energy consumption and greenhouse gas emissions. The EU's Horizon 2050 initiative sets ambitious goals to reduce these impacts through enhanced building renovation rates. The HiDALGO2 project supports this initiative by developing high-performance computing solutions, specifically through the Urban Building pilot application which utilizes advanced CI/CD methodologies to streamline simulation and deployment across various computational platforms.
\end{abstract}

\section{Introduction}
The building sector accounts for approximately 40\% of final energy consumption and 36\% of greenhouse gas emissions within the European Union. In response, the EU has established ambitious targets under the Horizon 2050 framework to double energy renovation rates over the next decade, highlighting the need for innovative solutions to drive these initiatives forward. The HiDALGO2 project, with its focus on high-performance computing and advanced simulations, is at the forefront of tackling this challenge, particularly through its Urban Building pilot application.

\section{Objectives of the HiDALGO2 Urban Building Pilot}
The Urban Building pilot in HiDALGO2 aims to leverage high-performance computing to enhance urban simulations for better energy management and air quality assessment. This section outlines the specific objectives and expected impacts of the project.

\subsection{Predictive Simulations}
Advanced simulation tools are employed to predict energy consumption, thermal comfort, and indoor air quality across both the building and urban scales. These simulations support detailed analysis at the individual building level and extend to broader urban environments, influencing urban planning and policy-making.

\subsection{Integration with Environmental Models}
Integrating building simulations with urban air pollution models enables the project to assess the environmental impact of building stocks comprehensively. This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness to environmental conditions.

\subsection{Impact and Implementation}
Implementing these objectives will facilitate more informed urban planning decisions, support policy development for energy efficiency, and contribute to reducing urban greenhouse gas emissions. The project also focuses on enhancing the interaction between different environmental models to provide a holistic view of urban ecosystems.

\section{The Role of CI/CD in Urban Building Simulations}
Continuous Integration (CI) and Continuous Deployment (CD) are pivotal in the development and operation of the Urban Building pilot. These practices enable efficient management of complex simulation software, ensuring seamless integration and deployment across various computational infrastructures.

\subsection{Continuous Integration: Ensuring Code Quality and Reliability}
CI practices in HiDALGO2 handle complex dependencies and computational requirements specific to urban building simulations. Key features include automated testing, code quality checks, and automated builds, ensuring that the software remains robust and maintainable.

\subsection{Continuous Deployment: Streamlining Software Delivery}
CD practices are tailored to manage deployment complexities across different HPC environments using containerization through Apptainer. This approach facilitates consistent, reproducible deployments, optimizing performance and resource utilization.

\section{Conclusion}
CI/CD practices in HiDALGO2 are vital for advancing urban building simulations, supporting the EU's energy efficiency goals, and contributing to the reduction of greenhouse gas emissions in the urban sector.

\bibliographystyle{splncs04}
\bibliography{mybib}

\end{document}

### 2024-05-25 hid2-urban-building-cicd.tex
add authors and ack

@@
 \usepackage{graphicx} % for including images
-
+\usepackage[T1]{fontenc}
 \begin{document}
 \title{Enhancing Urban Building Simulations in HiDALGO2 through CI/CD Innovations}
-\author{Vincent Chabannes \inst{1}\orcidID{0000-1111-2222-3333} and Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
+\author{Vincent Chabannes \inst{1}\orcidID{0000-1111-2222-3333} \and
+Javier Cladellas \inst{1}\orcidID{} \and 
+Abdoulaye Diallo \inst{1}\orcidID{} \and
+Maryam Maslek \inst{1}\orcidID{} \and
+Philippe Pinçon \inst{1}\orcidID{} \and
+Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
 \institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\ 
@@
 The EU's Horizon 2050 initiative sets ambitious goals to reduce these impacts through enhanced building renovation rates.
-The HiDALGO2 project supports this initiative by developing high-performance computing solutions, specifically through the Urban Building pilot application which utilizes advanced CI/CD methodologies to streamline simulation and deployment across various computational platforms.
+The HiDALGO2 project supports this initiative by developing high-performance computing solutions, specifically through the Urban Building pilot application, which utilizes advanced CI/CD methodologies to streamline simulation and deployment across various computational platforms.
+\keywords{HPC, Urban building, City Energy Simulation.}
+
 \end{abstract}
@@
 
+\begin{credits}
+\subsubsection{\ackname} d
+
+% \subsubsection{\discintname}
+% It is now necessary to declare any competing interests or to specifically
+% state that the authors have no competing interests. Please place the
+% statement with a bold run-in heading in small font size beneath the
+% (optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
+% system, is used, then the disclaimer can be provided directly in the system.},
+% for example: The authors have no competing interests to declare that are
+% relevant to the content of this article. Or: Author A has received research
+% grants from Company W. Author B has received a speaker honorarium from
+% Company X and owns stock in Company Y. Author C is a member of committee Z.
+\end{credits}
+
 \bibliographystyle{splncs04}

### 2024-05-25 hid2-urban-building-cicd.tex
first draft, need to add figures

@@
 \usepackage[T1]{fontenc}
+\usepackage{subcaption}
+
 \begin{document}
@@
 
+\section{Overview of Urban Building Modeling and Simulation}
+
+\subsection{Geometry Reconstruction of the Urban Model}
+
+The geometric reconstruction of urban environments within the HiDALGO2 project involves a sophisticated approach to creating multi-fidelity representations of buildings, terrain, vegetation, roads, and other urban elements.
+This section outlines the methodologies employed and the various levels of detail (LOD) used in the models.
+
+The primary challenge lies in accurately representing the complex urban landscape to support various simulations.
+A tiled web map approach is adopted, which allows for distributed data management and adapts the Level of Definition (LOD) based on specific needs.
+However, this approach requires the careful integration of tiles to ensure seamless representation.
+
+\subsubsection{Levels of Detail for Buildings}
+\begin{itemize}
+    \item \textbf{LOD-0:} The simplest form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
+    \item \textbf{LOD-1:} Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
+    \item \textbf{LOD-2:} At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses.
+This includes detailed geometries for each entity of the building, often using complex surface models like B-REP, swept solids, or CSG techniques.
+\end{itemize}
+
+\begin{figure}[htbp]
+\centering
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{buildings-lod0.png}
+  \caption{LOD-0}
+  \label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{buildings-lod1.png}
+  \caption{LOD-1}
+  \label{fig:sub2}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{buildings-lod2.png}
+  \caption{LOD-2}
+  \label{fig:sub3}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{buildings-lod2-zoom.png}
+  \caption{Caption for Image 4}
+  \label{fig:sub4}
+\end{subfigure}
+\caption{LOD-@ with a zoom}
+\label{fig:test}
+\end{figure}
+
+\subsection{Mesh Generation for Urban Environments}
+Building meshes are generated from metadata fetched from web services like OpenStreetMap, which provides multi-polygons with holes, representing the complex urban fabric.
+
+\subsubsection{Building Meshes}
+\begin{itemize}
+    \item \textbf{LOD-0 and LOD-1:} Buildings are modeled from 2D footprints extruded to form three-dimensional volumes.
+These volumes are then combined or subtracted to represent the district or the entire city, applying union operations on buildings touching or intersecting.
+    \item \textbf{LOD-2:} The focus is on conformal and watertight meshes suitable for detailed simulation tasks.
+These meshes are generated from Building Information Modeling (BIM) data in IFC format, allowing for a detailed representation of each building component.
+\end{itemize}
+
+\subsubsection{Terrain Modeling}
+The terrain is modeled using elevation data extracted from raster images, with the following process:
+\begin{enumerate}
+    \item Start by creating a uniform mesh based on the raster image size.
+    \item Evaluate the elevation at each node.
+    \item Compute isolines for elevation and perform mesh adaptation to reduce the mesh density where possible.
+    \item Glue each tile to ensure the continuity of the terrain mesh.
+\end{enumerate}
+
+\subsubsection{Integration of Terrain and Building Meshes}
+This process involves creating a conforming mesh that includes both the terrain and the buildings, ensuring that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
+
+\subsubsection{Visual Representation}
+Advanced rendering techniques are employed to visualize the multi-fidelity urban models, supporting both detailed analysis and general urban planning discussions.
+These visualizations are crucial for assessing the impact of urban changes and for stakeholder engagement.
+
+This approach enhances the accuracy, utility, and scalability of urban models, making them vital for comprehensive urban analysis and planning in the HiDALGO2 project.
+
+\subsubsection{Computational Tools for Building Meshes}
+
+In the urban modeling process, particularly in the generation of building meshes, the Computational Geometry Algorithms Library (CGAL) plays a pivotal role.
+CGAL is renowned for its robust and efficient algorithms which are crucial for handling complex geometric data and generating high-quality meshes from them.
+
+\paragraph{Current Mesh Generation Strategy}
+The current strategy for mesh generation utilizes multi-threading (MT) to handle various stages of the mesh construction process:
+\begin{enumerate}
+    \item \textbf{Initial Setup:} Determining the tiles to be used based on the specified location, done sequentially.
+    \item \textbf{Data Acquisition:} Parallel downloading of GIS data including buildings and elevation information.
+    \item \textbf{Data Preparation:} Repairing polygons to ensure they are suitable for mesh generation, a process executed in parallel using MT.
+    \item \textbf{Mesh Generation:} The terrain mesh is generated in parallel, employing CGAL's algorithms to ensure precision and efficiency.
+    \item \textbf{Mesh Union:} Performing union operations at tile junctions to ensure continuity, which is currently a sequential step.
+    \item \textbf{Final Mesh Generation:} Building meshes are generated using a parallel MT approach, leveraging CGAL for its advanced mesh generation capabilities.
+\end{enumerate}
+
+\paragraph{Advancing Towards Full Parallelism}
+The next steps in enhancing the mesh generation process involve moving towards a fully parallel approach using both Multi-threading (MT) and Message Passing Interface (MPI):
+\begin{itemize}
+    \item \textbf{Large-scale Objectives:} The aim is to scale the process up to handle entire cities or larger urban areas.
+    \item \textbf{Distributed Computing:} Utilizing MPI to manage distributed computing resources effectively.
+    \item \textbf{Tile Partitioning:} Creating partitions of tiles with overlapping areas to ensure complete and accurate building descriptions without the need for extensive MPI communication.
+    \item \textbf{Parallel Mesh Generation:} Each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.
+\end{itemize}
+
+\subsubsection{Partitioning Strategies Depending on Simulation Use Cases}
+Different partitioning strategies are employed depending on the specific requirements of the simulation use cases:
+\begin{itemize}
+    \item \textbf{Test Case 0:} For simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient.
+    \item \textbf{Test Case 1:} When buildings interact with environmental elements, a more complex partitioning strategy that considers both the buildings and their immediate non-building surroundings is necessary.
+    \item \textbf{Test Case 2:} For full interaction models, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring that all elements are considered to minimize communication overhead.
+    \item \textbf{Test Case 3:} Looking towards scenarios with extreme partitioning needs, a multigrid approach is considered, defining coarse and fine meshes to efficiently manage computational resources.
+\end{itemize}
+
+This multi-fidelity approach not only enhances the accuracy and applicability of urban models in simulations but also ensures scalability across different computational platforms, making it a cornerstone of urban analysis in the HiDALGO2 project.
+
+\subsubsection{Conclusion on mesh construction}
+Our strategy not only aims to improve the efficiency and scalability of the mesh generation process but also enhances the fidelity and accuracy of the urban models used in simulations.
+
+\subsection{Modeling and simulations}
+
+We now turn to describing the physical modeling of  city energy simulation.
+To do this we build on two main tools: Feel++ and Modelica.
+
+\subsubsection{Feel++ Toolchain}
+
+Feel++ is a comprehensive framework designed to tackle problems based on Ordinary Differential Equations (ODEs) and Partial Differential Equations (PDEs).
+Utilizing modern C++ (C++17 and C++20) standards coupled with a Python layer through Pybind11, Feel++ enables seamless parallelism and is equipped with default communicators that simplify the handling of complex computational tasks.
+The framework's versatility is evident in its deployment across various platforms, which includes both research and educational environments, as well as cloud services tailored for high-performance computing needs.
+
+Key features of the Feel++ framework include:
+\begin{itemize}
+    \item An extensive range of numerical methods to solve PDEs such as continuous Galerkin (cG), discontinuous Galerkin (dG), hybrid discontinuous Galerkin (hdG), and reduced basis methods (rb/mor).
+    \item Domain Specific Language (DSL) for Galerkin methods which enhances the ease of implementing and experimenting with new numerical methods.
+    \item The de Rham complex provides a comprehensive toolkit for constructing finite element spaces of arbitrary order.
+    \item Automatic differentiation and symbolic integration bridge the gap between mathematical expressions and their implementation.
+    \item The framework supports a diverse array of applications from fluid dynamics, structural mechanics, to heat transfer and electrostatics, demonstrating its flexibility and broad applicability.
+    \item Integration with SpeCxx for task-based parallel execution, improving performance and scalability on modern computational architectures.
+\end{itemize}
+
+\paragraph{Simulation Tools and Applications}
+Feel++ comes equipped with a variety of toolboxes tailored for specific application domains, offering pre-built scenarios for fluid dynamics, solid mechanics, and electromagnetism, among others.
+These toolboxes are designed to provide robust and efficient solutions, leveraging the capabilities of Feel++ to address complex multi-physics problems in real-world scenarios.
+
+Documentation and further details can be accessed through [Feel++ Toolboxes Documentation](https://docs.feelpp.org/toolboxes/latest/).
+
+This powerful toolchain is essential for the Urban Building pilot of the HiDALGO
+
+\subsubsection{Computing Shading Masks and View Factors with Feel++}
+
+In urban building energy simulations, the computation of shading masks and view factors is crucial for accurately modeling the impact of solar radiation on building surfaces.
+Shading masks quantify the percentage of blocked solar radiation for each building surface (including walls and roofs) depending on the direction of the sun.
+This is influenced by nearby structures such as other buildings, vegetation, and urban furniture.
+The view factors describe the fraction of radiation that leaves one surface and strikes another, which are essential for calculating radiative heat exchanges between building surfaces.
+
+\paragraph{Numerical Methods and Challenges}
+Both shading masks and view factors are computed using Monte Carlo and ray tracing techniques, which allow for handling complex geometries with various obstructions.
+Despite being purely geometric quantities, these calculations face significant challenges such as:
+\begin{itemize}
+    \item Efficient computation of integrals for view factors, especially when considering specular surfaces that require multiple ray bounces.
+    \item Managing large-scale mesh computations and data storage, particularly when detailed urban environments are modeled.
+\end{itemize}
+
+\paragraph{Implementation in Feel++}
+Feel++ facilitates these computations through its robust numerical methods optimized for high performance and parallel execution.
+For each face of a building, Feel++ computes solar masks using a Monte Carlo approach for various sun positions, ensuring efficient and scalable processing across multiple CPU cores.
+This enables the integration of dynamic solar shading effects into the simulation of building energy performance, providing a more accurate representation of real-world conditions.
+
+\subsubsection{Heat Transfer Modeling with Feel++ and Modelica}
+In the Urban Building Energy Model (UBEM), heat transfer analysis is a crucial component for predicting energy consumption, internal air temperature variations, and overall building energy performance.
+This analysis is facilitated by a combination of Feel++ and Modelica, which together enable detailed simulations of heat dynamics within urban buildings.
+
+\paragraph{Modelica for Multizone Heat Transfer}
+Modelica offers extensive capabilities for multizone building energy simulations, utilizing models that range from simple (LOD-0) to more complex (LOD-1) representations.
+The multizone approach in Modelica is particularly useful for modular and scalable simulations, where each zone of the building can be modeled with different fidelity based on the simulation requirements.
+This method leverages the generation of Functional Mock-up Units (FMUs) which integrate seamlessly into larger C/C++ applications, providing a robust framework for handling complex simulations involving multiple interacting systems.
+
+\paragraph{Finite Element Analysis with Feel++}
+Complementing Modelica's capabilities, Feel++ provides robust tools for finite element analysis, particularly in handling the detailed aspects of heat transfer within urban environments.
+It uses advanced numerical methods like reduced basis methods for rapid scenario testing and parallel-in-time algorithms for efficient simulations.
+This is particularly important for assessing the impact of solar radiation and external shading, which are modeled using both geometric and dynamic shading masks derived from solar paths.
+
+\paragraph{Integrated Approach}
+The integration of Feel++ and Modelica is exemplified in their use of shading masks and view factors, critical for accurate solar heat gain calculations.
+These masks are computed using Monte Carlo simulations and ray tracing methods to assess the percentage of solar radiation impacting various building surfaces.
+This data feeds into the Modelica simulations, enhancing the accuracy of the thermal load predictions.
+
+\paragraph{Challenges and Solutions}
+One of the main challenges in urban building simulation is managing the computational load, which is addressed through hybrid computing strategies that leverage both CPUs and GPUs.
+This approach ensures that large-scale simulations, necessary for city-wide energy analysis, remain feasible and efficient.
+Additionally, the mesh partitioning techniques discussed earlier are employed to optimize the data handling and processing times, further integrating the spatial data management with the thermal modeling processes.
+
+By utilizing the combined strengths of Feel++ for detailed finite element analysis and Modelica for system-level energy simulation, the UBEM framework achieves a comprehensive tool capable of addressing the complex dynamics of urban heat transfer and energy management.
+
 \section{The Role of CI/CD in Urban Building Simulations}
@@
 
+\section{Current Urban Building Workflow}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.9\textwidth]{kub-workflow.pdf}
+    \caption{Current Urban Building Workflow}
+    \label{fig:ub_workflow}
+\end{figure}
+
+The Urban Building workflow integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments effectively.
+The following subsections detail each component of the workflow as depicted in the provided diagram.
+
+\subsection{Data Acquisition and Preparation}
+\begin{itemize}
+    \item \textbf{Location Data:} Initial GIS data related to the specific location.
+    \item \textbf{Weather Data Integration:} Incorporation of both regulatory and open-source weather data through the MeteoGrid system, which is then transformed into a usable format for simulations.
+\end{itemize}
+
+\subsection{Data Processing}
+\begin{itemize}
+    \item \textbf{Partitioning:} The GIS data and 3D mesh data are partitioned for scalable processing.
+    \item \textbf{UBEM Generator:} Converts GIS data into Modelica and FEEL++ compatible formats for simulation.
+\end{itemize}
+
+\subsection{Simulation and Analysis}
+\begin{itemize}
+    \item \textbf{Urban Building Energy Model (UBEM):} Uses converted data to simulate energy consumption and indoor environmental quality.
+    \item \textbf{Radiative Heat Transfer:} Calculation of heat transfer effects due to radiation, enhancing the accuracy of the energy models.
+    \item \textbf{View Factors and Shading Masks:} Computes how buildings affect each other's exposure to natural light and heat, influencing the urban heat island effect and building energy needs.
+\end{itemize}
+
+\subsection{Coupling with Urban Air Pollution Model}
+\begin{itemize}
+    \item \textbf{Integration with UAP:} The building simulation outputs are fed into the Urban Air Pollution (UAP) simulator to assess the impact of building emissions on urban air quality.
+    \item \textbf{Feedback Loop:} Intermediate outputs from the UAP simulator are utilized to refine building simulation scenarios.
+\end{itemize}
+
+\subsection{Final Output and Urban Scale Energy Analysis}
+\begin{itemize}
+    \item \textbf{UBEM Simulator:} Generates final outputs that summarize the overall energy consumption and environmental impact of buildings at an urban scale.
+    \item \textbf{Comprehensive Urban Scale Analysis:} The final integration step where data from both the building energy models and air quality models are combined to provide a holistic view of urban environmental quality.
+\end{itemize}
+
+This workflow is critical for accurately simulating and understanding the complex interdependencies between urban building energy usage and urban air quality, supporting the broader objectives of the HiDALGO2 project to improve urban living conditions and sustainability.
+
+\section{Software Stack and CI/CD Framework for the Urban Building Pilot}
+The Urban Building pilot within the HiDALGO2 project leverages a sophisticated software stack centered around the Feel++ framework.
+This section details the components of the software stack and explains how the CI/CD framework facilitates efficient development and deployment.
+
+\subsection{Feel++ Framework Capabilities}
+Feel++ is a versatile framework designed for solving complex partial differential equations (PDEs) using high-performance computing (HPC).
+The capabilities of Feel++ are critical to the simulation tasks performed in the Urban Building pilot.
+
+\begin{itemize}
+    \item \textbf{Modular Software Stack:} Feel++ supports a range of functionalities essential for computational fluid dynamics (CFD), computational solid mechanics (CSM), and thermal simulations.
+Its software stack includes:
+    \begin{itemize}
+        \item MPI C++17/20 and Boost for parallel computing.
+        \item PETSc for scalable and efficient numerical solutions.
+        \item Python bindings for scripting and automation.
+        \item Modelica integration for multidomain physical modeling and simulation.
+    \end{itemize}
+
+    \item \textbf{Simulation Capabilities:}
+    \begin{itemize}
+        \item Advanced solvers for fluid dynamics, heat transfer, and electromagnetic simulations.
+        \item Support for reduced order methods, enhancing computational efficiency.
+        \item Integration with data assimilation, machine learning, and uncertainty quantification to improve prediction accuracy and robustness.
+    \end{itemize}
+\end{itemize}
+
+\subsection{CI/CD Using GitHub Actions and Docker}
+The development and deployment of the Urban Building pilot are streamlined through a CI/CD pipeline that utilizes GitHub Actions and Docker.
+This setup ensures that the software development lifecycle is robust, with continuous integration and deployment enhancing productivity and reliability.
+
+\begin{itemize}
+    \item \textbf{GitHub Actions:} Automates workflows to compile, test, and validate code changes in real-time, facilitating rapid development cycles and ensuring code quality.
+    \item \textbf{Docker:} Provides a containerized environment where Feel++ and its dependencies are encapsulated, ensuring consistent operations across different computing environments.
+Docker images are specifically tailored for various systems, accommodating a wide range of deployment scenarios.
+\end{itemize}
+
+% \subsection{Integration with Urban Air Pollution Models}
+% As part of the CI/CD pipeline, the integration testing includes coupling with % urban air pollution models to evaluate the impact of simulated building parameters % on urban air quality.
+This ensures that the software stack not only performs as % expected in isolated tests but also behaves correctly in integrated urban % simulation environments.
+%
+
+\section{CI/CD DevOps for Feel++}
+The Continuous Integration and Continuous Deployment (CI/CD) pipeline is central to the development and maintenance of the Feel++ framework, ensuring that updates and enhancements are efficiently integrated and deployed across all projects utilizing Feel++.
+Below we outline the structured approach taken using GitHub Actions, Docker, and Apptainer.
+
+\subsection{Feel++ Environment Setup}
+Feel++ utilizes a robust environment setup that is continuously integrated and uploaded to GitHub Container Registry (ghcr.io).
+The environment includes configurations for multiple operating systems and computational backends:
+\begin{itemize}
+    \item Continuous Integration (CI) environments for Ubuntu 22.04, Ubuntu 20.04, Ubuntu 24.04, and Debian 12.
+    \item Scheduled Integration (SCI) environments include Spack-based configurations for MPI and other computational libraries.
+\end{itemize}
+
+\subsection{Pipeline Trigger Mechanisms}
+The CI/CD pipelines for Feel++ are triggered through various mechanisms to ensure responsiveness and up-to-date compatibility:
+\begin{itemize}
+    \item \textbf{Pull Requests and Merges:} Triggers the CI to ensure that new code integrations meet all tests and standards.
+    \item \textbf{Graphical User Interface (GUI):} Allows developers to manually trigger pipelines through a GUI, facilitating quick deployments or tests.
+    \item \textbf{Scheduled Runs:} Ensures regular updates and maintenance checks are performed, even during periods of low manual activity.
+\end{itemize}
+
+\subsection{Docker and Apptainer Workflow}
+\begin{itemize}
+    \item \textbf{Docker Images:} All Docker images are tailored for specific system requirements and are uploaded to ghcr.io.
+These images are then utilized to ensure consistent environments across various deployment scenarios.
+    \item \textbf{Apptainer Images:} Apptainer (formerly Singularity) provides a secure way to handle containers.
+Images created for Apptainer ensure that Feel++ can be deployed in a secure and reproducible manner across HPC environments without requiring root privileges.
+\end{itemize}
+
+\subsection{Utilization by Projects}
+\begin{itemize}
+    \item Both Docker and Apptainer images are extensively used by projects built upon the Feel++ framework.
+These projects benefit from the robust, tested, and secure environments that Feel++ CI/CD practices ensure.
+\end{itemize}
+
+\section{HPC Operations (HPC-Ops)}
+Innovative HPC-Ops practices are integral to the deployment and benchmarking processes of the Feel++ framework, enabling it to perform consistently across diverse high-performance computing (HPC) systems.
+This section details the strategies and tools used for large-scale computational benchmarks and reproducibility assurance.
+
+\subsection{Benchmarking and Reproducibility}
+Upon successful updates or integrations, large-scale benchmarking is triggered to evaluate the performance and scalability of the Feel++ applications. These benchmarks are crucial for:
+\begin{itemize}
+    \item Validating the computational correctness and efficiency across platform variations.
+    \item Ensuring that performance optimizations are effective and do not introduce errors.
+\end{itemize}
+
+\subsection{Integration with HPC Systems}
+\begin{itemize}
+    \item \textbf{Apptainer Images:} Central to the HPC-Ops strategy, Apptainer (formerly Singularity) images are used to encapsulate the computing environment, making it portable and reproducible across all HPC platforms.
+These images are maintained and updated on GitHub Container Registry (ghcr.io).
+    \item \textbf{HPC Systems:} The workflow is designed to integrate with several EuroHPC systems such as LUMI, Karolina, Meluxina, and Discoverer, as well as other significant HPC infrastructures including local systems like Gaya and global platforms such as PSNC/Eagle.
+\end{itemize}
+
+\subsection{Automation Tools}
+\begin{itemize}
+    \item \textbf{Reframe:} Used for defining and managing systematic benchmarks that are reproducible across various HPC environments.
+    \item \textbf{GitHub Actions:} Automates the CI/CD pipeline, ensuring that any changes to the codebase are consistently and reliably deployed across all environments.
+    \item \textbf{SLURM:} A key component in scheduling and managing jobs on many of the integrated HPC systems, facilitating efficient resource management and job queueing.
+\end{itemize}
+
+\subsection{Challenges and Solutions}
+Discussing the challenges encountered in integrating such a diverse array of systems and the innovative solutions developed, including:
+\begin{itemize}
+    \item Ensuring compatibility and performance across different HPC architectures.
+    \item Automating the deployment and scaling of complex simulations in a secure and efficient manner.
+\end{itemize}
+
+\subsection{Conclusion}
+The HPC-Ops framework developed for Feel++ represents a significant advancement in the field of computational sciences, driving forward the capabilities for large-scale scientific computations.
+It sets a benchmark for how modern software frameworks can integrate with advanced HPC infrastructures to enhance computational research and applications.
+
+\section{Urban Building DevOps Framework}
+
+\subsection{Source Control and Management}
+GitHub serves as the central repository hosting the source code, with robust version control to manage contributions and revisions effectively.
+
+\subsection{Continuous Integration and Deployment (CI/CD)}
+\begin{itemize}
+    \item \textbf{Feel++ Environment Setup}: Leveraging Docker and Apptainer containers ensures a consistent and reproducible environment across different systems.
+Docker images are tailored to support various operating systems and configurations, which are regularly updated and pushed to GitHub Container Registry (ghcr.io).
+    \item \textbf{Automated Testing and Deployment}:
+    \begin{itemize}
+        \item GitHub Actions automates workflows for testing, building, and deploying applications. This includes automatic updates for documentation hosted on GitHub Pages.
+        \item Integration with GitHub ensures that code changes trigger automated workflows that build and test the software across multiple platforms.
+    \end{itemize}
+\end{itemize}
+
+\subsection{Packaging}
+The software is packaged into Wheel for Python libraries and DEB packages for Debian/Ubuntu systems.
+These packages facilitate easy distribution and installation of the software.
+Spack, a flexible package manager, is used for managing the installations of software on HPC systems, ensuring that dependencies are handled correctly across different environments.
+
+\subsection{Deployment on HPC Systems}
+Utilizing Apptainer (formerly Singularity) containers enhances portability and security, allowing the Urban Building simulations to be deployed seamlessly on various HPC systems including local clusters like Gaya and EuroHPC systems such as LUMI, Karolina, Meluxina, and Discoverer.
+The use of SLURM for job scheduling on these HPC systems ensures efficient management of computational resources.
+
+\subsection{Documentation and Training}
+Documentation is automatically generated and updated with each code push to the master branch, ensuring that all features and changes are well-documented.
+The documentation includes comprehensive guides on installation, configuration, and usage, along with API documentation generated directly from the source code.
+
+\subsection{Benchmarking and Quality Assurance}
+Continuous benchmarking is integrated into the CI/CD pipeline, triggering large-scale benchmark tests upon successful preliminary tests.
+This ensures that the software performs optimally across all supported platforms before any releases.
+Quality assurance practices include code reviews, unit testing, and integration testing, all automated through GitHub Actions.
+
+By leveraging these DevOps practices, the Urban Building pilot ensures that it remains robust, scalable, and adaptable to new HPC technologies and architectures, ultimately supporting the HiDALGO2 project's goals of advancing urban simulation technologies at a global scale.
+
+\section{Urban Building HPC Operations}
+
+The Urban Building High-Performance Computing (HPC) Operations outline a sophisticated workflow that integrates continuous integration and deployment (CI/CD) with advanced benchmarking strategies.
+These operations are crucial for ensuring the performance, scalability, and reliability of the Urban Building simulations on various HPC systems.
+
+\subsection{HPC Benchmarking CI/CD}
+The benchmarking CI/CD pipeline is triggered upon successful completion of the standard CI/CD processes, which include automated testing and validation of the software.
+New Apptainer containers are created and made available, facilitating deployment on diverse computational resources.
+
+\begin{itemize}
+    \item \textbf{Automated Testing:} Once new changes are integrated and the standard CI/CD pipeline succeeds, larger scale tests are automatically initiated on a designated HPC node with significant computational resources, for example, 128 cores.
+    \item \textbf{Manual and Scheduled Testing:} For extensive validation, tests can also be manually triggered or scheduled to run at predefined intervals.
+This flexibility allows for comprehensive performance assessments under varying loads and configurations.
+\end{itemize}
+
+\subsection{Use of Reframe}
+Reframe is employed as the regression testing framework, essential for verifying the stability and performance regressions of the software across updates. It enables:
+\begin{itemize}
+    \item Systematic execution of test suites across different HPC systems.
+    \item Collection and analysis of performance data to monitor software behavior and performance trends over time.
+\end{itemize}
+
+\subsection{Integration with HPC Systems}
+\begin{itemize}
+    \item \textbf{EuroHPC Integration:} The Urban Building pilot is integrated with several EuroHPC systems like LUMI, Karolina, Meluxina, and Discoverer, enhancing the capability to perform simulations at an unprecedented scale.
+    \item \textbf{Local and International HPC Systems:} The framework also supports deployment on local HPC systems (e.g., Gaya) and international platforms like PSNC's Eagle, ensuring wide accessibility and usability of the software.
+\end{itemize}
+
+\subsection{Monitoring and Reporting}
+All performance results are automatically captured and uploaded to the HiDALGO2 portal. This ensures that:
+\begin{itemize}
+    \item Stakeholders have real-time access to performance reports.
+    \item Decision-makers can review comprehensive data to guide further optimization and development efforts.
+\end{itemize}
+
+\subsection{Deployment and Scalability}
+\begin{itemize}
+    \item \textbf{Containerized Deployment:} Utilizing Docker and Apptainer containers ensures that the Urban Building application is portable and consistent across various computing environments.
+    \item \textbf{Scalable Benchmarking:} The capability to scale tests according to the available hardware and project requirements is critical, allowing the team to simulate urban environments of varying complexities.
+\end{itemize}
+
+This comprehensive HPC operations framework underlines the commitment of the HiDALGO2 project to leveraging cutting-edge computational technologies to enhance urban simulation studies, ensuring high performance and accuracy of the Urban Building models.
+
+\section{Conclusion}
+The CI/CD practices in Feel++ not only enhance the development lifecycle of the framework itself but also ensure that all dependent projects maintain high standards of reliability, security, and performance.
+The integration of Docker and Apptainer into the workflow enables wide-ranging deployment scenarios from personal computing environments to high-performance computing clusters.
+
+The integration of Feel++ within the HiDALGO2 project's Urban Building pilot through a sophisticated CI/CD framework supports the project's goal to enhance urban sustainability and air quality.
+The continuous development, testing, and deployment facilitated by this framework are vital for adapting to evolving urban challenges and computational needs.
+
 \section{Conclusion}
@@
 \begin{credits}
-\subsubsection{\ackname} d
+\subsubsection{\ackname} Hidalgo2, Exa-MA, ITI Irmia++
 

### 2024-05-25 hid2-urban-building-cicd.tex
add image folder + lots of new content

@@
 
-\section{Objectives of the HiDALGO2 Urban Building Pilot}
 The Urban Building pilot in HiDALGO2 aims to leverage high-performance computing to enhance urban simulations for better energy management and air quality assessment.
@@
 
-\subsection{Predictive Simulations}
 Advanced simulation tools are employed to predict energy consumption, thermal comfort, and indoor air quality across both the building and urban scales.
@@
 
-\subsection{Integration with Environmental Models}
 Integrating building simulations with urban air pollution models enables the project to assess the environmental impact of building stocks comprehensively.
@@
 
-\subsection{Impact and Implementation}
 Implementing these objectives will facilitate more informed urban planning decisions, support policy development for energy efficiency, and contribute to reducing urban greenhouse gas emissions.
@@
 \section{Overview of Urban Building Modeling and Simulation}
+
+We now provide an overview of the geometrical and physical modeling and simulation components of the Urban building application.
 
@@
 
-\subsubsection{Levels of Detail for Buildings}
+We describe our definition of Levels of Detail for Buildings
 \begin{itemize}
@@
 
+In the figure~\ref{fig:buildings}, we illustrate the different levels of details.
+
 \begin{figure}[htbp]
@@
   \centering
-  \includegraphics[width=\linewidth]{buildings-lod0.png}
+  \includegraphics[width=\linewidth]{images/buildings-lod0.png}
   \caption{LOD-0}
@@
   \centering
-  \includegraphics[width=\linewidth]{buildings-lod1.png}
+  \includegraphics[width=\linewidth]{images/buildings-lod1.png}
   \caption{LOD-1}
@@
   \centering
-  \includegraphics[width=\linewidth]{buildings-lod2.png}
+  \includegraphics[width=\linewidth]{images/buildings-lod2.png}
   \caption{LOD-2}
@@
   \centering
-  \includegraphics[width=\linewidth]{buildings-lod2-zoom.png}
-  \caption{Caption for Image 4}
+  \includegraphics[width=\linewidth]{images/buildings-lod2-zoom.png}
+  \caption{LOD-2 with a zoom}
   \label{fig:sub4}
 \end{subfigure}
-\caption{LOD-@ with a zoom}
-\label{fig:test}
+\caption{}
+\label{fig:buildings}
 \end{figure}
 
-\subsection{Mesh Generation for Urban Environments}
 Building meshes are generated from metadata fetched from web services like OpenStreetMap, which provides multi-polygons with holes, representing the complex urban fabric.
+For \textbf{LOD-0 and LOD-1}, buildings are modeled from 2D footprints extruded to form three-dimensional volumes.
+These volumes are then combined or subtracted to represent the district or the entire city, applying union operations on buildings that touch or intersect.
+In \textbf{LOD-2}, the focus shifts to creating conformal and watertight meshes that are suitable for detailed simulation tasks.
+These meshes are generated from Building Information Modeling (BIM) data in IFC format, enabling a detailed representation of each building component.
 
-\subsubsection{Building Meshes}
-\begin{itemize}
-    \item \textbf{LOD-0 and LOD-1:} Buildings are modeled from 2D footprints extruded to form three-dimensional volumes.
-These volumes are then combined or subtracted to represent the district or the entire city, applying union operations on buildings touching or intersecting.
-    \item \textbf{LOD-2:} The focus is on conformal and watertight meshes suitable for detailed simulation tasks.
-These meshes are generated from Building Information Modeling (BIM) data in IFC format, allowing for a detailed representation of each building component.
-\end{itemize}
+In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0~\ref{fig:city-strasbourg-lod0} and LOD-1\ref{fig:city-strasbourg-lod1} representations.
 
 \subsubsection{Terrain Modeling}
-The terrain is modeled using elevation data extracted from raster images, with the following process:
-\begin{enumerate}
-    \item Start by creating a uniform mesh based on the raster image size.
-    \item Evaluate the elevation at each node.
-    \item Compute isolines for elevation and perform mesh adaptation to reduce the mesh density where possible.
-    \item Glue each tile to ensure the continuity of the terrain mesh.
-\end{enumerate}
+The terrain modeling process utilizes elevation data extracted from raster images.
+The initial step involves creating a uniform mesh based on the size of the raster image.
+Following this, the elevation at each node is evaluated.
+Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible.
+Finally, each tile is glued together to ensure the continuity of the terrain mesh.
 
@@
 This process involves creating a conforming mesh that includes both the terrain and the buildings, ensuring that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
+The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect.
 
@@
 
+\begin{figure}[htbp]
+\centering
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-strasbourg-lod-0.png}
+  \caption{LOD-0}
+  \label{fig:city-strasbourg-lod0}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-strasbourg-lod-1.png}
+  \caption{LOD-1}
+  \label{fig:city-strasbourg-lod1}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-grenoble-terrain.png}
+  \caption{LOD-1 terrain}
+  \label{fig:city-grenoble-terrain}
+\end{subfigure}
+\caption{}
+\label{fig:city-strasbourg}
+\end{figure}
+
 \subsubsection{Computational Tools for Building Meshes}
@@
 In the urban modeling process, particularly in the generation of building meshes, the Computational Geometry Algorithms Library (CGAL) plays a pivotal role.
-CGAL is renowned for its robust and efficient algorithms which are crucial for handling complex geometric data and generating high-quality meshes from them.
+CGAL is renowned for its robust and efficient algorithms, which are crucial for handling complex geometric data and generating high-quality meshes from them.
 
 \paragraph{Current Mesh Generation Strategy}
-The current strategy for mesh generation utilizes multi-threading (MT) to handle various stages of the mesh construction process:
-\begin{enumerate}
-    \item \textbf{Initial Setup:} Determining the tiles to be used based on the specified location, done sequentially.
-    \item \textbf{Data Acquisition:} Parallel downloading of GIS data including buildings and elevation information.
-    \item \textbf{Data Preparation:} Repairing polygons to ensure they are suitable for mesh generation, a process executed in parallel using MT.
-    \item \textbf{Mesh Generation:} The terrain mesh is generated in parallel, employing CGAL's algorithms to ensure precision and efficiency.
-    \item \textbf{Mesh Union:} Performing union operations at tile junctions to ensure continuity, which is currently a sequential step.
-    \item \textbf{Final Mesh Generation:} Building meshes are generated using a parallel MT approach, leveraging CGAL for its advanced mesh generation capabilities.
-\end{enumerate}
+The current strategy for mesh generation employs multi-threading (MT) to handle various stages of the mesh construction process.
+Initially, the tiles to be used are determined based on the specified location, a task performed sequentially.
+Following this, GIS data, including buildings and elevation information, is downloaded in parallel.
+Next, polygons are repaired to ensure they are suitable for mesh generation, with this process executed in parallel using MT.
+The terrain mesh is then generated in parallel, employing CGAL's algorithms to ensure precision and efficiency.
+Union operations at tile junctions are performed to ensure continuity, a step that is currently sequential.
+Finally, building meshes are generated using a parallel MT approach, leveraging CGAL for its advanced mesh generation capabilities.
 
 \paragraph{Advancing Towards Full Parallelism}
-The next steps in enhancing the mesh generation process involve moving towards a fully parallel approach using both Multi-threading (MT) and Message Passing Interface (MPI):
-\begin{itemize}
-    \item \textbf{Large-scale Objectives:} The aim is to scale the process up to handle entire cities or larger urban areas.
-    \item \textbf{Distributed Computing:} Utilizing MPI to manage distributed computing resources effectively.
-    \item \textbf{Tile Partitioning:} Creating partitions of tiles with overlapping areas to ensure complete and accurate building descriptions without the need for extensive MPI communication.
-    \item \textbf{Parallel Mesh Generation:} Each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.
-\end{itemize}
+The next steps in enhancing the mesh generation process involve moving towards a fully parallel approach using both Multi-threading (MT) and Message Passing Interface (MPI).
+The goal is to scale the process up to handle entire cities or larger urban areas.
+This scale-up involves utilizing MPI to manage distributed computing resources effectively.
+To achieve this, partitions of tiles with overlapping areas are created to ensure complete and accurate building descriptions without the need for extensive MPI communication.
+Furthermore, each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.
 
 \subsubsection{Partitioning Strategies Depending on Simulation Use Cases}
-Different partitioning strategies are employed depending on the specific requirements of the simulation use cases:
-\begin{itemize}
-    \item \textbf{Test Case 0:} For simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient.
-    \item \textbf{Test Case 1:} When buildings interact with environmental elements, a more complex partitioning strategy that considers both the buildings and their immediate non-building surroundings is necessary.
-    \item \textbf{Test Case 2:} For full interaction models, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring that all elements are considered to minimize communication overhead.
-    \item \textbf{Test Case 3:} Looking towards scenarios with extreme partitioning needs, a multigrid approach is considered, defining coarse and fine meshes to efficiently manage computational resources.
-\end{itemize}
+Different partitioning strategies are employed depending on the specific requirements of the simulation use cases.
+For simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient, known as Test Case 0.
+In Test Case 1, where buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings.
+For full interaction models, as in Test Case 2, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring that all elements are considered to minimize communication overhead.
+Looking towards scenarios with extreme partitioning needs, Test Case 3 employs a multigrid approach, defining coarse and fine meshes to efficiently manage computational resources.
+This multi-fidelity approach not only enhances the accuracy and applicability of urban models in simulations but also ensures scalability across different computational platforms, making it a cornerstone of urban analysis in the HiDALGO2 project.
 
-This multi-fidelity approach not only enhances the accuracy and applicability of urban models in simulations but also ensures scalability across different computational platforms, making it a cornerstone of urban analysis in the HiDALGO2 project.
+The figure~\ref{fig:partitioning} illustrate the different strategies discussed previously and present a reconstruction of New York with 10km square reconstruction with hundreds of thousands of buildings which requires the large scale approach discussed but not yet implemented nor tested.
+\begin{figure}[htbp]
+\centering
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-strasbourg-lod0-parts.png}
+  \caption{LOD-0}
+  \label{fig:city-strasbourg-lod0-parts}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-strasbourg-lod1-parts.png}
+  \caption{LOD-1}
+  \label{fig:city-strasbourg-lod1-parts}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-newyork-largescale.png}
+  \caption{LOD-1 Large scale}
+  \label{fig:city-ny-largescale}
+\end{subfigure}
+\caption{}
+\label{fig:partitioning}
+\end{figure}
 
@@
 
+\begin{figure}[htbp]
+\centering
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/solar-masks-east-facing.png}
+  \caption{LOD-0}
+  \label{fig:sm-building-east}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/solar-masks-whole-building.png}
+  \caption{LOD-1}
+  \label{fig:sm-whole-building}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/solar-masks-strasbourg.png}
+  \caption{LOD-1 Large scale}
+  \label{fig:sm-strasbourg}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/view-factors-benchmark.png}
+  \caption{Heat transfer benchmark in 2D including view factors}
+  \label{fig:view-factor}
+\end{subfigure}
+\caption{Solar masks and view factors computations}
+\label{fig:solar-masks-vf}
+\end{figure}
+
+In the figure~\ref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in the panel~\ref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in the panel~\ref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in panel~\ref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in panel~\ref{fig:view-factor}.
+
 \subsubsection{Heat Transfer Modeling with Feel++ and Modelica}
@@
     \centering
-    \includegraphics[width=.9\textwidth]{kub-workflow.pdf}
+    \includegraphics[width=.9\textwidth]{images/kub-workflow.pdf}
     \caption{Current Urban Building Workflow}

### 2024-05-26 hid2-urban-building-cicd.tex
up, start citations, add ack, rewrite of CI/CD

--- 2024-05-25 hid2-urban-building-cicd.tex
@@
 \usepackage[T1]{fontenc}
+\usepackage{subcaption}
+\usepackage{url}
+\usepackage{xcolor}
+\definecolor{darkred}{rgb}{0.6, 0, 0}
+\definecolor{darkgreen}{rgb}{0, 0.5, 0}
+\definecolor{darkblue}{rgb}{0, 0, 0.5}
+\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,      % Enable colored links
+    linkcolor=darkred,    % Color for internal links
+    filecolor=darkgreen,  % Color for file links
+    urlcolor=darkblue,    % Color for external URLs
+    citecolor=darkmagenta % Color for citations
+}
+
 \begin{document}
@@
 
-\section{The Role of CI/CD in Urban Building Simulations}
-Continuous Integration (CI) and Continuous Deployment (CD) are pivotal in the development and operation of the Urban Building pilot.
+Feel++\cite{christophe_prudhomme_feelppfeelpp_2024}
+
+\section{Current Urban Building Workflow}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.9\textwidth]{images/kub-workflow.pdf}
+    \caption{Current Urban Building Workflow}
+    \label{fig:ub_workflow}
+\end{figure}
+
+The urban building workflow integrates various data sources and computational tools to effectively simulate and analyze urban building energy and its impact on urban environments.
+The process encompasses data acquisition, processing, simulation, and analysis, coupled with an integration into urban air pollution models.
+
+\subsection{Data Handling and Simulation Process}
+The workflow begins with the collection and preparation of GIS and weather data, transforming it into a format usable for simulations.
+This data is then partitioned for scalable processing, and converted into Modelica and Feel++ compatible formats through the UBEM Generator.
+
+Using the Urban Building Energy Model (UBEM), this processed data is employed to simulate energy consumption and indoor environmental quality.
+The simulation focuses on radiative heat transfer, enhancing the accuracy of the energy models.
+It also computes view factors and shading masks, assessing how buildings affect each other’s exposure to natural light and heat, which influences the urban heat island effect and overall building energy needs.
+
+The building simulation outputs are then fed into the Urban Air Pollution (UAP) simulator to evaluate the impact of building emissions on urban air quality.
+A feedback loop refines the building simulation scenarios based on intermediate outputs from the UAP simulator, ensuring that the models accurately reflect the complex interdependencies between urban building energy usage and urban air quality.
+
+\subsection{Final Analysis and Urban Scale Energy Evaluation}
+The final step involves the UBEM Simulator, which generates outputs summarizing the overall energy consumption and environmental impact of buildings at an urban scale.
+This comprehensive urban scale analysis merges data from both the building energy models and air quality models to provide a holistic view of urban environmental quality.
+
+This streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting the broader objectives of our application to improve urban living conditions and environmental impact.
+
+\section{Overview of Urban Building Modeling and Simulation}
+
+We now provide an overview of the geometrical and physical modeling and simulation components of the Urban building application.
+
+\subsection{Geometry Reconstruction of the Urban Model}
+
+The geometric reconstruction of urban environments within the HiDALGO2 project involves a sophisticated approach to creating multi-fidelity representations of buildings, terrain, vegetation, roads, and other urban elements.
+This section outlines the methodologies employed and the various levels of detail (LOD) used in the models.
+
+The primary challenge lies in accurately representing the complex urban landscape to support various simulations.
+A tiled web map approach is adopted, which allows for distributed data management and adapts the Level of Definition (LOD) based on specific needs.
+However, this approach requires the careful integration of tiles to ensure seamless representation.
+
+We describe our definition of Levels of Detail for Buildings
+\begin{itemize}
+    \item \textbf{LOD-0:} The simplest form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
+    \item \textbf{LOD-1:} Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
+    \item \textbf{LOD-2:} At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses.
+This includes detailed geometries for each entity of the building, often using complex surface models like B-REP, swept solids, or CSG techniques.
+\end{itemize}
+
+In the figure~\ref{fig:buildings}, we illustrate the different levels of details.
+
+\begin{figure}[htbp]
+\centering
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/buildings-lod0.png}
+  \caption{LOD-0}
+  \label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/buildings-lod1.png}
+  \caption{LOD-1}
+  \label{fig:sub2}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/buildings-lod2.png}
+  \caption{LOD-2}
+  \label{fig:sub3}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/buildings-lod2-zoom.png}
+  \caption{LOD-2 with a zoom}
+  \label{fig:sub4}
+\end{subfigure}
+\caption{}
+\label{fig:buildings}
+\end{figure}
+
+Building meshes are generated from metadata fetched from web services like OpenStreetMap, which provides multi-polygons with holes, representing the complex urban fabric.
+For \textbf{LOD-0 and LOD-1}, buildings are modeled from 2D footprints extruded to form three-dimensional volumes.
+These volumes are then combined or subtracted to represent the district or the entire city, applying union operations on buildings that touch or intersect.
+In \textbf{LOD-2}, the focus shifts to creating conformal and watertight meshes that are suitable for detailed simulation tasks.
+These meshes are generated from Building Information Modeling (BIM) data in IFC format, enabling a detailed representation of each building component.
+
+In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0~\ref{fig:city-strasbourg-lod0} and LOD-1\ref{fig:city-strasbourg-lod1} representations.
+
+\subsubsection{Terrain Modeling}
+The terrain modeling process utilizes elevation data extracted from raster images.
+The initial step involves creating a uniform mesh based on the size of the raster image.
+Following this, the elevation at each node is evaluated.
+Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible.
+Finally, each tile is glued together to ensure the continuity of the terrain mesh.
+
+\subsubsection{Integration of Terrain and Building Meshes}
+This process involves creating a conforming mesh that includes both the terrain and the buildings, ensuring that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
+The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect.
+
+\subsubsection{Visual Representation}
+Advanced rendering techniques are employed to visualize the multi-fidelity urban models, supporting both detailed analysis and general urban planning discussions.
+These visualizations are crucial for assessing the impact of urban changes and for stakeholder engagement.
+
+This approach enhances the accuracy, utility, and scalability of urban models, making them vital for comprehensive urban analysis and planning in the HiDALGO2 project.
+
+\begin{figure}[htbp]
+\centering
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-strasbourg-lod-0.png}
+  \caption{LOD-0}
+  \label{fig:city-strasbourg-lod0}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-strasbourg-lod-1.png}
+  \caption{LOD-1}
+  \label{fig:city-strasbourg-lod1}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-grenoble-terrain.png}
+  \caption{LOD-1 terrain}
+  \label{fig:city-grenoble-terrain}
+\end{subfigure}
+\caption{}
+\label{fig:city-strasbourg}
+\end{figure}
+
+\subsubsection{Computational Tools for Building Meshes}
+
+In the urban modeling process, particularly in the generation of building meshes, the Computational Geometry Algorithms Library (CGAL), plays a pivotal role.
+CGAL, \cite{the_cgal_project_cgal_2024} is renowned for its robust and efficient algorithms, which are crucial for handling complex geometric data and generating high-quality meshes from them.
+
+\paragraph{Current Mesh Generation Strategy}
+The current strategy for mesh generation employs multi-threading (MT) to handle various stages of the mesh construction process.
+Initially, the tiles to be used are determined based on the specified location, a task performed sequentially.
+Following this, GIS data, including buildings and elevation information, is downloaded in parallel.
+Next, polygons are repaired to ensure they are suitable for mesh generation, with this process executed in parallel using MT.
+The terrain mesh is then generated in parallel, employing CGAL's algorithms to ensure precision and efficiency.
+Union operations at tile junctions are performed to ensure continuity, a step that is currently sequential.
+Finally, building meshes are generated using a parallel MT approach, leveraging CGAL for its advanced mesh generation capabilities.
+
+\paragraph{Advancing Towards Full Parallelism}
+The next steps in enhancing the mesh generation process involve moving towards a fully parallel approach using both Multi-threading (MT) and Message Passing Interface (MPI).
+The goal is to scale the process up to handle entire cities or larger urban areas.
+This scale-up involves utilizing MPI to manage distributed computing resources effectively.
+To achieve this, partitions of tiles with overlapping areas are created to ensure complete and accurate building descriptions without the need for extensive MPI communication.
+Furthermore, each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.
+
+\subsubsection{Partitioning Strategies Depending on Simulation Use Cases}
+Different partitioning strategies are employed depending on the specific requirements of the simulation use cases.
+For simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient, known as Test Case 0.
+In Test Case 1, where buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings.
+For full interaction models, as in Test Case 2, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring that all elements are considered to minimize communication overhead.
+Looking towards scenarios with extreme partitioning needs, Test Case 3 employs a multigrid approach, defining coarse and fine meshes to efficiently manage computational resources.
+This multi-fidelity approach not only enhances the accuracy and applicability of urban models in simulations but also ensures scalability across different computational platforms, making it a cornerstone of urban analysis in the HiDALGO2 project.
+
+The figure~\ref{fig:partitioning} illustrates the different strategies discussed previously and present a reconstruction of New York with 10km square reconstruction with hundreds of thousands of buildings which requires the large scale approach discussed but not yet implemented nor tested.
+\begin{figure}[htbp]
+\centering
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-strasbourg-lod0-parts.png}
+  \caption{LOD-0}
+  \label{fig:city-strasbourg-lod0-parts}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-strasbourg-lod1-parts.png}
+  \caption{LOD-1}
+  \label{fig:city-strasbourg-lod1-parts}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/city-newyork-largescale.png}
+  \caption{LOD-1 Large scale}
+  \label{fig:city-ny-largescale}
+\end{subfigure}
+\caption{}
+\label{fig:partitioning}
+\end{figure}
+
+\subsubsection{Conclusion on mesh construction}
+Our strategy not only aims to improve the efficiency and scalability of the mesh generation process but also enhances the fidelity and accuracy of the urban models used in simulations.
+
+\subsection{Modeling and simulations}
+
+We now turn to describing the physical modeling of city energy simulation.
+To do this, we built on two main tools: Feel++ and Modelica.
+
+\subsubsection{Feel++ Toolchain}
+
+Feel++ is a comprehensive framework designed to tackle problems based on Ordinary Differential Equations (ODEs) and Partial Differential Equations (PDEs).
+Using modern C++ (C++17 and C++20) standards coupled with a Python layer through Pybind11, Feel++ enables seamless parallelism and is equipped with default communicators that simplify handling complex computational tasks.
+The framework's versatility is evident in its deployment across various platforms, including research and educational environments and cloud services tailored for high-performance computing needs.
+
+Key features of the Feel++ framework encompass an extensive range of numerical methods designed to address Partial Differential Equations (PDEs).
+These methods include continuous Galerkin (cG), discontinuous Galerkin (dG), hybrid discontinuous Galerkin (hdG), and reduced basis methods (rb/mor).
+A Domain Specific Language (DSL) for Galerkin methods significantly enhances the ease of implementing and experimenting with new numerical methods.
+The de Rham complex provides a comprehensive toolkit for constructing finite element spaces of arbitrary order, facilitating precise mathematical modeling.
+The framework's automatic differentiation and symbolic integration capabilities effectively bridge the gap between mathematical expressions and their computational implementation.
+Feel++ supports diverse applications from fluid dynamics and structural mechanics to heat transfer and electrostatics, demonstrating its flexibility and broad applicability.
+Furthermore, its integration with Specx for task-based parallel execution optimizes performance and scalability on modern computational architectures.
+
+\paragraph{Simulation Tools and Applications}
+Feel++ comes equipped with a variety of toolboxes tailored for specific application domains, offering pre-built scenarios for fluid dynamics, solid mechanics, and electromagnetism, among others.
+These toolboxes are designed to provide robust and efficient solutions, leveraging the capabilities of Feel++ to address complex multi-physics problems in real-world scenarios.
+
+Documentation and further details can be accessed through Feel++ Toolboxes Documentation\footnote{\url{https://docs.feelpp.org/toolboxes/latest/}}.
+This powerful toolchain is essential for the Urban Building pilot of the HiDALGO
+
+\subsubsection{Computing Shading Masks and View Factors with Feel++}
+
+In urban building energy simulations, the computation of shading masks and view factors is crucial for accurately modeling the impact of solar radiation on building surfaces.
+Shading masks quantify the percentage of blocked solar radiation for each building surface (including walls and roofs) depending on the direction of the sun.
+This is influenced by nearby structures such as other buildings, vegetation, and urban furniture.
+The view factors describe the fraction of radiation that leaves one surface and strikes another, which are essential for calculating radiative heat exchanges between building surfaces.
+
+\paragraph{Numerical Methods and Challenges}
+Both shading masks and view factors are computed using Monte Carlo and ray tracing techniques, which allow for handling complex geometries with various obstructions.
+Despite being purely geometric quantities, these calculations face significant challenges such as:
+\begin{itemize}
+    \item Efficient computation of integrals for view factors, especially when considering specular surfaces that require multiple ray bounces.
+    \item Managing large-scale mesh computations and data storage, particularly when detailed urban environments are modeled.
+\end{itemize}
+
+\paragraph{Implementation in Feel++}
+Feel++ facilitates these computations through its robust numerical methods optimized for high performance and parallel execution.
+For each face of a building, Feel++ computes solar masks using a Monte Carlo approach for various sun positions, ensuring efficient and scalable processing across multiple CPU cores.
+This enables the integration of dynamic solar shading effects into the simulation of building energy performance, providing a more accurate representation of real-world conditions.
+
+\begin{figure}[htbp]
+\centering
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/solar-masks-east-facing.png}
+  \caption{LOD-0}
+  \label{fig:sm-building-east}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/solar-masks-whole-building.png}
+  \caption{LOD-1}
+  \label{fig:sm-whole-building}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/solar-masks-strasbourg.png}
+  \caption{LOD-1 Large scale}
+  \label{fig:sm-strasbourg}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{images/view-factors-benchmark.png}
+  \caption{Heat transfer benchmark in 2D including view factors}
+  \label{fig:view-factor}
+\end{subfigure}
+\caption{Solar masks and view factors computations}
+\label{fig:solar-masks-vf}
+\end{figure}
+
+In the figure~\ref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in the panel~\ref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in the panel~\ref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in panel~\ref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in panel~\ref{fig:view-factor}.
+
+\subsubsection{Heat Transfer Modeling with Feel++ and Modelica}
+In the Urban Building Energy Model (UBEM), heat transfer analysis is a crucial component for predicting energy consumption, internal air temperature variations, and overall building energy performance.
+This analysis is facilitated by a combination of Feel++ and Modelica, which together enable detailed simulations of heat dynamics within urban buildings.
+
+\paragraph{Modelica for Multizone Heat Transfer}
+Modelica offers extensive capabilities for multizone building energy simulations, utilizing models that range from simple (LOD-0) to more complex (LOD-1) representations.
+The multizone approach in Modelica is particularly useful for modular and scalable simulations, where each zone of the building can be modeled with different fidelity based on the simulation requirements.
+This method leverages the generation of Functional Mock-up Units (FMUs) which integrate seamlessly into larger C/C++ applications, providing a robust framework for handling complex simulations involving multiple interacting systems.
+
+\paragraph{Finite Element Analysis with Feel++}
+Complementing Modelica's capabilities, Feel++ provides robust tools for finite element analysis, particularly in handling the detailed aspects of heat transfer within urban environments.
+It uses advanced numerical methods like reduced basis methods for rapid scenario testing and parallel-in-time algorithms for efficient simulations.
+This is particularly important for assessing the impact of solar radiation and external shading, which are modeled using both geometric and dynamic shading masks derived from solar paths.
+
+\paragraph{Integrated Approach}
+The integration of Feel++ and Modelica is exemplified in their use of shading masks and view factors, critical for accurate solar heat gain calculations.
+These masks are computed using Monte Carlo simulations and ray tracing methods to assess the percentage of solar radiation impacting various building surfaces.
+This data feeds into the Modelica simulations, enhancing the accuracy of the thermal load predictions.
+
+\paragraph{Challenges and Solutions}
+One of the main challenges in urban building simulation is managing the computational load, which is addressed through hybrid computing strategies that leverage both CPUs and GPUs.
+This approach ensures that large-scale simulations, necessary for city-wide energy analysis, remain feasible and efficient.
+Additionally, the mesh partitioning techniques discussed earlier are employed to optimize the data handling and processing times, further integrating the spatial data management with the thermal modeling processes.
+
+By utilizing the combined strengths of Feel++ for detailed finite element analysis and Modelica for system-level energy simulation, the UBEM framework is a tool capable of addressing the complex dynamics of urban heat transfer and energy management.
+
+Continuous Integration (CI) and Continuous Deployment (CD) are pivotal in developing and operating the Urban Building pilot.
 These practices enable efficient management of complex simulation software, ensuring seamless integration and deployment across various computational infrastructures.
 
-\subsection{Continuous Integration: Ensuring Code Quality and Reliability}
-CI practices in HiDALGO2 handle complex dependencies and computational requirements specific to urban building simulations.
-Key features include automated testing, code quality checks, and automated builds, ensuring that the software remains robust and maintainable.
+CI practices handle complex dependencies and computational requirements specific to urban building simulations.
+Key features include automated testing, code quality checks, and automated builds, ensuring the software remains robust and maintainable.
 
-\subsection{Continuous Deployment: Streamlining Software Delivery}
 CD practices are tailored to manage deployment complexities across different HPC environments using containerization through Apptainer.
@@
 
+\section{CI/CD Framework for the Urban Building Pilot}
+The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment.
+This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.
+
+\subsection{Standard CI/CD DevOps}
+The development and deployment of the Urban Building pilot are enhanced through a CI/CD pipeline employing GitHub Actions and Docker.
+GitHub Actions automate real-time workflows to compile, test, and validate code changes, thereby facilitating rapid development cycles and ensuring code quality.
+Docker, on the other hand, provides a containerized environment that encapsulates Feel++ along with its dependencies, ensuring consistent operations across diverse computing environments.
+These Docker images, customized for various system requirements, are maintained on the GitHub Container Registry (ghcr.io) to accommodate a wide range of deployment scenarios.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{images/feelpp-devops.png}
+    \caption{CI/CD devops for Feel++}
+    \label{fig:feelpp-devops}
+\end{figure}
+This CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. It includes mechanisms for:
+\begin{enumerate}
+    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
+    \item \textbf{Graphical User Interface (GUI):} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
+    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
+\end{enumerate}
+
+\subsection{HPC Operations (HPC-Ops)}
+For high-performance computing applications, the Urban Building pilot incorporates specialized HPC-Ops practices that ensure the software performs consistently across various HPC systems.
+This advanced CI/CD strategy uses Apptainer (formerly Singularity) for secure and reproducible deployments across HPC environments without root privileges.
+
+The Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPC-ops workflow
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{images/feelpp-hpcops.png}
+    \caption{CI/CD HPC-ops for Feel++}
+    \label{fig:feelpp-hpcops}
+\end{figure}
+
+The tools and Strategies for HPC-Ops are  \textit{(i) }\textbf{Reframe:} Utilized to define and manage systematic benchmarks that are reproducible across different HPC environments, facilitating the testing of performance and scalability;
+\textit{(ii)}\textbf{SLURM:} Employs its REST API if available, otherwise scripted SLURM usage for CI/CD for scheduling and managing jobs on integrated HPC systems, allowing programmable job submission and monitoring directly from CI workflows; and \textit{(iii)} \textbf{Apptainer:} Ensures that Docker containers can be deployed securely and efficiently in HPC settings, supporting portability and consistency.
+
+The integration with HPC systems such as LUMI, Karolina, Meluxina, and Discoverer, as well as local and international platforms like Gaya and PSNC's Eagle, enhances the capability to perform large-scale simulations.
+The operations include automatic testing that triggers larger scale tests on designated HPC nodes once new changes are integrated and verified by standard CI/CD pipelines.
+
+\textbf{Monitoring and Reporting:}
+Performance results from these operations are automatically captured and uploaded to the HiDALGO2 portal, ensuring that stakeholders have real-time access to performance reports and that decision-makers can review comprehensive data to guide further optimization and development efforts.
+
+This comprehensive framework underlines the commitment of the HiDALGO2 project to leveraging cutting-edge computational technologies to enhance urban simulation studies, ensuring high performance and accuracy of the Urban Building models.
+It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructures to significantly advance computational research and applications.
+
 \section{Conclusion}
+The CI/CD practices in Feel++ not only enhance the development lifecycle of the framework itself but also ensure that all dependent projects maintain high standards of reliability, security, and performance.
+The integration of Docker and Apptainer into the workflow enables wide-ranging deployment scenarios from personal computing environments to high-performance computing clusters.
+
+The integration of Feel++ within the HiDALGO2 project's Urban Building pilot through a sophisticated CI/CD framework supports the project's goal to enhance urban sustainability and air quality.
+The continuous development, testing, and deployment facilitated by this framework are vital for adapting to evolving urban challenges and computational needs.
+
 CI/CD practices in HiDALGO2 are vital for advancing urban building simulations, supporting the EU's energy efficiency goals, and contributing to the reduction of greenhouse gas emissions in the urban sector.
@@
 \begin{credits}
-\subsubsection{\ackname} d
+\subsubsection{\ackname} Funded  by  the  European  Union.
+This  work  has  received  funding  from  the European  High  Performance  Computing  Joint  Undertaking  (JU)  and  Poland, Germany,  Spain,  Hungary,  France,  Greece  under  grant  agreement  number: 101093457.
+This  publication  expresses  the  opinions  of  the  authors  and  not  necessarily those of the EuroHPC JU and Associated Countries which are not responsible for any use of the information contained in this publication
+
+Part of this work was also funded by \textit{(i)} the France 2030 NumPEx Exa-MA (ANR-22-EXNU-0002) project managed by the French National Research Agency (ANR), \textit{(ii)} AMIES the french agency for interaction between mathematics and enterprises and \textit{(iii)} CNRS through its prematuration programme.
+
+We acknowledge the EuroHPC Joint Undertaking for awarding this project access through  EuroHPC Development Access grants EHPC-DEV-2024D05-025 and EHPC-DEV-2023D08-047 to the EuroHPC supercomputers : \textit{(i)} Lumi, hosted by CSC (Finland) and the Lumi consortium, \textit{(ii)} Meluxina hosted by LuxProvide, Luxembourg, \textit{(iii)} Karolina hosted by IT4Innovations National Supercomputing Center, Czechia, \textit{(iv)} Discoverer osted by Sofia Tech Park, Bulgaria, \textit{(v)} Vega hosted by IZUM, Slovenia, and \textit{(vi)} Leonardo hosted by CINECA, Italy.
+
+Finally the authors would like to acknowledge the many fruitful discussions with our partners Luc Kern from Synapse Concept and Leopold Fischer from Cisco Meraki, our colleagues \textit{(i)} from Hidalgo2 ICCS Kostis Nikas, Aristomenis Theodoridis and Petros Anastasiadis for the discussions on Reframe and joining their EuroHPC access grant, \textit{(ii)} Hidalgo2 HLRS Sameer Haroon for the discussions on CI/CD, \textit{(iii)} Pierre Alliez from INRIA Titane and Andreas Fabri from Geometry Factory regarding the discussions on CGAL and using Polygon Repair, and finally \textit{(iv)} our former colleague Zohra Djatouti, now at Kipsum, which whom we initiated this endeavor.
 
@@
 \bibliographystyle{splncs04}
-\bibliography{mybib}
+\bibliography{references}
 

### 2024-05-26 old.tex
up, start citations, add ack, rewrite of CI/CD

\section{CI/CD Framework for the Urban Building Pilot}
The Urban Building application leverages a sophisticated software stack centered around the Feel++ framework. This section  explains how the CI/CD framework facilitates efficient development and deployment.

\subsection{CI/CD Using GitHub Actions and Docker}
The development and deployment of the Urban Building pilot are streamlined through a CI/CD pipeline that utilizes GitHub Actions and Docker. This setup ensures that the software development lifecycle is robust, with continuous integration and deployment enhancing productivity and reliability.

GitHub Actions automate workflows to compile, test, and validate code changes in real-time, facilitating rapid development cycles and ensuring code quality. Additionally, Docker provides a containerized environment where Feel++ and its dependencies are encapsulated, ensuring consistent operations across different computing environments. Docker images are specifically tailored for various systems, accommodating a wide range of deployment scenarios.

We start with the CI/CD DevOps for Feel++. 
The workflow is central to developing and maintaining the Feel++ framework, ensuring that updates and enhancements are efficiently integrated and deployed across all projects utilizing Feel++. Below we outline the structured approach taken using GitHub Actions, Docker, and Apptainer.

Feel++ utilizes a robust environment setup that is continuously integrated and uploaded to the GitHub Container Registry (ghcr.io). The environment includes configurations for multiple operating systems and computational backends:
\textit{(i)} first continuous integration (CI) environments for Ubuntu 22.04, Ubuntu 20.04, Ubuntu 24.04, and Debian 12 and \textit{(ii)} scheduled integration (SCI) environments including Spack-based configurations for MPI and other computational libraries.

The CI/CD pipelines for Feel++ are triggered through various mechanisms to ensure responsiveness and up-to-date compatibility: \textit{(i)} \textbf{Pull Requests and Merges:} Triggers the CI to ensure that new code integrations meet all tests and standards, \textit{(ii)} \textbf{Graphical User Interface (GUI):} Allows developers to manually trigger pipelines through a GUI, facilitating quick deployments or tests and \textit{(iii)} \textbf{Scheduled Runs:} Ensures regular updates and maintenance checks are performed, even during periods of low manual activity.

\subsection{Docker and Apptainer Workflow}
\begin{itemize}
    \item \textbf{Docker Images:} All Docker images are tailored for specific system requirements and are uploaded to ghcr.io. These images are then utilized to ensure consistent environments across various deployment scenarios.
    \item \textbf{Apptainer Images:} Apptainer (formerly Singularity) provides a secure way to handle containers. Images created for Apptainer ensure that Feel++ can be deployed in a secure and reproducible manner across HPC environments without requiring root privileges.
\end{itemize}

\subsection{Utilization by Projects}
\begin{itemize}
    \item Both Docker and Apptainer images are extensively used by projects built upon the Feel++ framework. These projects benefit from the robust, tested, and secure environments that Feel++ CI/CD practices ensure.
\end{itemize}

\section{HPC Operations (HPC-Ops)}
Innovative HPC-Ops practices are integral to the deployment and benchmarking processes of the Feel++ framework, enabling it to perform consistently across diverse high-performance computing (HPC) systems. This section details the strategies and tools used for large-scale computational benchmarks and reproducibility assurance.

\subsection{Benchmarking and Reproducibility}
Upon successful updates or integrations, large-scale benchmarking is triggered to evaluate the performance and scalability of the Feel++ applications. These benchmarks are crucial for:
\begin{itemize}
    \item Validating the computational correctness and efficiency across platform variations.
    \item Ensuring that performance optimizations are effective and do not introduce errors.
\end{itemize}

\subsection{Integration with HPC Systems}
\begin{itemize}
    \item \textbf{Apptainer Images:} Central to the HPC-Ops strategy, Apptainer (formerly Singularity) images are used to encapsulate the computing environment, making it portable and reproducible across all HPC platforms. These images are maintained and updated on GitHub Container Registry (ghcr.io).
    \item \textbf{HPC Systems:} The workflow is designed to integrate with several EuroHPC systems such as LUMI, Karolina, Meluxina, and Discoverer, as well as other significant HPC infrastructures including local systems like Gaya and global platforms such as PSNC/Eagle.
\end{itemize}

\subsection{Automation Tools}
Our automation toolchain employs several sophisticated technologies to enhance the deployment and management of high-performance computing environments. Reframe, a framework for defining and managing systematic benchmarks, ensures reproducibility across various HPC environments, simplifying performance and scalability testing on these complex systems. GitHub Actions automates the CI/CD pipeline, enabling consistent and reliable deployment of code changes across all platforms. This tool integrates directly with our GitHub repositories to automate, customize, and execute software development workflows efficiently. Furthermore, SLURM, crucial for scheduling and managing jobs on many integrated HPC systems, includes a REST API that facilitates efficient resource management and job queuing by allowing programmable job submissions and monitoring directly from CI workflows. Apptainer, formerly known as Singularity, rounds out our toolset by providing a containerization solution specifically tailored for HPC applications, enabling the creation of portable and reproducible computing environments crucial for maintaining consistency across different systems. Together, these tools form the backbone of our automated processes, driving the efficiency and reliability of our Urban Building simulations on diverse computational infrastructures.

The challenges encountered in integrating such a diverse array of systems and the innovative solutions developed, include
\textit{(i)} ensuring compatibility and performance across different HPC architectures and \textit{(ii)} automating the deployment and scaling of complex simulations securely and efficiently.

The HPC-Ops framework developed for Feel++ represents a significant advancement in the field of computational sciences, driving forward the capabilities for large-scale scientific computations. It sets a benchmark for how modern software frameworks can integrate with advanced HPC infrastructures to enhance computational research and applications.

\subsection{Urban Building DevOps Framework}

GitHub serves as the central repository hosting the source code, with robust version control to manage contributions and revisions effectively.

\subsection{Continuous Integration and Deployment (CI/CD)}
\begin{itemize}
    \item \textbf{Feel++ Environment Setup}: Leveraging Docker and Apptainer containers ensures a consistent and reproducible environment across different systems. Docker images are tailored to support various operating systems and configurations, which are regularly updated and pushed to GitHub Container Registry (ghcr.io).
    \item \textbf{Automated Testing and Deployment}:
    \begin{itemize}
        \item GitHub Actions automates workflows for testing, building, and deploying applications. This includes automatic updates for documentation hosted on GitHub Pages.
        \item Integration with GitHub ensures that code changes trigger automated workflows that build and test the software across multiple platforms.
    \end{itemize}
\end{itemize}

\subsection{Packaging}
The software is packaged into Wheel for Python libraries and DEB packages for Debian/Ubuntu systems. These packages facilitate easy distribution and installation of the software. Spack, a flexible package manager, is used for managing the installations of software on HPC systems, ensuring that dependencies are handled correctly across different environments.

\subsection{Deployment on HPC Systems}
Utilizing Apptainer (formerly Singularity) containers enhances portability and security, allowing the Urban Building simulations to be deployed seamlessly on various HPC systems including local clusters like Gaya and EuroHPC systems such as LUMI, Karolina, Meluxina, and Discoverer. The use of SLURM for job scheduling on these HPC systems ensures efficient management of computational resources.

\subsection{Documentation and Training}
Documentation is automatically generated and updated with each code push to the master branch, ensuring that all features and changes are well-documented. The documentation includes comprehensive guides on installation, configuration, and usage, along with API documentation generated directly from the source code.

\subsection{Benchmarking and Quality Assurance}
Continuous benchmarking is integrated into the CI/CD pipeline, triggering large-scale benchmark tests upon successful preliminary tests. This ensures that the software performs optimally across all supported platforms before any releases. Quality assurance practices include code reviews, unit testing, and integration testing, all automated through GitHub Actions.

By leveraging these DevOps practices, the Urban Building pilot ensures that it remains robust, scalable, and adaptable to new HPC technologies and architectures, ultimately supporting the HiDALGO2 project's goals of advancing urban simulation technologies at a global scale.

\section{Urban Building HPC Operations}

The Urban Building High-Performance Computing (HPC) Operations outline a sophisticated workflow that integrates continuous integration and deployment (CI/CD) with advanced benchmarking strategies. These operations are crucial for ensuring the performance, scalability, and reliability of the Urban Building simulations on various HPC systems.

\subsection{HPC Benchmarking CI/CD}
The benchmarking CI/CD pipeline is triggered upon successful completion of the standard CI/CD processes, which include automated testing and validation of the software. New Apptainer containers are created and made available, facilitating deployment on diverse computational resources.

\begin{itemize}
    \item \textbf{Automated Testing:} Once new changes are integrated and the standard CI/CD pipeline succeeds, larger scale tests are automatically initiated on a designated HPC node with significant computational resources, for example, 128 cores.
    \item \textbf{Manual and Scheduled Testing:} For extensive validation, tests can also be manually triggered or scheduled to run at predefined intervals. This flexibility allows for comprehensive performance assessments under varying loads and configurations.
\end{itemize}

\subsection{Use of Reframe}
Reframe is employed as the regression testing framework, essential for verifying the stability and performance regressions of the software across updates. It enables:
\begin{itemize}
    \item Systematic execution of test suites across different HPC systems.
    \item Collection and analysis of performance data to monitor software behavior and performance trends over time.
\end{itemize}

\subsection{Integration with HPC Systems}
\begin{itemize}
    \item \textbf{EuroHPC Integration:} The Urban Building pilot is integrated with several EuroHPC systems like LUMI, Karolina, Meluxina, and Discoverer, enhancing the capability to perform simulations at an unprecedented scale.
    \item \textbf{Local and International HPC Systems:} The framework also supports deployment on local HPC systems (e.g., Gaya) and international platforms like PSNC's Eagle, ensuring wide accessibility and usability of the software.
\end{itemize}

All performance results are automatically captured and uploaded to the HiDALGO2 portal. This ensures that \textit{(i)} Stakeholders have real-time access to performance reports and \textit{(ii)} decision-makers can review comprehensive data to guide further optimization and development efforts.

\subsection{Deployment and Scalability}
\begin{itemize}
    \item \textbf{Containerized Deployment:} Utilizing Docker and Apptainer containers ensures that the Urban Building application is portable and consistent across various computing environments.
    \item \textbf{Scalable Benchmarking:} The capability to scale tests according to the available hardware and project requirements is critical, allowing the team to simulate urban environments of varying complexities.
\end{itemize}

This comprehensive HPC operations framework underlines the commitment of the HiDALGO2 project to leveraging cutting-edge computational technologies to enhance urban simulation studies, ensuring high performance and accuracy of the Urban Building models.

### 2024-05-26 hid2-urban-building-cicd.tex
new figures, added captions and updated text

@@
 
-In the figure~\ref{fig:buildings}, we illustrate the different levels of details.
+In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
+Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
+Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM.
 
@@
   \includegraphics[width=\linewidth]{images/buildings-lod0.png}
-  \caption{LOD-0}
-  \label{fig:sub1}
+  \caption{LOD-0: a building is represented by its bounding box}
+  \label{fig:building-lod0}
 \end{subfigure}%
@@
   \includegraphics[width=\linewidth]{images/buildings-lod1.png}
-  \caption{LOD-1}
-  \label{fig:sub2}
+  \caption{LOD-1: a building is represented by its ground footprint elevated to its height}
+  \label{fig:building-lod1}
 \end{subfigure}
@@
   \includegraphics[width=\linewidth]{images/buildings-lod2.png}
-  \caption{LOD-2}
-  \label{fig:sub3}
+  \caption{LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.}
+  \label{fig:building-lod2}
 \end{subfigure}%
@@
   \includegraphics[width=\linewidth]{images/buildings-lod2-zoom.png}
-  \caption{LOD-2 with a zoom}
-  \label{fig:sub4}
+  \caption{LOD-2: A zoom on the LOD-@ building.}
+  \label{fig:building-lod2-zoom}
 \end{subfigure}
-\caption{}
+\caption{Different representations of a building using our LOD definition}
 \label{fig:buildings}
@@
 
-In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0~\ref{fig:city-strasbourg-lod0} and LOD-1\ref{fig:city-strasbourg-lod1} representations.
+In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.
 
@@
 
-The Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPC-ops workflow
+Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPC-ops workflow for Feel++. The Urban Building 
 \begin{figure}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{images/ub-devops.pdf}
+    \caption{Urban Building standard Devops}
+    \label{fig:ub-devops}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{images/ub-hpcops.pdf}
+    \caption{Urban Building HPC Ops workflow}
+    \label{fig:ub-hpcops}
+\end{figure}
 \section{Conclusion}

### 2024-05-28 hid2-urban-building-cicd.tex
final version before submission

@@
 \usepackage[T1]{fontenc}
-\usepackage{subcaption}
+\usepackage{wrapfig}
+\usepackage[]{subcaption}
+
 \usepackage{url}
+\usepackage{tikz}
 \usepackage{xcolor}
@@
 \begin{document}
-\title{Enhancing Urban Building Simulations in HiDALGO2 through CI/CD Innovations}
-\author{Vincent Chabannes \inst{1}\orcidID{0000-1111-2222-3333} \and
-Javier Cladellas \inst{1}\orcidID{} \and 
-Abdoulaye Diallo \inst{1}\orcidID{} \and
-Maryam Maslek \inst{1}\orcidID{} \and
-Philippe Pinçon \inst{1}\orcidID{} \and
+\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
+\author{}
+\author{Luca Berti (formerly)\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
+Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and 
+Abdoulaye Diallo \inst{1}\ \and
+Maryam Maslek Elayam \inst{1} \and
+Philippe Pinçon \inst{1} \and
 Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
@@
 \email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
-\authorrunning{V. Chabannes and C. Prud'homme}
+\authorrunning{V. Chabannes et al.}
 
@@
 The EU's Horizon 2050 initiative sets ambitious goals to reduce these impacts through enhanced building renovation rates.
-The HiDALGO2 project supports this initiative by developing high-performance computing solutions, specifically through the Urban Building pilot application, which utilizes advanced CI/CD methodologies to streamline simulation and deployment across various computational platforms.
-\keywords{HPC, Urban building, City Energy Simulation.}
+The CoE HiDALGO2 supports this initiative by developing high-performance computing solutions, specifically through the Urban Building pilot application, which utilizes advanced CI/CD methodologies to streamline simulation and deployment across various computational platforms, such as the EuroHPC JU supercomputers.
+The present work provides an overview of the Ktirio Urban Building framework (KUB), starting with an overview of the workflow and a description of some of the main ingredients of the software stack and discusses some current results performed on EuroHPC JU supercomputers using an innovative CI/CD pipeline.
+
+\keywords{HPC, HPCOps, Urban building, City Energy Simulation.}
 
@@
 \section{Introduction}
-The building sector accounts for approximately 40\% of final energy consumption and 36\% of greenhouse gas emissions within the European Union.
-In response, the EU has established ambitious targets under the Horizon 2050 framework to double energy renovation rates over the next decade, highlighting the need for innovative solutions to drive these initiatives forward.
-The HiDALGO2 project, with its focus on high-performance computing and advanced simulations, is at the forefront of tackling this challenge, particularly through its Urban Building pilot application.
+The building sector accounts for approximately 40\% of final energy consumption and 36\% of greenhouse gas emissions within the European Union~\cite{european_commision_energy_2020}.
+In response, the EU has established ambitious targets under the Horizon 2050 framework to double energy renovation rates over the next decade~\cite{european_commision_stakeholder_2021}, highlighting the need for innovative solutions to drive these initiatives forward.
+The Centre of Excellence (CoE) HiDALGO2 project, focusing on high-performance computing and advanced simulations, is at the forefront of tackling this challenge, mainly through its Urban Building pilot application.
 
-The Urban Building pilot in HiDALGO2 aims to leverage high-performance computing to enhance urban simulations for better energy management and air quality assessment.
-This section outlines the specific objectives and expected impacts of the project.
+The Ktirio Urban Building (KUB) pilot in CoE HiDALGO2 aims to leverage high-performance computing to enhance city energy simulation for better energy management and air quality assessment.
+Advanced simulation tools predict energy consumption, thermal comfort, and indoor air quality across both the building and urban scales.
+These simulations support detailed individual building-level analysis and extend to broader urban environments, influencing urban planning and policy-making.
 
-Advanced simulation tools are employed to predict energy consumption, thermal comfort, and indoor air quality across both the building and urban scales.
-These simulations support detailed analysis at the individual building level and extend to broader urban environments, influencing urban planning and policy-making.
+Building on the foundations of the Feel++ framework, our project introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers.
+This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying these simulations at scale.
+Integrating EuroHPC JU infrastructures represents a significant advancement in making high-performance computing resources accessible for urban simulation studies.
 
-Integrating building simulations with urban air pollution models enables the project to assess the environmental impact of building stocks comprehensively.
+Thanks to synergies with another CoE HiDALGO2 pilot, the KUB project is set to integrate building simulations with urban air pollution (UAP) models to comprehensively assess the environmental impact of building stocks soon.
 This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness to environmental conditions.
@@
 
-Feel++\cite{christophe_prudhomme_feelppfeelpp_2024}
+The paper is organized as follows: Section 2 discusses KUB's current workflow, Section 3 provides an overview of some modeling and simulation components, and finally, Section 4 delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.
 
-\section{Current Urban Building Workflow}
+%Feel++\cite{christophe_prudhomme_feelppfeelpp_2024}
+
+\section{Ktirio Urban Building Workflow}
 
@@
     \includegraphics[width=.9\textwidth]{images/kub-workflow.pdf}
-    \caption{Current Urban Building Workflow}
-    \label{fig:ub_workflow}
+    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
+    \label{fig:kub-workflow}
 \end{figure}
 
-The urban building workflow integrates various data sources and computational tools to effectively simulate and analyze urban building energy and its impact on urban environments.
-The process encompasses data acquisition, processing, simulation, and analysis, coupled with an integration into urban air pollution models.
+The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments.
+The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with urban air pollution (UAP) models.
 
 \subsection{Data Handling and Simulation Process}
-The workflow begins with the collection and preparation of GIS and weather data, transforming it into a format usable for simulations.
-This data is then partitioned for scalable processing, and converted into Modelica and Feel++ compatible formats through the UBEM Generator.
+The workflow begins with collecting and preparing GIS and weather data, transforming it into a format usable for simulations.
+This data is then partitioned for scalable processing and converted into Modelica and Feel++\cite{christophe_prudhomme_feelppfeelpp_2024} compatible formats through the UBEM Generator.
 
-Using the Urban Building Energy Model (UBEM), this processed data is employed to simulate energy consumption and indoor environmental quality.
+This processed data is employed to simulate energy consumption and indoor environmental quality using the Urban Building Energy Model (UBEM).
 The simulation focuses on radiative heat transfer, enhancing the accuracy of the energy models.
-It also computes view factors and shading masks, assessing how buildings affect each other’s exposure to natural light and heat, which influences the urban heat island effect and overall building energy needs.
+It also computes view factors and shading masks, assessing how buildings affect each other's exposure to natural light and heat, influencing the urban heat island effect and overall building energy needs.
 
-The building simulation outputs are then fed into the Urban Air Pollution (UAP) simulator to evaluate the impact of building emissions on urban air quality.
+The building simulation outputs are then optionally fed into the urban air pollution (UAP) simulator to evaluate the impact of building emissions on urban air quality.
 A feedback loop refines the building simulation scenarios based on intermediate outputs from the UAP simulator, ensuring that the models accurately reflect the complex interdependencies between urban building energy usage and urban air quality.
@@
 \subsection{Final Analysis and Urban Scale Energy Evaluation}
-The final step involves the UBEM Simulator, which generates outputs summarizing the overall energy consumption and environmental impact of buildings at an urban scale.
-This comprehensive urban scale analysis merges data from both the building energy models and air quality models to provide a holistic view of urban environmental quality.
+The final step involves the UBEM Simulator, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale.
+This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.
 
-This streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting the broader objectives of our application to improve urban living conditions and environmental impact.
+This streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting our application's broader objectives of improving urban living conditions and environmental impact.
 
@@
 
-\subsection{Geometry Reconstruction of the Urban Model}
+\subsection{Geometry Reconstruction of the KUB Urban Model}
 
-The geometric reconstruction of urban environments within the HiDALGO2 project involves a sophisticated approach to creating multi-fidelity representations of buildings, terrain, vegetation, roads, and other urban elements.
+The geometric reconstruction of urban environments within KUB involves a sophisticated approach to creating multi-fidelity representations of buildings, terrain, vegetation, roads, and other urban elements.
 This section outlines the methodologies employed and the various levels of detail (LOD) used in the models.
@@
 The primary challenge lies in accurately representing the complex urban landscape to support various simulations.
-A tiled web map approach is adopted, which allows for distributed data management and adapts the Level of Definition (LOD) based on specific needs.
-However, this approach requires the careful integration of tiles to ensure seamless representation.
+A tiled web map approach is adopted, which allows for distributed data management and adapts the Level of Detail (LOD) based on specific needs.
+However, this approach requires carefully integrating tiles to ensure seamless representation.
 
-We describe our definition of Levels of Detail for Buildings
+We describe our definition of Levels of Detail for Buildings such as:
 \begin{itemize}
-    \item \textbf{LOD-0:} The simplest form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
+    \item \textbf{LOD-0:} The most straightforward form, representing buildings as oriented bounding boxes.
+This level is typically used for large-scale preliminary analyses and quick visual assessments.
     \item \textbf{LOD-1:} Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
     \item \textbf{LOD-2:} At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses.
-This includes detailed geometries for each entity of the building, often using complex surface models like B-REP, swept solids, or CSG techniques.
+This includes detailed geometries for each building entity, often using complex surface models like B-REP, swept solids, or CSG techniques.
 \end{itemize}
 
+\begin{wrapfigure}{R}{0.6\textwidth} % 'R' or 'L' for right or left, and width
+\centering
+\subfloat[LOD-0: a building is represented by its bounding box]{%
+  \includegraphics[width=0.48\linewidth]{images/buildings-lod0.png}
+  \label{fig:building-lod0}
+}
+%\hfill % This ensures that the images are placed side by side
+\subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
+  \includegraphics[width=0.48\linewidth]{images/buildings-lod1.png}
+  \label{fig:building-lod1}
+}\\ % Ends the line for the first row of figures
+
+\subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
+  \includegraphics[width=0.48\linewidth]{images/buildings-lod2.png}
+  \label{fig:building-lod2}
+}
+%\hfill
+\subfloat[LOD-2: A zoom on the LOD-2 building.]{%
+  \includegraphics[width=0.48\linewidth]{images/buildings-lod2-zoom.png}
+  \label{fig:building-lod2-zoom}
+}
+
+\caption{Different representations of a building using our LOD definition}
+\label{fig:buildings}
+\end{wrapfigure}
 In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
@@
 Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM.
+In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.
 
-\begin{figure}[htbp]
-\centering
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/buildings-lod0.png}
-  \caption{LOD-0: a building is represented by its bounding box}
-  \label{fig:building-lod0}
-\end{subfigure}%
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/buildings-lod1.png}
-  \caption{LOD-1: a building is represented by its ground footprint elevated to its height}
-  \label{fig:building-lod1}
-\end{subfigure}
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/buildings-lod2.png}
-  \caption{LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.}
-  \label{fig:building-lod2}
-\end{subfigure}%
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/buildings-lod2-zoom.png}
-  \caption{LOD-2: A zoom on the LOD-@ building.}
-  \label{fig:building-lod2-zoom}
-\end{subfigure}
-\caption{Different representations of a building using our LOD definition}
-\label{fig:buildings}
-\end{figure}
-
-Building meshes are generated from metadata fetched from web services like OpenStreetMap, which provides multi-polygons with holes, representing the complex urban fabric.
+\subsubsection{Building Modeling}
+Building meshes are generated from metadata fetched from web services like OpenStreetMap~\cite{openstreetmap_contributors_planet_2017}, which provides multi-polygons with holes representing the complex urban fabric.
 For \textbf{LOD-0 and LOD-1}, buildings are modeled from 2D footprints extruded to form three-dimensional volumes.
 These volumes are then combined or subtracted to represent the district or the entire city, applying union operations on buildings that touch or intersect.
-In \textbf{LOD-2}, the focus shifts to creating conformal and watertight meshes that are suitable for detailed simulation tasks.
+In \textbf{LOD-2}, the focus shifts to creating conformal and watertight meshes suitable for detailed simulation tasks.
 These meshes are generated from Building Information Modeling (BIM) data in IFC format, enabling a detailed representation of each building component.
-
-In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.
 
@@
 Following this, the elevation at each node is evaluated.
-Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible.
+However, this method provides a very refined mesh, even when the terrain is flat. For this reason, we plan to apply the following procedure:
+\begin{itemize}
+    \item Compute an arbitrary number of isolines for elevation,
+    \item Build a new terrain mesh conform with the isolines nodes and adapt to terrain elevation gradient.
+\end{itemize}
+%Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible.
 Finally, each tile is glued together to ensure the continuity of the terrain mesh.
 
-\subsubsection{Integration of Terrain and Building Meshes}
-This process involves creating a conforming mesh that includes both the terrain and the buildings, ensuring that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
-The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect.
+\subsubsection{Vegetation Modeling}
+Including vegetation (trees) in this geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas has a significant impact. 
+We use the OpenStreetMap database to obtain the metadata associated with the vegetation.
+In addition to the position of the trees, we can also obtain other information, such as the tree's height and species.
+The current strategy is as follows:
+\begin{itemize}
+\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD).
+These geometric entities are parameterized so that a transformation can be applied.
+\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best we can (by searching around).
+\item Creating a tree geometric model using an affine transformation of the reference tree model.
+\end{itemize}
+
+\subsubsection{Integration of all urban geometric components}
+This process involves creating a conforming mesh that includes both components (buildings, terrains, vegetation).
+Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
+The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
+\textit{(iii)} Apply the intersection of vegetation with buildings and terrain.
+And \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).
 
 \subsubsection{Visual Representation}
-Advanced rendering techniques are employed to visualize the multi-fidelity urban models, supporting both detailed analysis and general urban planning discussions.
+Advanced rendering techniques visualize the multi-fidelity urban models, supporting detailed analysis and general urban planning discussions.
 These visualizations are crucial for assessing the impact of urban changes and for stakeholder engagement.
 
-This approach enhances the accuracy, utility, and scalability of urban models, making them vital for comprehensive urban analysis and planning in the HiDALGO2 project.
+This approach enhances urban models' accuracy, utility, and scalability, making them vital for comprehensive urban analysis and planning in the HiDALGO2 project.
 
-\begin{figure}[htbp]
+\begin{wrapfigure}{R}{0.6\textwidth}
 \centering
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/city-strasbourg-lod-0.png}
-  \caption{LOD-0}
-  \label{fig:city-strasbourg-lod0}
-\end{subfigure}%
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/city-strasbourg-lod-1.png}
-  \caption{LOD-1}
-  \label{fig:city-strasbourg-lod1}
-\end{subfigure}
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/city-grenoble-terrain.png}
-  \caption{LOD-1 terrain}
-  \label{fig:city-grenoble-terrain}
-\end{subfigure}
-\caption{}
+\subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
+  \includegraphics[width=0.4\textwidth]{images/city-strasbourg-lod-0.png}
+}
+\hfill % Ensures that the images are placed side by side
+\subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
+  \includegraphics[width=0.4\textwidth]{images/city-strasbourg-lod-1.png}
+}\\ % Ends the line for the first row of figures
+
+\subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
+  \includegraphics[width=0.4\textwidth]{images/city-grenoble-terrain.png}
+}
+
+\caption{Various representations of cities and terrain.
+Representation of Strasbourg center with LOD-0 in the top left panel and LOD-1 in the top right.
+LOD-1 city (Grenoble, France) representation with terrain elevation.}
 \label{fig:city-strasbourg}
-\end{figure}
+\end{wrapfigure}
 
-\subsubsection{Computational Tools for Building Meshes}
+\subsubsection{Computational Tools for Meshes Generation}
 
-In the urban modeling process, particularly in the generation of building meshes, the Computational Geometry Algorithms Library (CGAL), plays a pivotal role.
-CGAL, \cite{the_cgal_project_cgal_2024} is renowned for its robust and efficient algorithms, which are crucial for handling complex geometric data and generating high-quality meshes from them.
+In the urban modeling process, particularly in generating building meshes, the Computational Geometry Algorithms Library (CGAL) plays a pivotal role.
+CGAL, \cite{the_cgal_project_cgal_2024} is renowned for its robust and efficient algorithms, which are crucial for handling complex geometric data and generating high-quality meshes.
+This library is currently used for the following operations: boolean operation of polygon, multi-polygon repairs, mesh generation, mesh intersection, mesh adaptation, and building roof skeleton.
+
+All the features described above are not yet operational in our framework.
+We can reconstruct a geometric model of an urban area whose location is arbitrary so that the user can select an area anywhere in the world.
+The final mesh comprises all buildings LOD-0 or LOD-1 and the terrain with elevation.
+The integration of all the urban components is currently being investigated.
+This part requires fairly costly algorithms (mesh intersection), for which it will be necessary to form groups intelligently to reduce the computational cost.
 
@@
 The current strategy for mesh generation employs multi-threading (MT) to handle various stages of the mesh construction process.
-Initially, the tiles to be used are determined based on the specified location, a task performed sequentially.
+Initially, the tiles used are determined based on the specified location, a task performed sequentially.
 Following this, GIS data, including buildings and elevation information, is downloaded in parallel.
@@
 \paragraph{Advancing Towards Full Parallelism}
-The next steps in enhancing the mesh generation process involve moving towards a fully parallel approach using both Multi-threading (MT) and Message Passing Interface (MPI).
-The goal is to scale the process up to handle entire cities or larger urban areas.
+The following steps in enhancing the mesh generation process involve moving towards a fully parallel approach using both Multi-threading (MT) and Message Passing Interface (MPI).
+The goal is to scale the process to handle entire cities or larger urban areas.
 This scale-up involves utilizing MPI to manage distributed computing resources effectively.
-To achieve this, partitions of tiles with overlapping areas are created to ensure complete and accurate building descriptions without the need for extensive MPI communication.
+To achieve this, partitions of tiles with overlapping regions are created to ensure complete and accurate building descriptions without requiring extensive MPI communications.
 Furthermore, each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.
@@
 \subsubsection{Partitioning Strategies Depending on Simulation Use Cases}
-Different partitioning strategies are employed depending on the specific requirements of the simulation use cases.
-For simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient, known as Test Case 0.
-In Test Case 1, where buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings.
-For full interaction models, as in Test Case 2, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring that all elements are considered to minimize communication overhead.
-Looking towards scenarios with extreme partitioning needs, Test Case 3 employs a multigrid approach, defining coarse and fine meshes to efficiently manage computational resources.
-This multi-fidelity approach not only enhances the accuracy and applicability of urban models in simulations but also ensures scalability across different computational platforms, making it a cornerstone of urban analysis in the HiDALGO2 project.
+Data partitioning is a crucial stage in the deployment of the supercomputer simulator.
+We need to partition the geometry of the city in such a way as to distribute the simulation computation correctly.
+Different partitioning strategies are considered depending on the specific requirements of the simulation use cases :
+\begin{itemize}
+\item Case 0: simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient
+\item Case 1: buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings.
+The build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately.
+\item  Case 2: for full interaction models, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead.
+\item Case 3: Regarding scenarios with extreme partitioning needs, Test Case 3 employs a multi-grid approach, defining coarse and fine meshes to manage computational resources efficiently.
+This multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
+\end{itemize}
 
-The figure~\ref{fig:partitioning} illustrates the different strategies discussed previously and present a reconstruction of New York with 10km square reconstruction with hundreds of thousands of buildings which requires the large scale approach discussed but not yet implemented nor tested.
+The current version of our simulation framework has implemented case 0 and case 1.
+Cases 2 and 3 require a full conformal mesh, which is not yet available.
+Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
+\begin{wrapfigure}{R}{0.6\textwidth}
+\centering
+\subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
+  \includegraphics[width=0.48\linewidth]{images/city-strasbourg-lod0-parts.png}
+}
+%\hfill % Ensures that the images are placed side by side
+\subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
+  \includegraphics[width=0.48\linewidth]{images/city-strasbourg-lod1-parts.png}
+}
+%\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
+%  \includegraphics[width=0.4\textwidth]{images/city-newyork-largescale.png}
+%}
+\caption{Mesh partitioning illustrations}
+\label{fig:partitioning}
+\end{wrapfigure}
+
+The figure~\ref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in figure \ref{fig:city-ny-largescale}.
+This geometric model has an area of 400 $km^2$ (20 km square side of 20 km) and has generated around 450000 buildings.
+This example requires the large-scale approach discussed but not yet implemented or tested.
+
 \begin{figure}[htbp]
 \centering
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/city-strasbourg-lod0-parts.png}
-  \caption{LOD-0}
-  \label{fig:city-strasbourg-lod0-parts}
-\end{subfigure}%
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/city-strasbourg-lod1-parts.png}
-  \caption{LOD-1}
-  \label{fig:city-strasbourg-lod1-parts}
-\end{subfigure}
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/city-newyork-largescale.png}
-  \caption{LOD-1 Large scale}
+\subfloat[View on whole 3D mesh\label{fig:city-ny-largescale-whole}]{%
+  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-whole.png}
+}
+\hfill
+\subfloat[Zoom on Manhattan buildings\label{fig:city-ny-largescale-zoomB}]{%
+  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomB.png}
+}\\
+\subfloat[Focus on Manhattan\label{fig:city-ny-largescale-zoomZ}]{%
+  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomA.png}
+}
+\hfill
+\subfloat[Central Park\label{fig:city-ny-largescale-zoomC}]{%
+  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomC.png}
+}
+\caption{$20 \times 20 \mathrm{km}^2\ $ geometric reconstruction of New York City (LOD-1)}
 \label{fig:city-ny-largescale}
-\end{subfigure}
-\caption{}
-\label{fig:partitioning}
 \end{figure}
@@
 \subsubsection{Conclusion on mesh construction}
-Our strategy not only aims to improve the efficiency and scalability of the mesh generation process but also enhances the fidelity and accuracy of the urban models used in simulations.
+Our strategy aims to improve the efficiency and scalability of the mesh generation process and enhance the fidelity and accuracy of the urban models used in simulations.
 
@@
 
-\subsubsection{Feel++ Toolchain}
+\subsubsection{KUB is based on the Feel++ toolchain}
 
@@
 
-Key features of the Feel++ framework encompass an extensive range of numerical methods designed to address Partial Differential Equations (PDEs).
+Key features of the Feel++ framework encompass an extensive range of numerical methods designed to address Partial Differential Equations (PDEs), see~\cite{christophe_prudhomme_feelppfeelpp_2024}.
 These methods include continuous Galerkin (cG), discontinuous Galerkin (dG), hybrid discontinuous Galerkin (hdG), and reduced basis methods (rb/mor).
@@
 The framework's automatic differentiation and symbolic integration capabilities effectively bridge the gap between mathematical expressions and their computational implementation.
-Feel++ supports diverse applications from fluid dynamics and structural mechanics to heat transfer and electrostatics, demonstrating its flexibility and broad applicability.
+Feel++ supports diverse applications, from fluid dynamics and structural mechanics to heat transfer and electrostatics, demonstrating its flexibility and broad applicability.
 Furthermore, its integration with Specx for task-based parallel execution optimizes performance and scalability on modern computational architectures.
 
-\paragraph{Simulation Tools and Applications}
-Feel++ comes equipped with a variety of toolboxes tailored for specific application domains, offering pre-built scenarios for fluid dynamics, solid mechanics, and electromagnetism, among others.
+%\paragraph{Simulation Tools and Applications}
+%Feel++ comes equipped with various toolboxes tailored for specific application domains, offering pre-built scenarios for fluid dynamics, solid mechanics, and electromagnetism, among others.
 These toolboxes are designed to provide robust and efficient solutions, leveraging the capabilities of Feel++ to address complex multi-physics problems in real-world scenarios.
@@
 Documentation and further details can be accessed through Feel++ Toolboxes Documentation\footnote{\url{https://docs.feelpp.org/toolboxes/latest/}}.
-This powerful toolchain is essential for the Urban Building pilot of the HiDALGO
+This powerful toolchain is essential for KUB.
 
@@
 
-In urban building energy simulations, the computation of shading masks and view factors is crucial for accurately modeling the impact of solar radiation on building surfaces.
-Shading masks quantify the percentage of blocked solar radiation for each building surface (including walls and roofs) depending on the direction of the sun.
+In city energy simulations, the computation of shading masks and view factors is crucial for accurately modeling the impact of solar radiation on building surfaces.
+Shading masks quantify the percentage of blocked solar radiation for each building surface (including walls and roofs) depending on the sun's direction.
 This is influenced by nearby structures such as other buildings, vegetation, and urban furniture.
-The view factors describe the fraction of radiation that leaves one surface and strikes another, which are essential for calculating radiative heat exchanges between building surfaces.
+The view factors describe the fraction of radiation that leaves one surface and strikes another, essential for calculating radiative heat exchanges between building surfaces.
 
@@
 \centering
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/solar-masks-east-facing.png}
-  \caption{LOD-0}
-  \label{fig:sm-building-east}
-\end{subfigure}%
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/solar-masks-whole-building.png}
-  \caption{LOD-1}
-  \label{fig:sm-whole-building}
-\end{subfigure}
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/solar-masks-strasbourg.png}
-  \caption{LOD-1 Large scale}
-  \label{fig:sm-strasbourg}
-\end{subfigure}
-\begin{subfigure}{.4\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{images/view-factors-benchmark.png}
-  \caption{Heat transfer benchmark in 2D including view factors}
-  \label{fig:view-factor}
-\end{subfigure}
+\subfloat[LOD-0\label{fig:sm-building-east}]{%
+  \includegraphics[width=0.45\textwidth]{images/solar-masks-east-facing.png}
+}
+\hfill
+\subfloat[LOD-1\label{fig:sm-whole-building}]{%
+  \includegraphics[width=0.45\textwidth]{images/solar-masks-whole-building.png}
+}\\
+\subfloat[LOD-1 Large scale\label{fig:sm-strasbourg}]{%
+  \includegraphics[width=0.45\textwidth]{images/solar-masks-strasbourg.png}
+}
+\hfill
+\subfloat[Heat transfer benchmark in 2D including view factors~\cite{van_eck_surface_2016}\label{fig:view-factor}]{%
+  \includegraphics[width=0.45\textwidth]{images/view-factors-benchmark.png}
+}
 \caption{Solar masks and view factors computations}
@@
 
-In the figure~\ref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in the panel~\ref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in the panel~\ref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in panel~\ref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in panel~\ref{fig:view-factor}.
+In the figure~\ref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in the panel~\ref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in the panel~\ref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in panel~\ref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in panel~\ref{fig:view-factor}.
 
 \subsubsection{Heat Transfer Modeling with Feel++ and Modelica}
-In the Urban Building Energy Model (UBEM), heat transfer analysis is a crucial component for predicting energy consumption, internal air temperature variations, and overall building energy performance.
-This analysis is facilitated by a combination of Feel++ and Modelica, which together enable detailed simulations of heat dynamics within urban buildings.
+In the Urban Building Energy Model (UBEM), heat transfer analysis is crucial for predicting energy consumption, internal air temperature variations, and overall building energy performance.
+This analysis is facilitated by a combination of Feel++ and Modelica, enabling detailed simulations of heat dynamics within urban buildings.
 
@@
 Modelica offers extensive capabilities for multizone building energy simulations, utilizing models that range from simple (LOD-0) to more complex (LOD-1) representations.
-The multizone approach in Modelica is particularly useful for modular and scalable simulations, where each zone of the building can be modeled with different fidelity based on the simulation requirements.
-This method leverages the generation of Functional Mock-up Units (FMUs) which integrate seamlessly into larger C/C++ applications, providing a robust framework for handling complex simulations involving multiple interacting systems.
+The multizone approach in Modelica is beneficial for modular and scalable simulations, where each building zone can be modeled with different fidelity based on the simulation requirements.
+This method leverages the generation of Functional Mock-up Units (FMUs), which integrate seamlessly into larger C/C++ applications, providing a robust framework for handling complex simulations involving multiple interacting systems.
 
@@
 It uses advanced numerical methods like reduced basis methods for rapid scenario testing and parallel-in-time algorithms for efficient simulations.
-This is particularly important for assessing the impact of solar radiation and external shading, which are modeled using both geometric and dynamic shading masks derived from solar paths.
+This is particularly important for assessing the impact of solar radiation and external shading, which are modeled using geometric and dynamic shading masks derived from solar paths.
 
 \paragraph{Integrated Approach}
-The integration of Feel++ and Modelica is exemplified in their use of shading masks and view factors, critical for accurate solar heat gain calculations.
+The integration of Feel++ and Modelica is exemplified in their use of shading masks and view factors, which are critical for accurate solar heat gain calculations.
 These masks are computed using Monte Carlo simulations and ray tracing methods to assess the percentage of solar radiation impacting various building surfaces.
@@
 \paragraph{Challenges and Solutions}
-One of the main challenges in urban building simulation is managing the computational load, which is addressed through hybrid computing strategies that leverage both CPUs and GPUs.
+One of the main challenges in urban building simulation is managing the computational load, which is addressed through computing strategies that leverage currently CPUs but in the GPUs but, in the future, will enable hybrid computing with both CPUs and GPUs.
 This approach ensures that large-scale simulations, necessary for city-wide energy analysis, remain feasible and efficient.
@@
 
-By utilizing the combined strengths of Feel++ for detailed finite element analysis and Modelica for system-level energy simulation, the UBEM framework is a tool capable of addressing the complex dynamics of urban heat transfer and energy management.
+%By utilizing the combined strengths of Feel++ for detailed finite element analysis and Modelica for system-level energy simulation, the UBEM framework is a tool capable of %%addressing the complex dynamics of urban heat transfer and energy management.%
 
-Continuous Integration (CI) and Continuous Deployment (CD) are pivotal in developing and operating the Urban Building pilot.
+%Continuous Integration (CI) and Continuous Deployment (CD) are pivotal in developing and operating the Urban Building pilot.
 These practices enable efficient management of complex simulation software, ensuring seamless integration and deployment across various computational infrastructures.
 
-CI practices handle complex dependencies and computational requirements specific to urban building simulations.
+%CI practices handle complex dependencies and computational requirements specific to urban building simulations.
 Key features include automated testing, code quality checks, and automated builds, ensuring the software remains robust and maintainable.
 
-CD practices are tailored to manage deployment complexities across different HPC environments using containerization through Apptainer.
+%CD practices are tailored to manage deployment complexities across different HPC environments using containerization through Apptainer.
 This approach facilitates consistent, reproducible deployments, optimizing performance and resource utilization.
@@
 The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment.
-This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.
+%This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.
 
 \subsection{Standard CI/CD DevOps}
-The development and deployment of the Urban Building pilot are enhanced through a CI/CD pipeline employing GitHub Actions and Docker.
-GitHub Actions automate real-time workflows to compile, test, and validate code changes, thereby facilitating rapid development cycles and ensuring code quality.
-Docker, on the other hand, provides a containerized environment that encapsulates Feel++ along with its dependencies, ensuring consistent operations across diverse computing environments.
-These Docker images, customized for various system requirements, are maintained on the GitHub Container Registry (ghcr.io) to accommodate a wide range of deployment scenarios.
+The development and deployment of KUB builds on top of the Feel++ CI/CD framework.
+It employs GitHub Actions and Docker: GitHub Actions automate real-time workflows to compile, test, and validate code changes, facilitating rapid development cycles and ensuring code quality.
+On the other hand, Docker provides a containerized environment that encapsulates Feel++ and its dependencies, ensuring consistent operations across diverse computing environments.
+These Docker images, customized for various system requirements, are maintained on the GitHub Container Registry (ghcr.io) to accommodate multiple deployment scenarios.
 
@@
     \includegraphics[width=\textwidth]{images/feelpp-devops.png}
-    \caption{CI/CD devops for Feel++}
+    \caption{CI/CD DevOps for Feel++}
     \label{fig:feelpp-devops}
 \end{figure}
-This CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. It includes mechanisms for:
+The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework.
+The workflow leverages various main ingredients of GitHub Actions features.
 \begin{enumerate}
     \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
-    \item \textbf{Graphical User Interface (GUI):} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
+    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
     \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
@@
 
-\subsection{HPC Operations (HPC-Ops)}
-For high-performance computing applications, the Urban Building pilot incorporates specialized HPC-Ops practices that ensure the software performs consistently across various HPC systems.
-This advanced CI/CD strategy uses Apptainer (formerly Singularity) for secure and reproducible deployments across HPC environments without root privileges.
+\subsection{HPC DevOps (HPCOps)}
+Feel++ CI/CD workflow for high-performance computing applications incorporates specialized HPCOps (HPC DevOps) practices that ensure the software performs consistently across various HPC systems.
 
-Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPC-ops workflow for Feel++. The Urban Building 
+%This advanced CI/CD strategy uses Apptainer (formerly Singularity) for secure and reproducible deployments across HPC environments without root privileges.
+
+Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
 \begin{figure}
@@
     \includegraphics[width=\textwidth]{images/feelpp-hpcops.png}
-    \caption{CI/CD HPC-ops for Feel++}
+    \caption{CI/CD HPCOps for Feel++}
     \label{fig:feelpp-hpcops}
@@
 
-The tools and Strategies for HPC-Ops are  \textit{(i) }\textbf{Reframe:} Utilized to define and manage systematic benchmarks that are reproducible across different HPC environments, facilitating the testing of performance and scalability;
-\textit{(ii)}\textbf{SLURM:} Employs its REST API if available, otherwise scripted SLURM usage for CI/CD for scheduling and managing jobs on integrated HPC systems, allowing programmable job submission and monitoring directly from CI workflows; and \textit{(iii)} \textbf{Apptainer:} Ensures that Docker containers can be deployed securely and efficiently in HPC settings, supporting portability and consistency.
+The tools and strategies for HPCOps are  \textit{(i) }\textbf{Reframe-HPC:} Utilized to define and manage systematic benchmarks that are reproducible across different HPC environments, facilitating the testing of performance and scalability, see~\cite{karakasis_reframe-hpcreframe_2024};
+\textit{(ii)}\textbf{SLURM:} Employs its REST API if available, \textit{e.g.} on MeLuXiNa, otherwise scripted SLURM usage for CI/CD for scheduling and managing jobs on integrated HPC systems, allowing programmable job submission and monitoring directly from CI workflows, see~\cite{slurm_development_team_slurm_2024}; and \textit{(iii)} \textbf{Apptainer:} Ensures that Docker containers can be deployed securely and efficiently in HPC settings, supporting portability and consistency, see~\cite{apptainer_contributors_apptainer_2024}.
 
-The integration with HPC systems such as LUMI, Karolina, Meluxina, and Discoverer, as well as local and international platforms like Gaya and PSNC's Eagle, enhances the capability to perform large-scale simulations.
-The operations include automatic testing that triggers larger scale tests on designated HPC nodes once new changes are integrated and verified by standard CI/CD pipelines.
+Integration with EuroHPC JU supercomputers such as LUMI, Karolina, Meluxina, Discoverer, Vega, and Leonardo enhances the capability to perform large-scale simulations and check the parallel properties and correctness of Feel++.
+The operations include automatic testing that triggers larger-scale tests on designated HPC nodes once new changes are integrated and verified by standard CI/CD pipelines.
 
-\textbf{Monitoring and Reporting:}
-Performance results from these operations are automatically captured and uploaded to the HiDALGO2 portal, ensuring that stakeholders have real-time access to performance reports and that decision-makers can review comprehensive data to guide further optimization and development efforts.
+Regarding monitoring and reporting, performance results from these operations are automatically captured and uploaded to the data storage system, such as the performance reports
 
-This comprehensive framework underlines the commitment of the HiDALGO2 project to leveraging cutting-edge computational technologies to enhance urban simulation studies, ensuring high performance and accuracy of the Urban Building models.
-It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructures to significantly advance computational research and applications.
+\begin{wrapfigure}{R}{.7\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{images/ub-devops.pdf}
+    \caption{KUB standard DevOps}
+    \label{fig:kub-devops}
+\end{wrapfigure}
+This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications. 
+It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{images/ub-devops.pdf}
-    \caption{Urban Building standard Devops}
-    \label{fig:ub-devops}
-\end{figure}
+Figure~\ref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.
+
+Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot large-scaleale cases.
+It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.
 
@@
     \caption{Urban Building HPC Ops workflow}
-    \label{fig:ub-hpcops}
+    \label{fig:kub-hpcops}
 \end{figure}
+
+\subsection{Benchmarking KUB}
+
+Finally, we display some results of our benchmarking activities~\cite{hidalgo2_d31_2024} for the KUB application regarding HPC performance.
+Running these experiments regularly is essential for maintaining the program's efficiency when developing the application and after machine updates.
+Hence, we have used the KUB application in the Strasbourg city center, with a square area of $4 \mathrm{km}^2$ (approximately 17K buildings).
+The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see Figure~\ref{fig:kub-hpcops}.
+Figure \ref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina.
+They present results for the total execution (end-to-end) of the KUB application and the simulation component.
+
+\begin{wrapfigure}{R}{0.6\textwidth}  % Adjust 'R' and width as needed
+  \centering
+  \begin{subfloat}[Scalability tests on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
+    \includegraphics[width=0.9\linewidth]{images/kub-scalability.png}
+    \label{fig:scalability}
+  }\end{subfloat}
+  \\
+  \begin{subfloat}[Execution breakdown on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
+    \includegraphics[width=0.9\linewidth]{images/kub-bencharkings-execution.png}
+    \label{fig:execution-breakdown}
+  }\end{subfloat}
+  \caption{Detailed performance metrics for scalability and execution on EuroHPC systems}
+  \label{fig:combined-metrics}
+\end{wrapfigure}
+The pipeline's simulation part scales almost linearly, which is expected as the buildings are not coupled together in the model currently used for the simulation.
+On the other hand, the total execution of the pilot's pipeline does not scale; as more nodes are employed, the performance degrades.
+
+To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in Figure \ref{fig:execution-breakdown}.
+This figure reports the portion of the total execution taken by:
+\begin{itemize}
+\item Pre-processing (Pre-proc): The time elapsed in initialization before entering the time loop of the simulation
+\item Simulation (Simulation): The cumulative time spent calculating the new solution at each time step
+\item Post-processing (Post-proc): The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
+\end{itemize}
+
+Pre-processing does not scale.
+However, it occupies only a small part of the total execution, and thus it is not performance-critical.
+On the other hand, as more nodes are employed and the time spent in the actual simulation is decreased, the post-processing stage dominates the execution.
+It becomes the main bottleneck, causing the previously observed performance degradation.
+This behavior is caused by the multiple files being written in parallel on the shared file system.
+More specifically, most of the writing time is spent in opening and closing files in parallel.
+We are investigating potential solutions, such as asynchronous writes, data caching, etc.
+Finally, as the project progresses, we expect the urban building models used in the simulation to become more complex, leading to an increase in the time occupied by the simulation part and, hence, to a reduction of the impact of post-processing on the total execution time of the pilot.
+
 \section{Conclusion}
-The CI/CD practices in Feel++ not only enhance the development lifecycle of the framework itself but also ensure that all dependent projects maintain high standards of reliability, security, and performance.
-The integration of Docker and Apptainer into the workflow enables wide-ranging deployment scenarios from personal computing environments to high-performance computing clusters.
 
-The integration of Feel++ within the HiDALGO2 project's Urban Building pilot through a sophisticated CI/CD framework supports the project's goal to enhance urban sustainability and air quality.
-The continuous development, testing, and deployment facilitated by this framework are vital for adapting to evolving urban challenges and computational needs.
+We are developing the computational Ktirio Urban Building(KUB) framework: assembling this very compelling application encompasses challenges in mathematics --- scalable modeling and simulation, large-scale watertight robust mesh generation, advanced analysis including data simulation --- and computer science --- scalable framework, software architecture, modern development, testing and packaging environment including standard DevOps and now HPCOps.---
+The overall programming, integration, delivery, and deployment environment is critical to develop such an application.
+To our knowledge, this is the first application that can be automatically benchmarked and executed on EuroHPC JU systems thanks to CI/CD or HPCOps.
+Moreover, the workflow from Feel++ to KUB provides a considerable gain in terms of development and testing time, automated  as much as possible, and enabling researchers and developers to focus their work better.
 
-CI/CD practices in HiDALGO2 are vital for advancing urban building simulations, supporting the EU's energy efficiency goals, and contributing to the reduction of greenhouse gas emissions in the urban sector.
+Our next steps include \textit{(i)} enabling tasks-based parallelism using the C++ framework Specx, see~\cite{cardosi_specx_2022}; \textit{(ii)} improving the modeling and simulation components, including mesh generation, handling of vegetation and urban furniture, and enabling view factors as well as providing a variety of configurable building energy models; \textit{(iii)} enhanced parallel strategies particularly in terms of partitioning and improved large scale I/O.
 
@@
 \subsubsection{\ackname} Funded by the  European  Union.
-This  work  has  received  funding  from  the European  High  Performance  Computing  Joint  Undertaking  (JU)  and  Poland, Germany,  Spain,  Hungary,  France,  Greece  under  grant  agreement  number: 101093457.
+This work has received funding from the European High-Performance Computing Joint Undertaking (EuroHPC JU)  and  Poland, Germany,  Spain,  Hungary,  France, and Greece under grant agreement number 101093457.
 This  publication  expresses  the  opinions  of  the  authors  and  not  necessarily those of the EuroHPC JU and Associated Countries which are not responsible for any use of the information contained in this publication
 
-Part of this work was also funded by \textit{(i)} the France 2030 NumPEx Exa-MA (ANR-22-EXNU-0002) project managed by the French National Research Agency (ANR), \textit{(ii)} AMIES the french agency for interaction between mathematics and enterprises and \textit{(iii)} CNRS through its prematuration programme.
+Part of this work was also funded by \textit{(i)} the France 2030 NumPEx Exa-MA (ANR-22-EXNU-0002) project managed by the French National Research Agency (ANR), \textit{(ii)} AMIES, the french agency for interaction between mathematics and enterprises and \textit{(iii)} CNRS through its prematuration programme.
 
-We acknowledge the EuroHPC Joint Undertaking for awarding this project access through  EuroHPC Development Access grants EHPC-DEV-2024D05-025 and EHPC-DEV-2023D08-047 to the EuroHPC supercomputers : \textit{(i)} Lumi, hosted by CSC (Finland) and the Lumi consortium, \textit{(ii)} Meluxina hosted by LuxProvide, Luxembourg, \textit{(iii)} Karolina hosted by IT4Innovations National Supercomputing Center, Czechia, \textit{(iv)} Discoverer osted by Sofia Tech Park, Bulgaria, \textit{(v)} Vega hosted by IZUM, Slovenia, and \textit{(vi)} Leonardo hosted by CINECA, Italy.
+We acknowledge the EuroHPC Joint Undertaking for awarding this project access through  EuroHPC Development Access grants EHPC-DEV-2024D05-025 and EHPC-DEV-2023D08-047 to the EuroHPC JU supercomputers : \textit{(i)} Kumi, hosted by CSC (Finland) and the Lumi consortium, \textit{(ii)} MeluXina hosted by LuxProvide, Luxembourg, \textit{(iii)} Karolina hosted by IT4Innovations National Supercomputing Center, Czechia, \textit{(iv)} Discoverer hosted by Sofia Tech Park, Bulgaria, \textit{(v)} Vega hosted by IZUM, Slovenia, and \textit{(vi)} Leonardo hosted by CINECA, Italy.
 

### 2024-07-03 compress.py
images compression script

@@ -1,0 +1,28 @@
+from PIL import Image
+import os
+
+
+def compress_images(directory, quality=85):
+    if not os.path.exists(directory):
+        print("Directory does not exist")
+        return
+
+    output_directory = os.path.join(directory, "compressed")
+    if not os.path.exists(output_directory):
+        os.makedirs(output_directory)
+
+    for filename in os.listdir(directory):
+        if filename.endswith(".jpg") or filename.endswith(".jpeg"):
+            img = Image.open(os.path.join(directory, filename))
+            img.save(os.path.join(output_directory, filename),
+                     "JPEG", quality=quality)
+        elif filename.endswith(".png"):
+            img = Image.open(os.path.join(directory, filename))
+            img.save(os.path.join(output_directory, filename),
+                     "PNG", optimize=True, quality=quality)
+
+    print(f"Images compressed and saved to {output_directory}")
+
+
+directory = 'images'
+compress_images(directory,quality=50)

### 2024-08-06 article.hid2-ub-cicd.ppam24.tex
setup article.template workflow
#1

--- 2024-05-28 hid2-urban-building-cicd.tex
@@
 
+\usepackage{ifthen}
+
+\newcommand{\imagedir}{./} % default directory
+% Shell command to check if a directory exists
+\immediate\write18{if [ -d "./images" ]; then echo "\\\\renewcommand{\\imagedir}{./images/}"; fi > checkdir.tex}
+
+% Input the output commands from the shell
+\InputIfFileExists{checkdir.tex}{}{}
+
 \begin{document}
+
 \title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
 \author{}
-\author{Luca Berti (formerly)\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
+\author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
 Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and 
-Abdoulaye Diallo \inst{1}\ \and
-Maryam Maslek Elayam \inst{1} \and
-Philippe Pinçon \inst{1} \and
+Abdoulaye Diallo \inst{1}\orcidID{0009-0006-8731-0547}\ \and
+Maryam Maslek Elayam \inst{1}\orcidID{0000-0003-0880-5180} \and
+Philippe Pinçon \inst{1}\orcidID{0009-0009-7724-3055 } \and
 Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
@@
 \email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
+
 \authorrunning{V. Chabannes et al.}
@@
 These simulations support detailed individual building-level analysis and extend to broader urban environments, influencing urban planning and policy-making.
+KUB is part of the platform Ktirio~\cite{cemosis_ktirio_2024} which itself is based on Feel++~\cite{christophe_prudhomme_feelppfeelpp_2024}.
 
@@
     \centering
-    \includegraphics[width=.9\textwidth]{images/kub-workflow.pdf}
+    \includegraphics[width=.9\textwidth]{\imagedir kub-workflow.pdf}
     \caption{Current Urban Building Workflow from localization to city energy simulation report.}
@@
 \subfloat[LOD-0: a building is represented by its bounding box]{%
-  \includegraphics[width=0.48\linewidth]{images/buildings-lod0.png}
+  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod0.png}
   \label{fig:building-lod0}
@@
 \subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
-  \includegraphics[width=0.48\linewidth]{images/buildings-lod1.png}
+  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod1.png}
   \label{fig:building-lod1}
@@
 \subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
-  \includegraphics[width=0.48\linewidth]{images/buildings-lod2.png}
+  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod2.png}
   \label{fig:building-lod2}
@@
 \subfloat[LOD-2: A zoom on the LOD-2 building.]{%
-  \includegraphics[width=0.48\linewidth]{images/buildings-lod2-zoom.png}
+  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod2-zoom.png}
   \label{fig:building-lod2-zoom}
@@
 \subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
-  \includegraphics[width=0.4\textwidth]{images/city-strasbourg-lod-0.png}
+  \includegraphics[width=0.4\textwidth]{\imagedir city-strasbourg-lod-0.png}
 }
@@
 \subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
-  \includegraphics[width=0.4\textwidth]{images/city-strasbourg-lod-1.png}
+  \includegraphics[width=0.4\textwidth]{\imagedir city-strasbourg-lod-1.png}
 }\\ % Ends the line for the first row of figures
@@
 \subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
-  \includegraphics[width=0.4\textwidth]{images/city-grenoble-terrain.png}
+  \includegraphics[width=0.4\textwidth]{\imagedir city-grenoble-terrain.png}
 }
@@
 CGAL, \cite{the_cgal_project_cgal_2024} is renowned for its robust and efficient algorithms, which are crucial for handling complex geometric data and generating high-quality meshes.
-This library is currently used for the following operations: boolean operation of polygon, multi-polygon repairs, mesh generation, mesh intersection, mesh adaptation, and building roof skeleton.
+This library is currently used for the following operations: boolean operation of polygon, multi-polygon repairs~\cite{loriot_polygon_2024}, mesh generation, mesh intersection, mesh adaptation, and building roof skeleton.
 
@@
 Following this, GIS data, including buildings and elevation information, is downloaded in parallel.
-Next, polygons are repaired to ensure they are suitable for mesh generation, with this process executed in parallel using MT.
+Next, polygons are repaired~\cite{loriot_polygon_2024} to ensure they are suitable for mesh generation, with this process executed in parallel using MT.
 The terrain mesh is then generated in parallel, employing CGAL's algorithms to ensure precision and efficiency.
@@
 \subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
-  \includegraphics[width=0.48\linewidth]{images/city-strasbourg-lod0-parts.png}
+  \includegraphics[width=0.48\linewidth]{\imagedir city-strasbourg-lod0-parts.png}
 }
@@
 \subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
-  \includegraphics[width=0.48\linewidth]{images/city-strasbourg-lod1-parts.png}
+  \includegraphics[width=0.48\linewidth]{\imagedir city-strasbourg-lod1-parts.png}
 }
 %\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
-%  \includegraphics[width=0.4\textwidth]{images/city-newyork-largescale.png}
+%  \includegraphics[width=0.4\textwidth]{\imagedir city-newyork-largescale.png}
 %}
@@
 \subfloat[View on whole 3D mesh\label{fig:city-ny-largescale-whole}]{%
-  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-whole.png}
+  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-whole.png}
 }
@@
 \subfloat[Zoom on Manhattan buildings\label{fig:city-ny-largescale-zoomB}]{%
-  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomB.png}
+  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomB.png}
 }\\
 \subfloat[Focus on Manhattan\label{fig:city-ny-largescale-zoomZ}]{%
-  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomA.png}
+  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomA.png}
 }
@@
 \subfloat[Central Park\label{fig:city-ny-largescale-zoomC}]{%
-  \includegraphics[width=0.45\textwidth]{images/city-newyork-largescale-zoomC.png}
+  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomC.png}
 }
@@
 \subfloat[LOD-0\label{fig:sm-building-east}]{%
-  \includegraphics[width=0.45\textwidth]{images/solar-masks-east-facing.png}
+  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-east-facing.png}
 }
@@
 \subfloat[LOD-1\label{fig:sm-whole-building}]{%
-  \includegraphics[width=0.45\textwidth]{images/solar-masks-whole-building.png}
+  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-whole-building.png}
 }\\
 \subfloat[LOD-1 Large scale\label{fig:sm-strasbourg}]{%
-  \includegraphics[width=0.45\textwidth]{images/solar-masks-strasbourg.png}
+  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-strasbourg.png}
 }
@@
 \subfloat[Heat transfer benchmark in 2D including view factors~\cite{van_eck_surface_2016}\label{fig:view-factor}]{%
-  \includegraphics[width=0.45\textwidth]{images/view-factors-benchmark.png}
+  \includegraphics[width=0.45\textwidth]{\imagedir view-factors-benchmark.png}
 }
@@
     \centering
-    \includegraphics[width=\textwidth]{images/feelpp-devops.png}
+    \includegraphics[width=\textwidth]{\imagedir feelpp-devops.png}
     \caption{CI/CD DevOps for Feel++}
@@
     \centering
-    \includegraphics[width=\textwidth]{images/feelpp-hpcops.png}
+    \includegraphics[width=\textwidth]{\imagedir feelpp-hpcops.png}
     \caption{CI/CD HPCOps for Feel++}
@@
     \centering
-    \includegraphics[width=\linewidth]{images/ub-devops.pdf}
+    \includegraphics[width=\linewidth]{\imagedir ub-devops.pdf}
     \caption{KUB standard DevOps}
@@
 
-Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot large-scaleale cases.
+Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases.
 It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.
@@
     \centering
-    \includegraphics[width=\textwidth]{images/ub-hpcops.pdf}
-    \caption{Urban Building HPC Ops workflow}
+    \includegraphics[width=\textwidth]{\imagedir ub-hpcops.pdf}
+    \caption{Ktirio Urban Building HPCOps workflow}
     \label{fig:kub-hpcops}
@@
   \begin{subfloat}[Scalability tests on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
-    \includegraphics[width=0.9\linewidth]{images/kub-scalability.png}
+    \includegraphics[width=0.9\linewidth]{\imagedir kub-scalability.png}
     \label{fig:scalability}
@@
   \begin{subfloat}[Execution breakdown on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
-    \includegraphics[width=0.9\linewidth]{images/kub-bencharkings-execution.png}
+    \includegraphics[width=0.9\linewidth]{\imagedir kub-bencharkings-execution.png}
     \label{fig:execution-breakdown}
@@
 
-Our next steps include \textit{(i)} enabling tasks-based parallelism using the C++ framework Specx, see~\cite{cardosi_specx_2022}; \textit{(ii)} improving the modeling and simulation components, including mesh generation, handling of vegetation and urban furniture, and enabling view factors as well as providing a variety of configurable building energy models; \textit{(iii)} enhanced parallel strategies particularly in terms of partitioning and improved large scale I/O.
+Our next steps include \textit{(i)} enabling tasks-based parallelism using the C++ framework Specx, see~\cite{cardosi_specx_2022}; \textit{(ii)} improving the modeling and simulation components, including mesh generation, handling of vegetation and urban furniture, and enabling view factors as well as providing a variety of configurable building energy models; \textit{(iii)} enhanced parallel strategies particularly in terms of partitioning and improved large scale I/O; and of course \textit{(iv)} pursue our benchmarking activities on EuroHPC JU supercomputers.
 

### 2024-08-06 compress.py

@@ -2,27 +2,37 @@ from PIL import Image
 import os
 
 
-def compress_images(directory, quality=85):
+def resize_and_compress_images(directory, max_width, max_height, quality=85):
     if not os.path.exists(directory):
         print("Directory does not exist")
         return
 
-    output_directory = os.path.join(directory, "compressed")
+    output_directory = os.path.join(directory, "processed")
     if not os.path.exists(output_directory):
         os.makedirs(output_directory)
 
     for filename in os.listdir(directory):
-        if filename.endswith(".jpg") or filename.endswith(".jpeg"):
-            img = Image.open(os.path.join(directory, filename))
-            img.save(os.path.join(output_directory, filename),
-                     "JPEG", quality=quality)
-        elif filename.endswith(".png"):
-            img = Image.open(os.path.join(directory, filename))
-            img.save(os.path.join(output_directory, filename),
-                     "PNG", optimize=True, quality=quality)
+        print(f"Processing {filename}")
+        if filename.endswith(".jpg") or filename.endswith(".jpeg") or filename.endswith(".png"):
+            img_path = os.path.join(directory, filename)
+            with Image.open(img_path) as img:
+                # Calculate the new size preserving the aspect ratio
+                img.thumbnail((max_width, max_height), Image.Resampling.LANCZOS)
+                # Save the processed image
+                if filename.endswith(".jpg") or filename.endswith(".jpeg"):
+                    img.save(os.path.join(output_directory, filename),
+                             "JPEG", quality=quality)
+                elif filename.endswith(".png"):
+                    img.save(os.path.join(output_directory, filename),
+                             "PNG", optimize=True, quality=quality)
 
-    print(f"Images compressed and saved to {output_directory}")
+    print(f"Images resized and compressed, saved to {output_directory}")
 
 
+# Set the directory path to your image folder
 directory = 'images'
-compress_images(directory,quality=50)
+# Set the maximum width and height for the images (in pixels)
+max_width = 595  # A4 width in points (1 point = 1/72 inch)
+max_height = 842  # A4 height in points
+
+resize_and_compress_images(directory, max_width, max_height)

### 2024-08-06 article.hid2-ub-cicd.ppam24.tex
use image naming
#1

@@
     \centering
-    \includegraphics[width=.9\textwidth]{\imagedir kub-workflow.pdf}
+    \includegraphics[width=.9\textwidth]{img-kub-workflow.pdf}
     \caption{Current Urban Building Workflow from localization to city energy simulation report.}
@@
 \subfloat[LOD-0: a building is represented by its bounding box]{%
-  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod0.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod0.png}
   \label{fig:building-lod0}
@@
 \subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
-  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod1.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod1.png}
   \label{fig:building-lod1}
@@
 \subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
-  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod2.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2.png}
   \label{fig:building-lod2}
@@
 \subfloat[LOD-2: A zoom on the LOD-2 building.]{%
-  \includegraphics[width=0.48\linewidth]{\imagedir buildings-lod2-zoom.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2-zoom.png}
   \label{fig:building-lod2-zoom}
@@
 \subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
-  \includegraphics[width=0.4\textwidth]{\imagedir city-strasbourg-lod-0.png}
+  \includegraphics[width=0.4\textwidth]{img-compressed-city-strasbourg-lod-0.png}
 }
@@
 \subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
-  \includegraphics[width=0.4\textwidth]{\imagedir city-strasbourg-lod-1.png}
+  \includegraphics[width=0.4\textwidth]{img-compressed-city-strasbourg-lod-1.png}
 }\\ % Ends the line for the first row of figures
@@
 \subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
-  \includegraphics[width=0.4\textwidth]{\imagedir city-grenoble-terrain.png}
+  \includegraphics[width=0.4\textwidth]{img-compressed-city-grenoble-terrain.png}
 }
@@
 \subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
-  \includegraphics[width=0.48\linewidth]{\imagedir city-strasbourg-lod0-parts.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod0-parts.png}
 }
@@
 \subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
-  \includegraphics[width=0.48\linewidth]{\imagedir city-strasbourg-lod1-parts.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod1-parts.png}
 }
 %\subfloat[Partitioning Case 3: Large scale\label{fig:city-ny-largescale}]{%
-%  \includegraphics[width=0.4\textwidth]{\imagedir city-newyork-largescale.png}
+%  \includegraphics[width=0.4\textwidth]{img-compressed-city-newyork-largescale.png}
 %}
@@
 \subfloat[View on whole 3D mesh\label{fig:city-ny-largescale-whole}]{%
-  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-whole.png}
+  \includegraphics[width=0.45\textwidth]{img-compressed-city-newyork-largescale-whole.png}
 }
@@
 \subfloat[Zoom on Manhattan buildings\label{fig:city-ny-largescale-zoomB}]{%
-  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomB.png}
+  \includegraphics[width=0.45\textwidth]{img-compressed-city-newyork-largescale-zoomB.png}
 }\\
 \subfloat[Focus on Manhattan\label{fig:city-ny-largescale-zoomZ}]{%
-  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomA.png}
+  \includegraphics[width=0.45\textwidth]{img-compressed-city-newyork-largescale-zoomA.png}
 }
@@
 \subfloat[Central Park\label{fig:city-ny-largescale-zoomC}]{%
-  \includegraphics[width=0.45\textwidth]{\imagedir city-newyork-largescale-zoomC.png}
+  \includegraphics[width=0.45\textwidth]{img-compressed-city-newyork-largescale-zoomC.png}
 }
@@
 \subfloat[LOD-0\label{fig:sm-building-east}]{%
-  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-east-facing.png}
+  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-east-facing.png}
 }
@@
 \subfloat[LOD-1\label{fig:sm-whole-building}]{%
-  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-whole-building.png}
+  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-whole-building.png}
 }\\
 \subfloat[LOD-1 Large scale\label{fig:sm-strasbourg}]{%
-  \includegraphics[width=0.45\textwidth]{\imagedir solar-masks-strasbourg.png}
+  \includegraphics[width=0.45\textwidth]{img-compressed-solar-masks-strasbourg.png}
 }
@@
 \subfloat[Heat transfer benchmark in 2D including view factors~\cite{van_eck_surface_2016}\label{fig:view-factor}]{%
-  \includegraphics[width=0.45\textwidth]{\imagedir view-factors-benchmark.png}
+  \includegraphics[width=0.45\textwidth]{img-compressed-view-factors-benchmark.png}
 }
@@
     \centering
-    \includegraphics[width=\textwidth]{\imagedir feelpp-devops.png}
+    \includegraphics[width=\textwidth]{img-compressed-feelpp-devops.png}
     \caption{CI/CD DevOps for Feel++}
@@
     \centering
-    \includegraphics[width=\textwidth]{\imagedir feelpp-hpcops.png}
+    \includegraphics[width=\textwidth]{img-compressed-feelpp-hpcops.png}
     \caption{CI/CD HPCOps for Feel++}
@@
     \centering
-    \includegraphics[width=\linewidth]{\imagedir ub-devops.pdf}
+    \includegraphics[width=\linewidth]{img-ub-devops.pdf}
     \caption{KUB standard DevOps}
@@
     \centering
-    \includegraphics[width=\textwidth]{\imagedir ub-hpcops.pdf}
+    \includegraphics[width=\textwidth]{img-ub-hpcops.pdf}
     \caption{Ktirio Urban Building HPCOps workflow}
@@
   \begin{subfloat}[Scalability tests on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
-    \includegraphics[width=0.9\linewidth]{\imagedir kub-scalability.png}
+    \includegraphics[width=0.9\linewidth]{img-compressed-kub-scalability.png}
     \label{fig:scalability}
@@
   \begin{subfloat}[Execution breakdown on a few EuroHPC systems from 1 to 32 nodes of 128 cores per node]{
-    \includegraphics[width=0.9\linewidth]{\imagedir kub-bencharkings-execution.png}
+    \includegraphics[width=0.9\linewidth]{img-compressed-kub-bencharkings-execution.png}
     \label{fig:execution-breakdown}

### 2024-08-07 article.hid2-ub-cicd.ppam24.tex
fix tex
#1
up format
#1

@@
 \usepackage{hyperref}
-\hypersetup{
-    colorlinks=true,      % Enable colored links
-    linkcolor=darkred,    % Color for internal links
-    filecolor=darkgreen,  % Color for file links
-    urlcolor=darkblue,    % Color for external URLs
-    citecolor=darkmagenta % Color for citations
+
+\IfFileExists{.git/gitHeadInfo.gin}{
+    \usepackage[pcount,grumpy,mark,markifdirty]{gitinfo2}
+}{%
+    \usepackage[local,pcount,grumpy,mark,markifdirty]{gitinfo2}
 }
 
-\usepackage{ifthen}
-
-\newcommand{\imagedir}{./} % default directory
-% Shell command to check if a directory exists
-\immediate\write18{if [ -d "./images" ]; then echo "\\\\renewcommand{\\imagedir}{./images/}"; fi > checkdir.tex}
-
-% Input the output commands from the shell
-\InputIfFileExists{checkdir.tex}{}{}
-
-\begin{document}
+%% By default, llncs tocdepth value is 0, so only chapters and parts are shown in the ToC, but no sections and deeper levels of structure.
+%% If \setcounter{tocdepth}{1} is used, the sections show up in the ToC.
+%% I suggest to use \usepackage{tocbibind} in order to add the LoF and LoT in the ToC as well, if the ToC should not be listed itself, use \usepackage[nottoc]{tocbibind} instead.
+%% As long as no figure or table environments with \caption commands or explicit \addcontentsline{lof}{...}{...} etc. are used, the LoF and LoT are empty of course.
+\setcounter{secnumdepth}{4}
+\setcounter{tocdepth}{1}
+\usepackage[section,notlof,notlot,nottoc,]{tocbibind}
 
 \title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
-\author{}
 \author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
@@
 \email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
+\date{\gitReln\  \gitAuthorDate\ (\gitAbbrevHash)}
+\authorrunning{V. Chabannes et al.}
 
-\authorrunning{V. Chabannes et al.}
+% Define custom color
+\definecolor{CustomBlue}{rgb}{0.25, 0.41, 0.88} % RoyalBlue
+% Set up hyperref with the custom citecolor
+\hypersetup{
+    pdftitle={\@title},
+    pdfauthor={\@author},
+    pdfsubject={\@subject},
+    pdfkeywords={HPC, HPCOps, Urban building, City Energy Simulation},
+    bookmarksnumbered,bookmarksopen,linktocpage,
+    colorlinks=true,
+    citecolor=CustomBlue,
+    linkcolor=CustomBlue,
+    urlcolor=blue
+}
+
+\begin{document}
 
@@
 
+\tableofcontents
+\listoffigures
+%\listoftables
+
 \section{Introduction}
+\label{sec:introduction}
+
 The building sector accounts for approximately 40\% of final energy consumption and 36\% of greenhouse gas emissions within the European Union~\cite{european_commision_energy_2020}.
@@
 \section{Ktirio Urban Building Workflow}
+\label{sec:kub-workflow}
 
@@
 \subsection{Data Handling and Simulation Process}
+\label{sec:data-handling}
+
 The workflow begins with collecting and preparing GIS and weather data, transforming it into a format usable for simulations.
@@
 \subsection{Final Analysis and Urban Scale Energy Evaluation}
+\label{sec:final-analysis}
+
 The final step involves the UBEM Simulator, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale.
@@
 \section{Overview of Urban Building Modeling and Simulation}
+\label{sec:urban-building}
 

### 2024-08-28 article.hid2-ub-cicd.ppam24.tex
update update KUB CICD images #4
update KUB workflow image #5
Enhancing paper text and images

@@
 \usepackage{graphicx} % for including images
+\usepackage{float}
 \usepackage[T1]{fontenc}
@@
 %% As long as no figure or table environments with \caption commands or explicit \addcontentsline{lof}{...}{...} etc. are used, the LoF and LoT are empty of course.
-\setcounter{secnumdepth}{4}
+\setcounter{secnumdepth}{3}
 \setcounter{tocdepth}{1}
@@
 
-\tableofcontents
-\listoffigures
+%\tableofcontents
+%\listoffigures
 %\listoftables
@@
 
-Building on the foundations of the Feel++ framework, our project introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers.
-This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying these simulations at scale.
+Building on the foundations of the Feel++ framework, this paper introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers.
+This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying and running these simulations at multiple scales.
 Integrating EuroHPC JU infrastructures represents a significant advancement in making high-performance computing resources accessible for urban simulation studies.
 
-Thanks to synergies with another CoE HiDALGO2 pilot, the KUB project is set to integrate building simulations with urban air pollution (UAP) models to comprehensively assess the environmental impact of building stocks soon.
-This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness to environmental conditions.
+Thanks to synergies with other CoE HiDALGO2 pilots, the KUB project is set to integrate building simulations with Urban Air Pollution (UAP) pilot models to comprehensively assess the environmental impact of building stocks soon.
+This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.
 
-Implementing these objectives will facilitate more informed urban planning decisions, support policy development for energy efficiency, and contribute to reducing urban greenhouse gas emissions.
-The project also focuses on enhancing the interaction between different environmental models to provide a holistic view of urban ecosystems.
+Implementing the proposed KUB workflow will facilitate more informed urban planning decisions, support policy development for energy efficiency, and contribute to reducing urban greenhouse gas emissions.
+The project also focuses on enhancing the interactions between different environmental models to provide a holistic view of urban ecosystems.
 
-The paper is organized as follows: Section 2 discusses KUB's current workflow, Section 3 provides an overview of some modeling and simulation components, and finally, Section 4 delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.
+This paper is organized as follows: Section~\ref{sec:kub-workflow} discusses KUB's current workflow, Section~\ref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, Section~\ref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.
 
@@
 \label{sec:kub-workflow}
+
+The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments.
+The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.
 
@@
 
-The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments.
-The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with urban air pollution (UAP) models.
-
 \subsection{Data Handling and Simulation Process}
@@
 
-The workflow begins with collecting and preparing GIS and weather data, transforming it into a format usable for simulations.
-This data is then partitioned for scalable processing and converted into Modelica and Feel++\cite{christophe_prudhomme_feelppfeelpp_2024} compatible formats through the UBEM Generator.
+The workflow begins with collecting and preparing GIS and weather data and transforming them into a usable format for simulations.
+The transformed data are then partitioned for scalable processing and converted into Modelica and Feel++~\cite{christophe_prudhomme_feelppfeelpp_2024} compatible formats through the \textit{UBEM Generator}.
 
-This processed data is employed to simulate energy consumption and indoor environmental quality using the Urban Building Energy Model (UBEM).
-The simulation focuses on radiative heat transfer, enhancing the accuracy of the energy models.
-It also computes view factors and shading masks, assessing how buildings affect each other's exposure to natural light and heat, influencing the urban heat island effect and overall building energy needs.
+This processed data is employed to simulate energy consumption and indoor environmental quality using the \textit{Urban Building Energy Model (UBEM)}.
+The simulation focuses on a \textit{radiative heat transfer model}, enabling enhancement of the accuracy of the energy models.
+It also computes \textit{view factors} and \textit{shading masks}, assessing how buildings affect each other's exposure to natural light and heat and overall building energy needs, and the outdoor environment by influencing the urban heat island effect.
 
-The building simulation outputs are then optionally fed into the urban air pollution (UAP) simulator to evaluate the impact of building emissions on urban air quality.
-A feedback loop refines the building simulation scenarios based on intermediate outputs from the UAP simulator, ensuring that the models accurately reflect the complex interdependencies between urban building energy usage and urban air quality.
+The building simulation outputs are then optionally fed into the \textit{Urban Air Pollution (UAP) simulator} to evaluate the impact of building emissions on urban air quality.
+A feedback loop refines the building simulation scenarios based on intermediate outputs from the \textit{UAP simulator}, ensuring that the models accurately reflect the complex interdependencies between urban building energy usage and urban air quality.
 
@@
 
-The final step involves the UBEM Simulator, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale.
+The final step involves the \textit{UBEM Simulator}, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale.
 This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.
 
-This streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting our application's broader objectives of improving urban living conditions and environmental impact.
+The described streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting our application's broader objectives of improving urban living conditions and environmental impact.
 
@@
 
-We now provide an overview of the geometrical and physical modeling and simulation components of the Urban building application.
+This section provides an overview of the geometrical and physical modeling and simulation components of our urban building application.
 
@@
 The geometric reconstruction of urban environments within KUB involves a sophisticated approach to creating multi-fidelity representations of buildings, terrain, vegetation, roads, and other urban elements.
-This section outlines the methodologies employed and the various levels of detail (LOD) used in the models.
+This section outlines the methodologies employed and the various Levels of Detail (LOD) used in the different models of kUB workflow.
 
@@
 
-\begin{wrapfigure}{R}{0.6\textwidth} % 'R' or 'L' for right or left, and width
+\begin{figure}[ht]%{R}{1\textwidth} % 'R' or 'L' for right or left, and width
 \centering
@@
 \label{fig:buildings}
-\end{wrapfigure}
-In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
+\end{figure}
+
+In the figure~\ref{fig:buildings}, we illustrate the different levels of details.
+Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
 Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height.
@@
 Following this, the elevation at each node is evaluated.
-However, this method provides a very refined mesh, even when the terrain is flat. For this reason, we plan to apply the following procedure:
+However, this method provides a very refined mesh, even when the terrain is flat.
+For this reason, we plan to apply a mesh adaptation technique to reduce mesh density where feasible, using the following processing:
 \begin{itemize}
@@
 \subsubsection{Vegetation Modeling}
-Including vegetation (trees) in this geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas has a significant impact. 
+Including vegetation (trees) in our geometric model is essential for the simulation of buildings.
+The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  .
 We use the OpenStreetMap database to obtain the metadata associated with the vegetation.
@@
 These geometric entities are parameterized so that a transformation can be applied.
-\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best we can (by searching around).
+\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
 \item Creating a tree geometric model using an affine transformation of the reference tree model.
@@
 \subsubsection{Integration of all urban geometric components}
-This process involves creating a conforming mesh that includes both components (buildings, terrains, vegetation).
+This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation).
 Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
 The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
-\textit{(iii)} Apply the intersection of vegetation with buildings and terrain.
-And \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).
+\textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).
 
@@
 
-\begin{wrapfigure}{R}{0.6\textwidth}
+%\begin{wrapfigure}{R}{0.6\textwidth}
+\begin{figure}[ht]
 \centering
-\subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
-  \includegraphics[width=0.4\textwidth]{img-compressed-city-strasbourg-lod-0.png}
+\subfloat[Representation of Strasbourg center with LOD-0\label{fig:city-strasbourg-lod0}]{%
+  \includegraphics[width=0.48\textwidth]{img-compressed-city-strasbourg-lod-0.png}
 }
 \hfill % Ensures that the images are placed side by side
-\subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
-  \includegraphics[width=0.4\textwidth]{img-compressed-city-strasbourg-lod-1.png}
+\subfloat[Representation of Strasbourg center with LOD-1\label{fig:city-strasbourg-lod1}]{%
+  \includegraphics[width=0.48\textwidth]{img-compressed-city-strasbourg-lod-1.png}
 }\\ % Ends the line for the first row of figures
 
-\subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
-  \includegraphics[width=0.4\textwidth]{img-compressed-city-grenoble-terrain.png}
+\subfloat[Representation of Grenoble LOD-1 terrain elevation\label{fig:city-grenoble-terrain}]{%
+  \includegraphics[width=0.48\textwidth]{img-compressed-city-grenoble-terrain.png}
 }
 
-\caption{Various representations of cities and terrain.
-Representation of Strasbourg center with LOD-0 in the top left panel and LOD-1 in the top right.
-LOD-1 city (Grenoble, France) representation with terrain elevation.}
+\caption{Various representations of cities and terrains}
 \label{fig:city-strasbourg}
-\end{wrapfigure}
+\vspace{-0.5cm}
+\end{figure}
+%\end{wrapfigure}
 
@@
 
-All the features described above are not yet operational in our framework.
+Features using CGAL algorithms are not yet operational in our framework.
 We can reconstruct a geometric model of an urban area whose location is arbitrary so that the user can select an area anywhere in the world.
-The final mesh comprises all buildings LOD-0 or LOD-1 and the terrain with elevation.
+The final mesh comprises all buildings in LOD-0 or LOD-1 and the terrain with elevation.
 The integration of all the urban components is currently being investigated.
@@
 This scale-up involves utilizing MPI to manage distributed computing resources effectively.
-To achieve this, partitions of tiles with overlapping regions are created to ensure complete and accurate building descriptions without requiring extensive MPI communications.
+To achieve the latter objective, partitions of tiles with overlapping regions are created to ensure complete and accurate building descriptions without requiring extensive MPI communications.
 Furthermore, each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.
@@
 \subsubsection{Partitioning Strategies Depending on Simulation Use Cases}
+
 Data partitioning is a crucial stage in the deployment of the supercomputer simulator.
@@
 
-\begin{figure}[htbp]
+\begin{figure}[ht]
 \centering
@@
 \section{CI/CD Framework for the Urban Building Pilot}
+\label{sec:cicd-framework}
+
 The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment.

### 2024-08-30 article.hid2-ub-cicd.ppam24.tex
Added equations to the paper

@@
 To do this, we built on two main tools: Feel++ and Modelica. 
+\subsubsection{Governing equation of the simulation}
+The physical model of the city is based on a multizone model.
+One zone is allocated per building floor.
+The energy balance for each zone is calculated taking into account energy exchanges with adjacents zone and the environment.
+The energy balance is written according to the first law of thermodynamics, in an isolated system the sum of all form of energy is constant.
+\begin{equation}
+    C\cdot \frac{dT}{dt}=\phi_{HVAC}+\phi_{gain}-\phi_{losses}
+\end{equation}
+To give an overview of the equation's term we will give a brief summary.
+\begin{itemize}
+  \item $C\cdot \frac{dT}{dt}$ : thermal inertia of the construction. 
+  \item $\phi_{HVAC}$ : energy output of the Heating Ventilation and Air Conditioning systems. 
+  \item $\phi_{gain}$ : often reffered to as free energy gain, depends on solar gains, and building's occupation.
+  \item $\phi_{losses}$ : energy losses throught wall/roof/slab, and air exchange.
+\end{itemize}
+
+\textbf{HVAC heatflow}
+
+As for now we fixed the heating system as an ideal heat source.
+Meaning the heatflow adapt to maintain a set temperature inside the building.
+
+\textbf{Heat gain}
+
+The heatflow gain is composed of solar gain and internal gain.
+
+\textbf{Internal heat gain}
+
+The internal heat gain are a function of human presence inside of a building :
+\begin{equation}
+  \phi_{int}=Met\cdot d_{inhabitant}(timetable)
+\end{equation}
+
+\textbf{Solar heat gain}
+
+The solar heat gain can be written as a sum of the different solar fluxes : direct, diffuse and reflected.
+\begin{equation}
+  \phi_{swl}=\alpha\cdot S\cdot(E_{dir}+E_{diff}+E_{ref})\cdot 
+\end{equation}
+
+The direct solar radiation is written as such :
+\begin{equation}
+  E_{dir}=F_{dir}\cdot cos(I)
+\end{equation}
+
+$F_{dir}$ is a function of the horizontal solar radiation measured by a weather station.
+\begin{equation}
+  F_{dir}=\frac{F_{dir,Hz}}{sin(H_s)}
+\end{equation}
+\begin{equation}
+  cos(I)=cos(H_s)\cdot sin(\beta)\cdot cos(A_{zs}-A_{z})+sin(H_s)\cdot cos(\beta)
+\end{equation}
+
+The diffuse solar radiation is written as such :
+\begin{equation}
+  E_{dif}=F_{dif,Hz}+\frac{1+cos(\beta)}{2}
+\end{equation}
+
+The reflected solar radiation is written as such :
+\begin{equation}
+  E_{ref}=[F_{dir,Hz}+F_{dif,Hz}]\cdot \frac{1+cos(\beta)}{2}\cdot albedo
+\end{equation}
+
+\textbf{Conduction losses}
+
+\underline {I need to dive in the modelica model to extract the equation for the convection losses}
+
+In this scenario we do not compute the thermal brige for the models.
+\begin{equation}
+  \phi_{wall}=\sum_{j} U_j\cdot S_j\cdot \Delta T
+\end{equation}
+
+\textbf{Radiation losses}
+
+\underline{I'm not sure the Radiation exchange within a zone are taken into account, i need to check but i saw somewhere that} 
+\underline{for LOD0-1 only the big wave length heatflow with external wall surface->sky are taken into account}
+\begin{equation}
+  \phi_{net,i}=\sum_{j\not=i}\frac{J_i-J_j}{\frac{1}{S_i\cdot F_{ij}}}
+\end{equation}
+\begin{equation}
+  \phi_{net,i}=S_i\cdot \frac{\epsilon_i}{1-\epsilon_i}\cdot (\sigma\cdot T_i^4-J_i)
+\end{equation}
+
+\textbf{Air change}
+\begin{equation}
+  \phi_{air}=0,34\cdot Q_v\cdot \Delta T
+\end{equation}
 
@@
 
+\textbf{Nomenclature}
+
+$\alpha$ : Absorption of a material.
+
+$\beta$ : Angle of inclination of the wall to the horizontal.
+
+$\Delta T$ : Temperature difference. [K]
+
+$\epsilon$ : Emissivity of the surface.
+
+$\phi_{air}$ : Air heatflow. [W]
+
+$\phi_{net}$ : radiative heatflow. [W]
+
+$\phi_{swl}$ : Solar heatflow from short wave lenght. [W]
+
+$\phi_{wall}$ : Heatflow through a wall. [W]
+
+$albedo$ : Reflective properties of the material.
+
+$A_z$ : Azimuth of the surface.
+
+$A_{zs}$ : Azimuth of the sun.
+
+$C$ : Heatcapacity of the zone. [W$\cdot K^{-1}$]
+
+$d_{inhabitant}(timetable)$ : density of inhabitant in a building as a function of a timetable set for the building type.
+
+$E_{dir}$ : Direct solar heatflow. [W$\cdot m^{-2}$]
+
+$E_{dif}$ : Diffuse solar heatflow. [W$\cdot m^{-2}$]
+
+$E_{ref}$ : Reflected solar heatflow. [W$\cdot m^{-2}$]
+
+$F_{dir}$ : Direct solar radiation. [W$\cdot m^{-2}$]
+
+$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data. [W$\cdot m^{-2}$]
+
+$F_{ij}$ : View factor between a $surface_{(i)}$ and a $surface_{(j)}$.
+
+$H_s$ : Angular height of the sun.
+
+$J$ : Radiosity of a surface. [$W\cdot m^{-2}$]
+
+$Met$ : Metabolic rate [W]
+
+$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity [$W\cdot K^{-1}$]
+
+$S$ : Surface. [$m^2$]
+
+$U_j$ : Conductance of a $wall_j$. [$W\cdot m^{-2}\cdot K^{-1}$]
+
 \bibliographystyle{splncs04}

### 2024-09-04 article.hid2-ub-cicd.ppam24.tex
Added some explaination to the equations #6

--- 2024-08-28 article.hid2-ub-cicd.ppam24.tex
@@
 To do this, we built on two main tools: Feel++ and Modelica. 
+\subsubsection{Governing equation of the simulation}
+The physical model of the city is based on a multizone model.
+One zone is allocated per building floor.
+The energy balance for each zone is calculated taking into account energy exchanges with adjacents zone and the environment.
+The energy balance is written according to the first law of thermodynamics, in an isolated system the sum of all form of energy is constant.
+\begin{equation}
+    C\cdot \frac{dT}{dt}=\phi_{HVAC}+\phi_{gain}-\phi_{losses}
+\end{equation}
+To give an overview of the equation's term we will give a brief summary.
+\begin{itemize}
+  \item $C\cdot \frac{dT}{dt}$ : represents the thermal inertia of the construction. 
+  This term quantifies how the temperature of the zone changes over time due to its thermal mass. 
+  \begin{itemize}
+    \item $C$ :This is a measure of how much heat a material can store and release. 
+    It combines the heat capacity of the construction (how much energy is required to change the temperature) with the rate of temperature change.
+    \item $\frac{dT}{dt}$ : This is the rate of change of temperature with respect to time. 
+    A higher thermal inertia means the construction will have a slower temperature change in response to energy inputs and losses, effectively buffering temperature fluctuations.
+  \end{itemize}
+  \item $\phi_{HVAC}$ : This term represents the energy input from the Heating, Ventilation, and Air Conditioning (HVAC) systems. 
+  It includes energy added to the zone to maintain desired temperature levels.
+  \item $\phi_{gain}$ : Referred to as free energy gain, this term includes solar gains (heat from sunlight) and internal gains (heat generated by occupants and equipment).
+  \item $\phi_{losses}$ : Represents the energy lost through walls, roofs, floors, and air exchanges with the environment.
+\end{itemize}
+
+\textbf{HVAC heatflow}
+
+In this model, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.
+
+\textbf{Heat gain}
+
+Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.\\
+
+\textbf{Internal heat gain}
+
+Captures the heat produced by occupants inside the building. 
+It is modeled as a function of metabolic rate $Met$ and the number of inhabitants, which varies according to a timetable.
+\begin{equation}
+  \phi_{int}=Met\cdot d_{inhabitant}(timetable)
+\end{equation}
+
+\textbf{Solar heat gain}
+
+Calculate the total solar heat gain, which includes contributions from direct, diffuse, and reflected solar radiation. 
+In regard with the building’s surface characteristics and shading coefficient.
+\begin{equation}
+  \phi_{solar}=\alpha\cdot S\cdot(E_{dir}+E_{diff}+E_{ref})\cdot S_C
+\end{equation}
+Direct solar radiation, where the horizontal solar radiation is adjusted for the angle of incidence of the sunlight.
+\begin{equation}
+  E_{dir}=F_{dir}\cdot cos(I)
+\end{equation}
+$F_{dir}$ is the direct solar radiation it is a function of the horizontal solar radiation measured by a weather station.
+\begin{equation}
+  F_{dir}=\frac{F_{dir,Hz}}{sin(H_s)}
+\end{equation}
+$Cos (I)$ : calculates the cosine of the angle of incidence of sunlight, incorporating the sun's altitude and azimuth angles as well as the building's tilt angle
+\begin{equation}
+  cos(I)=cos(H_s)\cdot sin(\beta)\cdot cos(A_{zs}-A_{z})+sin(H_s)\cdot cos(\beta)
+\end{equation}
+Diffuse solar radiation, which includes contributions from the sky dome and is adjusted for the building's tilt.
+\begin{equation}
+  E_{dif}=F_{dif,Hz}+\frac{1+cos(\beta)}{2}
+\end{equation}
+Reflected solar radiation, calculated using the total horizontal radiation and the environnement's albedo
+\begin{equation}
+  E_{ref}=[F_{dir,Hz}+F_{dif,Hz}]\cdot \frac{1+cos(\beta)}{2}\cdot albedo
+\end{equation}
+
+\textbf{Conduction losses}
+
+Energy loss through walls is computed by summing the losses across all wall segments.
+It depends on the heat transfer coefficient , the wall area , and the temperature difference between the indoor and outdoor environments.
+
+In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depends of specifics informations on the building's envelope that we do not have.
+\begin{equation}
+  \phi_{wall}=\sum_{j} U_j\cdot S_j\cdot \Delta T
+\end{equation}
+
+\textbf{Convection losses}
+
+The convection losses are computed differently regarding the surface of the wall they are applied to.
+
+On the interior surface we apply a constant :
+\begin{equation}
+  \phi_{conv,int}=\alpha_{conv} \cdot \Delta T
+\end{equation}
+
+On the exterior surface we used a forced convection model :
+\begin{equation}
+  \phi_{conv,int}=(1,8+4,8\cdot v_{air}) \cdot \Delta T
+\end{equation}
+
+Radiation losses describe the heat energy lost due to thermal radiation. 
+This is an important factor in buildings as it impacts both energy efficiency and thermal comfort.
+We defferenciate between the exterior of the wall that exange with the sky and the interior where the walls exchange between each other.
+
+Exterior radiation exchange. 
+\begin{equation}
+  \phi_{net,sky} = \varepsilon_i \cdot \sigma \cdot (T_i^4-T_{sky})
+\end{equation}
+Interior radiation exchange.
+\begin{equation}
+  J[i] = \varepsilon_i \cdot \sigma \cdot T_i^4 + (1.0 - \varepsilon_i) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]
+\end{equation}
+Radiative heat exchange $J[i]$ :
+\begin{itemize}
+  \item $\varepsilon_i \cdot \sigma \cdot T_i^4$ : 
+  This term calculates the heat radiated by the surface i. 
+  $\epsilon$ is a measure of how effectively the surface emmit radiation.
+  The $T^4$ refelect the fact that radiative heatloss increase rapidly with temperature.
+  \item $(1.0 - \varepsilon_i) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$ : 
+  This term accounts for the heat absorbed from other surfaces $j$ within the zone.
+  The factor $(1.0 - \varepsilon_i)$ adjust for the fraction of incoming radiation that is not emitted by surface $i$.
+\end{itemize}
+\begin{equation}
+  \phi_{net,int}[i] = \frac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot (\sigma \cdot T_i^4 - J[i])
+\end{equation}
+Net radiation flow $Q_{flow}[i]$ :
+\begin{itemize}
+  \item $\frac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot (\sigma \cdot T_i^4 - J[i])$ :
+  This term calculate the net heat flow due to radiation for surface $i$.
+  It considers the difference between the heat emmited by the surface and the heat received from other surfaces.
+  The ratio $\frac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
+\end{itemize}
+
+\textbf{Air change}
+
+Represents the energy loss due to air exchange between the zone and the exterior.
+\begin{equation}
+  \phi_{air}=0,34\cdot Q_v\cdot \Delta T
+\end{equation}
 
@@
 
+\textbf{Nomenclature}\\
+$\alpha$ : Absorption of a material.\hfill[-]\\
+$\alpha_{conv}$ : heat conductance of convection\hfill[-]\\
+$\beta$ : Angle of inclination of the wall to the horizontal.\hfill[-]\\
+$\Delta T$ : Temperature difference.\hfill[K]\\
+$\epsilon$ : Emissivity of the surface.\hfill[-]\\
+$\phi_{air}$ : Air heatflow.\hfill[W]\\
+$\phi_{net}$ : radiative heatflow.\hfill[W]\\
+$\phi_{solar}$ : Solar heatflow from short wave lenght.\hfill[W]\\
+$\phi_{wall}$ : Heatflow through a wall.\hfill[W]\\
+$\sigma$ : Stefan-Boltzmann constant $5,67\cdot10^{-8}$\hfill[W$\cdot m^{-2}\cdot K^{-4}$]\\
+$albedo$ : Reflective properties of the material.\hfill[-]\\
+$A_z$ : Azimuth of the surface.\hfill[-]\\
+$A_{zs}$ : Azimuth of the sun.\hfill[-]\\
+$C$ : Heatcapacity of the zone.\hfill[W$\cdot K^{-1}$]\\
+$d_{inhabitant}(timetable)$ : density of inhabitant in a building as a function of a timetable set for the building type.\hfill[-]\\
+$E_{dir}$ : Direct solar heatflow.\hfill[W$\cdot m^{-2}$]\\
+$E_{dif}$ : Diffuse solar heatflow.\hfill[W$\cdot m^{-2}$]\\
+$E_{ref}$ : Reflected solar heatflow.\hfill[W$\cdot m^{-2}$]\\
+$F_{dir}$ : Direct solar radiation.\hfill[W$\cdot m^{-2}$]\\
+$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data.\hfill[W$\cdot m^{-2}$]\\
+$F_{ij}$ : View factor between a $surface_{(i)}$ and a $surface_{(j)}$.\hfill[-]\\
+$H_s$ : Angular height of the sun. \hfill[-]\\
+$J$ : Radiosity of a surface.\hfill[$W\cdot m^{-2}$]\\
+$Met$ : Metabolic rate\hfill[W]\\
+$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity
+
+\raggedleft{[$W\cdot K^{-1}$]}\\
+$S$ : Surface.\hfill[$m^2$]\\
+$S_C$ : Shading coefficient $\in$[0,1]\hfill[-]\\
+$U_j$ : Conductance of a $wall_j$.\hfill[$W\cdot m^{-2}\cdot K^{-1}$]\\
+$V_{air}$ : Wind speed \hfill[m$\cdot s^{-1}$]
+
 \bibliographystyle{splncs04}

### 2024-09-05 article.hid2-ub-cicd.ppam24.tex
Corrections #6

@@
 One zone is allocated per building floor.
-The energy balance for each zone is calculated taking into account energy exchanges with adjacents zone and the environment.
-The energy balance is written according to the first law of thermodynamics, in an isolated system the sum of all form of energy is constant.
+The energy balance for each zone is calculated taking into account energy exchanges with adjacent zones and the environment.
+The energy balance is written according to the first law of thermodynamics : in an isolated system, the sum of all forms of energy is constant.
 \begin{equation}
@@
     \item $\frac{dT}{dt}$ : This is the rate of change of temperature with respect to time. 
-    A higher thermal inertia means the construction will have a slower temperature change in response to energy inputs and losses, effectively buffering temperature fluctuations.
+    A higher thermal inertia means the construction will have a slower rate of temperature change in response to energy inputs and losses, effectively buffering temperature fluctuations.
   \end{itemize}
@@
 
-Captures the heat produced by occupants inside the building. 
+The internal heat gain captures the heat produced by occupants inside the building. 
 It is modeled as a function of metabolic rate $Met$ and the number of inhabitants, which varies according to a timetable.
@@
 
-Calculate the total solar heat gain, which includes contributions from direct, diffuse, and reflected solar radiation. 
-In regard with the building’s surface characteristics and shading coefficient.
+Calculate the total solar heat gain, which includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient..
 \begin{equation}
@@
 \end{equation}
-Direct solar radiation, where the horizontal solar radiation is adjusted for the angle of incidence of the sunlight.
+Direct solar radiation is the component of solar radiation that is adjusted for the angle of incidence of the sunlight.
 \begin{equation}
@@
 \begin{equation}
-  E_{dif}=F_{dif,Hz}+\frac{1+cos(\beta)}{2}
+  E_{diff}=F_{dif,Hz}+\frac{1+cos(\beta)}{2}
 \end{equation}
@@
 Energy loss through walls is computed by summing the losses across all wall segments.
-It depends on the heat transfer coefficient , the wall area , and the temperature difference between the indoor and outdoor environments.
+It depends on the heat transfer coefficient, the wall area, and the temperature difference between the indoor and outdoor environments.
 
-In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depends of specifics informations on the building's envelope that we do not have.
+In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depends of specifics informations on the building's envelope, which we do not have.
 \begin{equation}
@@
 
-On the exterior surface we used a forced convection model :
+On the exterior surface we use a forced convection model :
 \begin{equation}
-  \phi_{conv,int}=(1,8+4,8\cdot v_{air}) \cdot \Delta T
+  \phi_{conv,ext}=(1.8+4.8\cdot v_{air}) \cdot \Delta T
 \end{equation}
@@
 This is an important factor in buildings as it impacts both energy efficiency and thermal comfort.
-We defferenciate between the exterior of the wall that exange with the sky and the interior where the walls exchange between each other.
+We differentiate between the exterior of the wall that exchange with the sky and the interior where the walls exchange between each other.
 
@@
   This term calculates the heat radiated by the surface i. 
-  $\epsilon$ is a measure of how effectively the surface emmit radiation.
-  The $T^4$ refelect the fact that radiative heatloss increase rapidly with temperature.
+  $\epsilon$ is a measure of how effectively the surface emit radiation.
+  The $T^4$ reflect the fact that radiative heat loss increases rapidly with temperature.
   \item $(1.0 - \varepsilon_i) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$ : 
   This term accounts for the heat absorbed from other surfaces $j$ within the zone.
-  The factor $(1.0 - \varepsilon_i)$ adjust for the fraction of incoming radiation that is not emitted by surface $i$.
+  The factor $(1.0 - \varepsilon_i)$ adjusts for the fraction of incoming radiation that is not emitted by surface $i$.
 \end{itemize}
 \begin{equation}
-  \phi_{net,int}[i] = \frac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot (\sigma \cdot T_i^4 - J[i])
+  \phi_{net,int}[i] = S\cdot \frac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot (\sigma \cdot T_i^4 - J[i])
 \end{equation}
@@
   This term calculate the net heat flow due to radiation for surface $i$.
-  It considers the difference between the heat emmited by the surface and the heat received from other surfaces.
+  It considers the difference between the heat emited by the surface and the heat received from other surfaces.
   The ratio $\frac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
@@
 
-Represents the energy loss due to air exchange between the zone and the exterior.
+This term represents the energy loss due to air exchange between the zone and the exterior.
 \begin{equation}
-  \phi_{air}=0,34\cdot Q_v\cdot \Delta T
+  \phi_{air}=0.34\cdot Q_v\cdot \Delta T
 \end{equation}
@@
 $\alpha$ : Absorption of a material.\hfill[-]\\
-$\alpha_{conv}$ : heat conductance of convection\hfill[-]\\
+$\alpha_{conv}$=10 : heat conductance of convection\hfill[-]\\
 $\beta$ : Angle of inclination of the wall to the horizontal.\hfill[-]\\
@@
 $E_{dir}$ : Direct solar heatflow.\hfill[W$\cdot m^{-2}$]\\
-$E_{dif}$ : Diffuse solar heatflow.\hfill[W$\cdot m^{-2}$]\\
+$E_{diff}$ : Diffuse solar heatflow.\hfill[W$\cdot m^{-2}$]\\
 $E_{ref}$ : Reflected solar heatflow.\hfill[W$\cdot m^{-2}$]\\

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
Correction for Radiation losses #6
change workflow images update CI/CD and workflow images #2

--- 2024-08-30 article.hid2-ub-cicd.ppam24.tex
@@
 \usepackage{graphicx} % for including images
-\usepackage{float}
 \usepackage[T1]{fontenc}
@@
 %% As long as no figure or table environments with \caption commands or explicit \addcontentsline{lof}{...}{...} etc. are used, the LoF and LoT are empty of course.
-\setcounter{secnumdepth}{3}
+\setcounter{secnumdepth}{4}
 \setcounter{tocdepth}{1}
@@
 
-%\tableofcontents
-%\listoffigures
+\tableofcontents
+\listoffigures
 %\listoftables
@@
 
-Building on the foundations of the Feel++ framework, this paper introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers.
-This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying and running these simulations at multiple scales.
+Building on the foundations of the Feel++ framework, our project introduces an innovative CI/CD environment specifically designed for deployment on EuroHPC JU supercomputers.
+This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying these simulations at scale.
 Integrating EuroHPC JU infrastructures represents a significant advancement in making high-performance computing resources accessible for urban simulation studies.
 
-Thanks to synergies with other CoE HiDALGO2 pilots, the KUB project is set to integrate building simulations with Urban Air Pollution (UAP) pilot models to comprehensively assess the environmental impact of building stocks soon.
-This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.
+Thanks to synergies with another CoE HiDALGO2 pilot, the KUB project is set to integrate building simulations with urban air pollution (UAP) models to comprehensively assess the environmental impact of building stocks soon.
+This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness to environmental conditions.
 
-Implementing the proposed KUB workflow will facilitate more informed urban planning decisions, support policy development for energy efficiency, and contribute to reducing urban greenhouse gas emissions.
-The project also focuses on enhancing the interactions between different environmental models to provide a holistic view of urban ecosystems.
+Implementing these objectives will facilitate more informed urban planning decisions, support policy development for energy efficiency, and contribute to reducing urban greenhouse gas emissions.
+The project also focuses on enhancing the interaction between different environmental models to provide a holistic view of urban ecosystems.
 
-This paper is organized as follows: Section~\ref{sec:kub-workflow} discusses KUB's current workflow, Section~\ref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, Section~\ref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.
+The paper is organized as follows: Section 2 discusses KUB's current workflow, Section 3 provides an overview of some modeling and simulation components, and finally, Section 4 delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.
 
@@
 
-The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments.
-The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.
-
 \begin{figure}
     \centering
-    \includegraphics[width=.9\textwidth]{img-kub-workflow.pdf}
+    \includegraphics[width=.9\textwidth,page=1]{img-kub-workflow.pdf}
     \caption{Current Urban Building Workflow from localization to city energy simulation report.}
@@
 
+The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments.
+The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with urban air pollution (UAP) models.
+
 \subsection{Data Handling and Simulation Process}
@@
 
-The workflow begins with collecting and preparing GIS and weather data and transforming them into a usable format for simulations.
-The transformed data are then partitioned for scalable processing and converted into Modelica and Feel++~\cite{christophe_prudhomme_feelppfeelpp_2024} compatible formats through the \textit{UBEM Generator}.
+The workflow begins with collecting and preparing GIS and weather data, transforming it into a format usable for simulations.
+This data is then partitioned for scalable processing and converted into Modelica and Feel++\cite{christophe_prudhomme_feelppfeelpp_2024} compatible formats through the UBEM Generator.
 
-This processed data is employed to simulate energy consumption and indoor environmental quality using the \textit{Urban Building Energy Model (UBEM)}.
-The simulation focuses on a \textit{radiative heat transfer model}, enabling enhancement of the accuracy of the energy models.
-It also computes \textit{view factors} and \textit{shading masks}, assessing how buildings affect each other's exposure to natural light and heat and overall building energy needs, and the outdoor environment by influencing the urban heat island effect.
+This processed data is employed to simulate energy consumption and indoor environmental quality using the Urban Building Energy Model (UBEM).
+The simulation focuses on radiative heat transfer, enhancing the accuracy of the energy models.
+It also computes view factors and shading masks, assessing how buildings affect each other's exposure to natural light and heat, influencing the urban heat island effect and overall building energy needs.
 
-The building simulation outputs are then optionally fed into the \textit{Urban Air Pollution (UAP) simulator} to evaluate the impact of building emissions on urban air quality.
-A feedback loop refines the building simulation scenarios based on intermediate outputs from the \textit{UAP simulator}, ensuring that the models accurately reflect the complex interdependencies between urban building energy usage and urban air quality.
+The building simulation outputs are then optionally fed into the urban air pollution (UAP) simulator to evaluate the impact of building emissions on urban air quality.
+A feedback loop refines the building simulation scenarios based on intermediate outputs from the UAP simulator, ensuring that the models accurately reflect the complex interdependencies between urban building energy usage and urban air quality.
 
@@
 
-The final step involves the \textit{UBEM Simulator}, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale.
+The final step involves the UBEM Simulator, which generates large-scale outputs that summarize the overall energy consumption and environmental impact of buildings on an urban scale.
 This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.
 
-The described streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting our application's broader objectives of improving urban living conditions and environmental impact.
+This streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting our application's broader objectives of improving urban living conditions and environmental impact.
 
@@
 
-This section provides an overview of the geometrical and physical modeling and simulation components of our urban building application.
+We now provide an overview of the geometrical and physical modeling and simulation components of the Urban building application.
 
@@
 The geometric reconstruction of urban environments within KUB involves a sophisticated approach to creating multi-fidelity representations of buildings, terrain, vegetation, roads, and other urban elements.
-This section outlines the methodologies employed and the various Levels of Detail (LOD) used in the different models of kUB workflow.
+This section outlines the methodologies employed and the various levels of detail (LOD) used in the models.
 
@@
 
-\begin{figure}[ht]%{R}{1\textwidth} % 'R' or 'L' for right or left, and width
+\begin{wrapfigure}{R}{0.6\textwidth} % 'R' or 'L' for right or left, and width
 \centering
@@
 \label{fig:buildings}
-\end{figure}
-
-In the figure~\ref{fig:buildings}, we illustrate the different levels of details.
-Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
+\end{wrapfigure}
+In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
 Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height.
@@
 Following this, the elevation at each node is evaluated.
-However, this method provides a very refined mesh, even when the terrain is flat.
-For this reason, we plan to apply a mesh adaptation technique to reduce mesh density where feasible, using the following processing:
+However, this method provides a very refined mesh, even when the terrain is flat. For this reason, we plan to apply the following procedure:
 \begin{itemize}
@@
 \subsubsection{Vegetation Modeling}
-Including vegetation (trees) in our geometric model is essential for the simulation of buildings.
-The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  .
+Including vegetation (trees) in this geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas has a significant impact.
 We use the OpenStreetMap database to obtain the metadata associated with the vegetation.
@@
 These geometric entities are parameterized so that a transformation can be applied.
-\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
+\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best we can (by searching around).
 \item Creating a tree geometric model using an affine transformation of the reference tree model.
@@
 \subsubsection{Integration of all urban geometric components}
-This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation).
+This process involves creating a conforming mesh that includes both components (buildings, terrains, vegetation).
 Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
 The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
-\textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).
+\textit{(iii)} Apply the intersection of vegetation with buildings and terrain.
+And \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).
 
@@
 
-%\begin{wrapfigure}{R}{0.6\textwidth}
-\begin{figure}[ht]
+\begin{wrapfigure}{R}{0.6\textwidth}
 \centering
-\subfloat[Representation of Strasbourg center with LOD-0\label{fig:city-strasbourg-lod0}]{%
-  \includegraphics[width=0.48\textwidth]{img-compressed-city-strasbourg-lod-0.png}
+\subfloat[LOD-0\label{fig:city-strasbourg-lod0}]{%
+  \includegraphics[width=0.4\textwidth]{img-compressed-city-strasbourg-lod-0.png}
 }
 \hfill % Ensures that the images are placed side by side
-\subfloat[Representation of Strasbourg center with LOD-1\label{fig:city-strasbourg-lod1}]{%
-  \includegraphics[width=0.48\textwidth]{img-compressed-city-strasbourg-lod-1.png}
+\subfloat[LOD-1\label{fig:city-strasbourg-lod1}]{%
+  \includegraphics[width=0.4\textwidth]{img-compressed-city-strasbourg-lod-1.png}
 }\\ % Ends the line for the first row of figures
 
-\subfloat[Representation of Grenoble LOD-1 terrain elevation\label{fig:city-grenoble-terrain}]{%
-  \includegraphics[width=0.48\textwidth]{img-compressed-city-grenoble-terrain.png}
+\subfloat[LOD-1 terrain\label{fig:city-grenoble-terrain}]{%
+  \includegraphics[width=0.4\textwidth]{img-compressed-city-grenoble-terrain.png}
 }
 
-\caption{Various representations of cities and terrains}
+\caption{Various representations of cities and terrain.
+Representation of Strasbourg center with LOD-0 in the top left panel and LOD-1 in the top right.
+LOD-1 city (Grenoble, France) representation with terrain elevation.}
 \label{fig:city-strasbourg}
-\vspace{-0.5cm}
-\end{figure}
-%\end{wrapfigure}
+\end{wrapfigure}
 
@@
 
-Features using CGAL algorithms are not yet operational in our framework.
+All the features described above are not yet operational in our framework.
 We can reconstruct a geometric model of an urban area whose location is arbitrary so that the user can select an area anywhere in the world.
-The final mesh comprises all buildings in LOD-0 or LOD-1 and the terrain with elevation.
+The final mesh comprises all buildings LOD-0 or LOD-1 and the terrain with elevation.
 The integration of all the urban components is currently being investigated.
@@
 This scale-up involves utilizing MPI to manage distributed computing resources effectively.
-To achieve the latter objective, partitions of tiles with overlapping regions are created to ensure complete and accurate building descriptions without requiring extensive MPI communications.
+To achieve this, partitions of tiles with overlapping regions are created to ensure complete and accurate building descriptions without requiring extensive MPI communications.
 Furthermore, each process uses an MT strategy to generate meshes independently, with overlapping zones allowing for the creation of complete building structures.
@@
 \subsubsection{Partitioning Strategies Depending on Simulation Use Cases}
-
 Data partitioning is a crucial stage in the deployment of the supercomputer simulator.
@@
 To do this, we built on two main tools: Feel++ and Modelica.
-\subsubsection{Governing equation of the simulation}
-The physical model of the city is based on a multizone model.
-One zone is allocated per building floor.
-The energy balance for each zone is calculated taking into account energy exchanges with adjacents zone and the environment.
-The energy balance is written according to the first law of thermodynamics, in an isolated system the sum of all form of energy is constant.
-\begin{equation}
-    C\cdot \frac{dT}{dt}=\phi_{HVAC}+\phi_{gain}-\phi_{losses}
-\end{equation}
-To give an overview of the equation's term we will give a brief summary.
-\begin{itemize}
-  \item $C\cdot \frac{dT}{dt}$ : thermal inertia of the construction. 
-  \item $\phi_{HVAC}$ : energy output of the Heating Ventilation and Air Conditioning systems. 
-  \item $\phi_{gain}$ : often reffered to as free energy gain, depends on solar gains, and building's occupation.
-  \item $\phi_{losses}$ : energy losses throught wall/roof/slab, and air exchange.
-\end{itemize}
-
-\textbf{HVAC heatflow}
-
-As for now we fixed the heating system as an ideal heat source.
-Meaning the heatflow adapt to maintain a set temperature inside the building.
-
-\textbf{Heat gain}
-
-The heatflow gain is composed of solar gain and internal gain.
-
-\textbf{Internal heat gain}
-
-The internal heat gain are a function of human presence inside of a building :
-\begin{equation}
-  \phi_{int}=Met\cdot d_{inhabitant}(timetable)
-\end{equation}
-
-\textbf{Solar heat gain}
-
-The solar heat gain can be written as a sum of the different solar fluxes : direct, diffuse and reflected.
-\begin{equation}
-  \phi_{swl}=\alpha\cdot S\cdot(E_{dir}+E_{diff}+E_{ref})\cdot 
-\end{equation}
-
-The direct solar radiation is written as such :
-\begin{equation}
-  E_{dir}=F_{dir}\cdot cos(I)
-\end{equation}
-
-$F_{dir}$ is a function of the horizontal solar radiation measured by a weather station.
-\begin{equation}
-  F_{dir}=\frac{F_{dir,Hz}}{sin(H_s)}
-\end{equation}
-\begin{equation}
-  cos(I)=cos(H_s)\cdot sin(\beta)\cdot cos(A_{zs}-A_{z})+sin(H_s)\cdot cos(\beta)
-\end{equation}
-
-The diffuse solar radiation is written as such :
-\begin{equation}
-  E_{dif}=F_{dif,Hz}+\frac{1+cos(\beta)}{2}
-\end{equation}
-
-The reflected solar radiation is written as such :
-\begin{equation}
-  E_{ref}=[F_{dir,Hz}+F_{dif,Hz}]\cdot \frac{1+cos(\beta)}{2}\cdot albedo
-\end{equation}
-
-\textbf{Conduction losses}
-
-\underline {I need to dive in the modelica model to extract the equation for the convection losses}
-
-In this scenario we do not compute the thermal brige for the models.
-\begin{equation}
-  \phi_{wall}=\sum_{j} U_j\cdot S_j\cdot \Delta T
-\end{equation}
-
-\textbf{Radiation losses}
-
-\underline{I'm not sure the Radiation exchange within a zone are taken into account, i need to check but i saw somewhere that} 
-\underline{for LOD0-1 only the big wave length heatflow with external wall surface->sky are taken into account}
-\begin{equation}
-  \phi_{net,i}=\sum_{j\not=i}\frac{J_i-J_j}{\frac{1}{S_i\cdot F_{ij}}}
-\end{equation}
-\begin{equation}
-  \phi_{net,i}=S_i\cdot \frac{\epsilon_i}{1-\epsilon_i}\cdot (\sigma\cdot T_i^4-J_i)
-\end{equation}
-
-\textbf{Air change}
-\begin{equation}
-  \phi_{air}=0,34\cdot Q_v\cdot \Delta T
-\end{equation}
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[htbp]
 \centering
@@
 \section{CI/CD Framework for the Urban Building Pilot}
-\label{sec:cicd-framework}
-
 The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment.
@@
     \centering
-    \includegraphics[width=\textwidth]{img-compressed-feelpp-devops.png}
+    \includegraphics[width=\textwidth]{img-feelpp-devops.pdf}
     \caption{CI/CD DevOps for Feel++}
@@
     \centering
-    \includegraphics[width=\textwidth]{img-compressed-feelpp-hpcops.png}
+    \includegraphics[width=\textwidth]{img-feelpp-hpcops.pdf}
     \caption{CI/CD HPCOps for Feel++}
@@
     \centering
-    \includegraphics[width=\linewidth]{img-ub-devops.pdf}
+    \includegraphics[width=\linewidth,page=1]{img-ub-devops-hpcops.pdf}
     \caption{KUB standard DevOps}
@@
     \centering
-    \includegraphics[width=\textwidth]{img-ub-hpcops.pdf}
+    \includegraphics[width=\linewidth,page=2]{img-ub-devops-hpcops.pdf}
     \caption{Ktirio Urban Building HPCOps workflow}
@@
 \subsection{Benchmarking KUB}
+\label{sec:benchmarking}
 
@@
 
-\textbf{Nomenclature}
-
-$\alpha$ : Absorption of a material.
-
-$\beta$ : Angle of inclination of the wall to the horizontal.
-
-$\Delta T$ : Temperature difference. [K]
-
-$\epsilon$ : Emissivity of the surface.
-
-$\phi_{air}$ : Air heatflow. [W]
-
-$\phi_{net}$ : radiative heatflow. [W]
-
-$\phi_{swl}$ : Solar heatflow from short wave lenght. [W]
-
-$\phi_{wall}$ : Heatflow through a wall. [W]
-
-$albedo$ : Reflective properties of the material.
-
-$A_z$ : Azimuth of the surface.
-
-$A_{zs}$ : Azimuth of the sun.
-
-$C$ : Heatcapacity of the zone. [W$\cdot K^{-1}$]
-
-$d_{inhabitant}(timetable)$ : density of inhabitant in a building as a function of a timetable set for the building type.
-
-$E_{dir}$ : Direct solar heatflow. [W$\cdot m^{-2}$]
-
-$E_{dif}$ : Diffuse solar heatflow. [W$\cdot m^{-2}$]
-
-$E_{ref}$ : Reflected solar heatflow. [W$\cdot m^{-2}$]
-
-$F_{dir}$ : Direct solar radiation. [W$\cdot m^{-2}$]
-
-$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data. [W$\cdot m^{-2}$]
-
-$F_{ij}$ : View factor between a $surface_{(i)}$ and a $surface_{(j)}$.
-
-$H_s$ : Angular height of the sun.
-
-$J$ : Radiosity of a surface. [$W\cdot m^{-2}$]
-
-$Met$ : Metabolic rate [W]
-
-$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity [$W\cdot K^{-1}$]
-
-$S$ : Surface. [$m^2$]
-
-$U_j$ : Conductance of a $wall_j$. [$W\cdot m^{-2}\cdot K^{-1}$]
-
 \bibliographystyle{splncs04}

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex

--- 2024-09-04 article.hid2-ub-cicd.ppam24.tex
@@
     \centering
-    \includegraphics[width=.9\textwidth]{img-kub-workflow.pdf}
+    \includegraphics[width=.9\textwidth,page=1]{img-kub-workflow.pdf}
     \caption{Current Urban Building Workflow from localization to city energy simulation report.}
@@
 \label{fig:buildings}
+
 \end{figure}
 
-In the figure~\ref{fig:buildings}, we illustrate the different levels of details.
-Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
-Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height.
+In \cref{fig:buildings}, we illustrate the different levels of details.
+\Cref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
+\Cref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height.
 Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM.
@@
 \subsubsection{Vegetation Modeling}
+
 Including vegetation (trees) in our geometric model is essential for the simulation of buildings.
@@
 The current strategy is as follows:
+
 \begin{itemize}
@@
 \subsubsection{Integration of all urban geometric components}
+
 This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation).
@@
 To do this, we built on two main tools: Feel++ and Modelica.
-\subsubsection{Governing equation of the simulation}
-The physical model of the city is based on a multizone model.
-One zone is allocated per building floor.
-The energy balance for each zone is calculated taking into account energy exchanges with adjacents zone and the environment.
-The energy balance is written according to the first law of thermodynamics, in an isolated system the sum of all form of energy is constant.
-\begin{equation}
-    C\cdot \frac{dT}{dt}=\phi_{HVAC}+\phi_{gain}-\phi_{losses}
-\end{equation}
-To give an overview of the equation's term we will give a brief summary.
-\begin{itemize}
-  \item $C\cdot \frac{dT}{dt}$ : represents the thermal inertia of the construction. 
-  This term quantifies how the temperature of the zone changes over time due to its thermal mass. 
-  \begin{itemize}
-    \item $C$ :This is a measure of how much heat a material can store and release. 
-    It combines the heat capacity of the construction (how much energy is required to change the temperature) with the rate of temperature change.
-    \item $\frac{dT}{dt}$ : This is the rate of change of temperature with respect to time. 
-    A higher thermal inertia means the construction will have a slower temperature change in response to energy inputs and losses, effectively buffering temperature fluctuations.
-  \end{itemize}
-  \item $\phi_{HVAC}$ : This term represents the energy input from the Heating, Ventilation, and Air Conditioning (HVAC) systems. 
-  It includes energy added to the zone to maintain desired temperature levels.
-  \item $\phi_{gain}$ : Referred to as free energy gain, this term includes solar gains (heat from sunlight) and internal gains (heat generated by occupants and equipment).
-  \item $\phi_{losses}$ : Represents the energy lost through walls, roofs, floors, and air exchanges with the environment.
-\end{itemize}
-
-\textbf{HVAC heatflow}
-
-In this model, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.
-
-\textbf{Heat gain}
-
-Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.\\
-
-\textbf{Internal heat gain}
-
-Captures the heat produced by occupants inside the building. 
-It is modeled as a function of metabolic rate $Met$ and the number of inhabitants, which varies according to a timetable.
-\begin{equation}
-  \phi_{int}=Met\cdot d_{inhabitant}(timetable)
-\end{equation}
-
-\textbf{Solar heat gain}
-
-Calculate the total solar heat gain, which includes contributions from direct, diffuse, and reflected solar radiation. 
-In regard with the building’s surface characteristics and shading coefficient.
-\begin{equation}
-  \phi_{solar}=\alpha\cdot S\cdot(E_{dir}+E_{diff}+E_{ref})\cdot S_C
-\end{equation}
-Direct solar radiation, where the horizontal solar radiation is adjusted for the angle of incidence of the sunlight.
-\begin{equation}
-  E_{dir}=F_{dir}\cdot cos(I)
-\end{equation}
-$F_{dir}$ is the direct solar radiation it is a function of the horizontal solar radiation measured by a weather station.
-\begin{equation}
-  F_{dir}=\frac{F_{dir,Hz}}{sin(H_s)}
-\end{equation}
-$Cos (I)$ : calculates the cosine of the angle of incidence of sunlight, incorporating the sun's altitude and azimuth angles as well as the building's tilt angle
-\begin{equation}
-  cos(I)=cos(H_s)\cdot sin(\beta)\cdot cos(A_{zs}-A_{z})+sin(H_s)\cdot cos(\beta)
-\end{equation}
-Diffuse solar radiation, which includes contributions from the sky dome and is adjusted for the building's tilt.
-\begin{equation}
-  E_{dif}=F_{dif,Hz}+\frac{1+cos(\beta)}{2}
-\end{equation}
-Reflected solar radiation, calculated using the total horizontal radiation and the environnement's albedo
-\begin{equation}
-  E_{ref}=[F_{dir,Hz}+F_{dif,Hz}]\cdot \frac{1+cos(\beta)}{2}\cdot albedo
-\end{equation}
-
-\textbf{Conduction losses}
-
-Energy loss through walls is computed by summing the losses across all wall segments.
-It depends on the heat transfer coefficient , the wall area , and the temperature difference between the indoor and outdoor environments.
-
-In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depends of specifics informations on the building's envelope that we do not have.
-\begin{equation}
-  \phi_{wall}=\sum_{j} U_j\cdot S_j\cdot \Delta T
-\end{equation}
-
-\textbf{Convection losses}
-
-The convection losses are computed differently regarding the surface of the wall they are applied to.
-
-On the interior surface we apply a constant :
-\begin{equation}
-  \phi_{conv,int}=\alpha_{conv} \cdot \Delta T
-\end{equation}
-
-On the exterior surface we used a forced convection model :
-\begin{equation}
-  \phi_{conv,int}=(1,8+4,8\cdot v_{air}) \cdot \Delta T
-\end{equation}
-
-Radiation losses describe the heat energy lost due to thermal radiation. 
-This is an important factor in buildings as it impacts both energy efficiency and thermal comfort.
-We defferenciate between the exterior of the wall that exange with the sky and the interior where the walls exchange between each other.
-
-Exterior radiation exchange. 
-\begin{equation}
-  \phi_{net,sky} = \varepsilon_i \cdot \sigma \cdot (T_i^4-T_{sky})
-\end{equation}
-Interior radiation exchange.
-\begin{equation}
-  J[i] = \varepsilon_i \cdot \sigma \cdot T_i^4 + (1.0 - \varepsilon_i) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]
-\end{equation}
-Radiative heat exchange $J[i]$ :
-\begin{itemize}
-  \item $\varepsilon_i \cdot \sigma \cdot T_i^4$ : 
-  This term calculates the heat radiated by the surface i. 
-  $\epsilon$ is a measure of how effectively the surface emmit radiation.
-  The $T^4$ refelect the fact that radiative heatloss increase rapidly with temperature.
-  \item $(1.0 - \varepsilon_i) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$ : 
-  This term accounts for the heat absorbed from other surfaces $j$ within the zone.
-  The factor $(1.0 - \varepsilon_i)$ adjust for the fraction of incoming radiation that is not emitted by surface $i$.
-\end{itemize}
-\begin{equation}
-  \phi_{net,int}[i] = \frac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot (\sigma \cdot T_i^4 - J[i])
-\end{equation}
-Net radiation flow $Q_{flow}[i]$ :
-\begin{itemize}
-  \item $\frac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot (\sigma \cdot T_i^4 - J[i])$ :
-  This term calculate the net heat flow due to radiation for surface $i$.
-  It considers the difference between the heat emmited by the surface and the heat received from other surfaces.
-  The ratio $\frac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
-\end{itemize}
-
-\textbf{Air change}
-
-Represents the energy loss due to air exchange between the zone and the exterior.
-\begin{equation}
-  \phi_{air}=0,34\cdot Q_v\cdot \Delta T
-\end{equation}
 
@@
 
-\textbf{Nomenclature}\\
-$\alpha$ : Absorption of a material.\hfill[-]\\
-$\alpha_{conv}$ : heat conductance of convection\hfill[-]\\
-$\beta$ : Angle of inclination of the wall to the horizontal.\hfill[-]\\
-$\Delta T$ : Temperature difference.\hfill[K]\\
-$\epsilon$ : Emissivity of the surface.\hfill[-]\\
-$\phi_{air}$ : Air heatflow.\hfill[W]\\
-$\phi_{net}$ : radiative heatflow.\hfill[W]\\
-$\phi_{solar}$ : Solar heatflow from short wave lenght.\hfill[W]\\
-$\phi_{wall}$ : Heatflow through a wall.\hfill[W]\\
-$\sigma$ : Stefan-Boltzmann constant $5,67\cdot10^{-8}$\hfill[W$\cdot m^{-2}\cdot K^{-4}$]\\
-$albedo$ : Reflective properties of the material.\hfill[-]\\
-$A_z$ : Azimuth of the surface.\hfill[-]\\
-$A_{zs}$ : Azimuth of the sun.\hfill[-]\\
-$C$ : Heatcapacity of the zone.\hfill[W$\cdot K^{-1}$]\\
-$d_{inhabitant}(timetable)$ : density of inhabitant in a building as a function of a timetable set for the building type.\hfill[-]\\
-$E_{dir}$ : Direct solar heatflow.\hfill[W$\cdot m^{-2}$]\\
-$E_{dif}$ : Diffuse solar heatflow.\hfill[W$\cdot m^{-2}$]\\
-$E_{ref}$ : Reflected solar heatflow.\hfill[W$\cdot m^{-2}$]\\
-$F_{dir}$ : Direct solar radiation.\hfill[W$\cdot m^{-2}$]\\
-$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data.\hfill[W$\cdot m^{-2}$]\\
-$F_{ij}$ : View factor between a $surface_{(i)}$ and a $surface_{(j)}$.\hfill[-]\\
-$H_s$ : Angular height of the sun. \hfill[-]\\
-$J$ : Radiosity of a surface.\hfill[$W\cdot m^{-2}$]\\
-$Met$ : Metabolic rate\hfill[W]\\
-$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity
-
-\raggedleft{[$W\cdot K^{-1}$]}\\
-$S$ : Surface.\hfill[$m^2$]\\
-$S_C$ : Shading coefficient $\in$[0,1]\hfill[-]\\
-$U_j$ : Conductance of a $wall_j$.\hfill[$W\cdot m^{-2}\cdot K^{-1}$]\\
-$V_{air}$ : Wind speed \hfill[m$\cdot s^{-1}$]
-
 \bibliographystyle{splncs04}

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
use cleveref

@@
 }
+\usepackage{cleveref}
 
@@
 \Cref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
-Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM.
-In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.
+\Cref{fig:building-lod2} and~\cref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. 
+In \Cref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see \cref{fig:city-strasbourg-lod0}, and LOD-1, see \cref{fig:city-strasbourg-lod1}, representations.
 

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
use cref
use cleveref for referencing section, caption and tables #25

@@
 
-This paper is organized as follows: Section~\ref{sec:kub-workflow} discusses KUB's current workflow, Section~\ref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, Section~\ref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.
+This paper is organized as follows: \cref{sec:kub-workflow} discusses KUB's current workflow, \cref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, \cref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.
 
@@
 
-The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments.
+The Ktirio urban building workflow, see \cref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments.
 The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.
@@
 Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
-The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
+\Cref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
 \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).
@@
 
-The figure~\ref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in figure \ref{fig:city-ny-largescale}.
+\Cref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in \cref{fig:city-ny-largescale}.
 This geometric model has an area of 400 $km^2$ (20 km square side of 20 km) and has generated around 450000 buildings.
@@
 
-In the figure~\ref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in the panel~\ref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in the panel~\ref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in panel~\ref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in panel~\ref{fig:view-factor}.
+In \cref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in \cref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in \cref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in \cref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in \cref{fig:view-factor}.
 
@@
 \end{figure}
-The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework.
+The CI/CD workflow, see \cref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. 
 The workflow leverages various main ingredients of GitHub Actions features.
@@
 
-Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++.
+\Cref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++.
 \begin{figure}
@@
 
-Figure~\ref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.
+\Cref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.
 
-Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases.
+\Cref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases.
 It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.
@@
 Hence, we have used the KUB application in the Strasbourg city center, with a square area of $4 \mathrm{km}^2$ (approximately 17K buildings).
-The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see Figure~\ref{fig:kub-hpcops}.
-Figure \ref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina.
+The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see \cref{fig:kub-hpcops}.
+\Cref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina.
 They present results for the total execution (end-to-end) of the KUB application and the simulation component.
@@
 
-To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in Figure \ref{fig:execution-breakdown}.
-This figure reports the portion of the total execution taken by:
+To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in \cref{fig:execution-breakdown}. 
+\cref{fig:execution-breakdown} reports the portion of the total execution taken by:
 \begin{itemize}

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
add gwenole as author #26
@GwennoleChappron could you provide your orcid ID ?

@@
 \title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
-\author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
+\author{Luca Berti\inst{1} \and 
+Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
+Gwennolé Chappron \inst{1}\orcidID{0000-0002-0001-0002} \and
 Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
add reporting related paragraphs. #14

--- 2024-10-25 article.hid2-ub-cicd.ppam24.tex
@@
 }
-\usepackage{cleveref}
 
@@
     \centering
-    \includegraphics[width=.9\textwidth,page=1]{img-kub-workflow.pdf}
+    \includegraphics[width=.9\textwidth]{img-kub-workflow.pdf}
     \caption{Current Urban Building Workflow from localization to city energy simulation report.}
@@
 This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.
+
+In addition to these exports, the simulator condenses, aggregates and saves relevant quantities on the fly to avoid having to manipulate large data volumes after the simulation.
+These metrics concern weather information, energy consumption and comfort assessment, and are exported in JSON format.
+The produced files are uploaded to a data management platform via the CI/CD pipeline, who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results.
+
+Insights are presented in the form of a comprehensive report and are automatically deployed on a website built using the \textit{Antora} framework.
+End users are finally able to explore the simulation outputs in a detailed but malleable manner, for both the city and the building scales.
+
+The figure \ref{fig:ktirio-cases-report} presents a gallery of city reports that are taken as test cases for the Urban Building pilot, as well as an example of a city report section showing the occlusion factor and heat flow plot.
+\begin{figure}[htbp]
+  \centering
+  \subfloat[Gallery of test case cities reports\label{fig:city-gallery}]{%
+    \includegraphics[width=0.45\textwidth]{img-compressed-city-gallery.png}
+  }
+  \hfill
+  \subfloat[Section of a city report\label{fig:city-report-section}]{%
+    \includegraphics[width=0.45\textwidth]{img-compressed-city-report-section.png}
+  }
+  \caption{Screenshots of the \url{https://cases.ktirio.fr} reporting website.}
+  \label{fig:ktirio-cases-report}
+\end{figure}
 
@@
 \label{fig:buildings}
-
 \end{figure}
 
-In \cref{fig:buildings}, we illustrate the different levels of details. 
-\Cref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. 
-\Cref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
-\Cref{fig:building-lod2} and~\cref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. 
-In \Cref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see \cref{fig:city-strasbourg-lod0}, and LOD-1, see \cref{fig:city-strasbourg-lod1}, representations.
+In the figure~\ref{fig:buildings}, we illustrate the different levels of details.
+Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
+Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height.
+Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM.
+In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.
 
@@
 \subsubsection{Vegetation Modeling}
-
 Including vegetation (trees) in our geometric model is essential for the simulation of buildings.
@@
 The current strategy is as follows:
-
 \begin{itemize}
@@
 \subsubsection{Integration of all urban geometric components}
-
 This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation).
@@
     \centering
-    \includegraphics[width=\textwidth]{img-feelpp-devops.pdf}
+    \includegraphics[width=\textwidth]{img-compressed-feelpp-devops.png}
     \caption{CI/CD DevOps for Feel++}
@@
     \centering
-    \includegraphics[width=\textwidth]{img-feelpp-hpcops.pdf}
+    \includegraphics[width=\textwidth]{img-compressed-feelpp-hpcops.png}
     \caption{CI/CD HPCOps for Feel++}
@@
     \centering
-    \includegraphics[width=\linewidth,page=1]{img-ub-devops-hpcops.pdf}
+    \includegraphics[width=\linewidth]{img-ub-devops.pdf}
     \caption{KUB standard DevOps}
@@
     \centering
-    \includegraphics[width=\linewidth,page=2]{img-ub-devops-hpcops.pdf}
+    \includegraphics[width=\textwidth]{img-ub-hpcops.pdf}
     \caption{Ktirio Urban Building HPCOps workflow}
@@
 \subsection{Benchmarking KUB}
-\label{sec:benchmarking}
 

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
add crefs #14

@@
 These metrics concern weather information, energy consumption and comfort assessment, and are exported in JSON format.
-The produced files are uploaded to a data management platform via the CI/CD pipeline, who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results.
+The produced files are uploaded to a data management platform via the CI/CD pipeline \cref{fig:kub-devops}, who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results \cref{sec:cicd-framework}.
 
@@
 
-The figure \ref{fig:ktirio-cases-report} presents a gallery of city reports that are taken as test cases for the Urban Building pilot, as well as an example of a city report section showing the occlusion factor and heat flow plot.
+\Cref{fig:ktirio-cases-report} presents a gallery of city reports that are taken as test cases for the Urban Building pilot, as well as an example of a city report section showing the occlusion factor and heat flow plot.
 \begin{figure}[htbp]

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
add cleveref package and fix syntax #14

@@
 These metrics concern weather information, energy consumption and comfort assessment, and are exported in JSON format.
-The produced files are uploaded to a data management platform via the CI/CD pipeline \cref{fig:kub-devops}, who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results \cref{sec:cicd-framework}.
+The produced files are uploaded to a data management platform via the CI/CD pipeline (see \cref{fig:kub-devops}), who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results, as detailed in \cref{sec:cicd-framework}.
 

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
fix #13 #17

--- 2024-10-25 article.hid2-ub-cicd.ppam24.tex
@@
 This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.
-
-In addition to these exports, the simulator condenses, aggregates and saves relevant quantities on the fly to avoid having to manipulate large data volumes after the simulation.
-These metrics concern weather information, energy consumption and comfort assessment, and are exported in JSON format.
-The produced files are uploaded to a data management platform via the CI/CD pipeline, who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results.
-
-Insights are presented in the form of a comprehensive report and are automatically deployed on a website built using the \textit{Antora} framework.
-End users are finally able to explore the simulation outputs in a detailed but malleable manner, for both the city and the building scales.
-
-The figure \ref{fig:ktirio-cases-report} presents a gallery of city reports that are taken as test cases for the Urban Building pilot, as well as an example of a city report section showing the occlusion factor and heat flow plot.
-\begin{figure}[htbp]
-  \centering
-  \subfloat[Gallery of test case cities reports\label{fig:city-gallery}]{%
-    \includegraphics[width=0.45\textwidth]{img-compressed-city-gallery.png}
-  }
-  \hfill
-  \subfloat[Section of a city report\label{fig:city-report-section}]{%
-    \includegraphics[width=0.45\textwidth]{img-compressed-city-report-section.png}
-  }
-  \caption{Screenshots of the \url{https://cases.ktirio.fr} reporting website.}
-  \label{fig:ktirio-cases-report}
-\end{figure}
 
@@
 
+\subsubsection{Input data}
+
+To run a KUB simulation, several input files need to be generated.
+We have several metadata files (in JSON format), mesh data files (in MSH format), and
+meteorological measurement files (in CSV format).
+In the table \ref{tab:input-data-size-comparison}, we have listed these files
+with their corresponding sizes.
+In this comparison, we used New York City as the location
+and a duration of one year for the simulation.
+In addition, we compared the size of the input data with the size of the zone.
+
+\begin{table}[h]
+\begin{center}
+  \begin{tabular}{|c|| c | c | c|} 
+    \hline
+    Files & $4 \times 4 \mathrm{km}^2$ & $10 \times 10 \mathrm{km}^2$ & $20 \times 20 \mathrm{km}^2$ \\ [0.5ex] 
+    \hline\hline
+    geographicdata\_setup.json & 4.0 K  & 4.0 K & 4.0 K \\ 
+    \hline
+    gis.json & 23 M & 117M & 470 M \\
+    \hline
+    mesh\_lod0.msh & 17 M & 112M & 496 M \\
+    \hline
+    mesh\_lod1.msh & 44 M & 240M & 896 M \\
+    \hline
+    weather-data-0.hourly-variables.csv & 384 K  & 384 K  & 384 K  \\
+    \hline
+    weather-data.json & 4.0 K  & 4.0 K & 4.0 K  \\ [1ex] 
+    \hline
+  \end{tabular}
+\end{center}
+\caption{Size comparison of input data using New York city.}
+\label{tab:input-data-size-comparison}
+\end{table}
+
 \section{CI/CD Framework for the Urban Building Pilot}
@@
 
+The total elapsed time varies from 100 seconds to 1000 seconds in function of the number of Nodes.
+All machines tested have an elapsed time of the same magnitude order.
+
 Pre-processing does not scale.

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex

@@
 \title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
-\author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
+\author{Luca Berti\inst{1} \and 
+Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
+Gwennolé Chappron \inst{1}\orcidID{0009-0003-7588-3370} \and
 Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and
@@
 \label{fig:buildings}
+
 \end{figure}
 
-In the figure~\ref{fig:buildings}, we illustrate the different levels of details.
-Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
-Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height.
-Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM.
-In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.
+In \cref{fig:buildings}, we illustrate the different levels of details. 
+\Cref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. 
+\Cref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
+\Cref{fig:building-lod2} and~\cref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. 
+In \Cref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see \cref{fig:city-strasbourg-lod0}, and LOD-1, see \cref{fig:city-strasbourg-lod1}, representations.
 
@@
 \subsubsection{Integration of all urban geometric components}
+
 This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation).
 Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
-The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
+\Cref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
 \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).
@@
 
-\subsubsection{Input data}
-
-To run a KUB simulation, several input files need to be generated.
-We have several metadata files (in JSON format), mesh data files (in MSH format), and
-meteorological measurement files (in CSV format).
-In the table \ref{tab:input-data-size-comparison}, we have listed these files
-with their corresponding sizes.
-In this comparison, we used New York City as the location
-and a duration of one year for the simulation.
-In addition, we compared the size of the input data with the size of the zone.
-
-\begin{table}[h]
-\begin{center}
-  \begin{tabular}{|c|| c | c | c|} 
-    \hline
-    Files & $4 \times 4 \mathrm{km}^2$ & $10 \times 10 \mathrm{km}^2$ & $20 \times 20 \mathrm{km}^2$ \\ [0.5ex] 
-    \hline\hline
-    geographicdata\_setup.json & 4.0 K  & 4.0 K & 4.0 K \\ 
-    \hline
-    gis.json & 23 M & 117M & 470 M \\
-    \hline
-    mesh\_lod0.msh & 17 M & 112M & 496 M \\
-    \hline
-    mesh\_lod1.msh & 44 M & 240M & 896 M \\
-    \hline
-    weather-data-0.hourly-variables.csv & 384 K  & 384 K  & 384 K  \\
-    \hline
-    weather-data.json & 4.0 K  & 4.0 K & 4.0 K  \\ [1ex] 
-    \hline
-  \end{tabular}
-\end{center}
-\caption{Size comparison of input data using New York city.}
-\label{tab:input-data-size-comparison}
-\end{table}
-
 \section{CI/CD Framework for the Urban Building Pilot}
@@
 
-Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
+\Cref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++.
 \begin{figure}
     \centering
-    \includegraphics[width=\textwidth]{img-compressed-feelpp-hpcops.png}
+    \includegraphics[width=\textwidth]{img-feelpp-hpcops.pdf}
     \caption{CI/CD HPCOps for Feel++}
@@
 \end{itemize}
-
-The total elapsed time varies from 100 seconds to 1000 seconds in function of the number of Nodes.
-All machines tested have an elapsed time of the same magnitude order.
 

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex

@@
 This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.
+
+In addition to these exports, the simulator condenses, aggregates and saves relevant quantities on the fly to avoid having to manipulate large data volumes after the simulation.
+These metrics concern weather information, energy consumption and comfort assessment, and are exported in JSON format.
+The produced files are uploaded to a data management platform via the CI/CD pipeline (see \cref{fig:kub-devops}), who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results, as detailed in \cref{sec:cicd-framework}.
+
+Insights are presented in the form of a comprehensive report and are automatically deployed on a website built using the \textit{Antora} framework.
+End users are finally able to explore the simulation outputs in a detailed but malleable manner, for both the city and the building scales.
+
+\Cref{fig:ktirio-cases-report} presents a gallery of city reports that are taken as test cases for the Urban Building pilot, as well as an example of a city report section showing the occlusion factor and heat flow plot.
+\begin{figure}[htbp]
+  \centering
+  \subfloat[Gallery of test case cities reports\label{fig:city-gallery}]{%
+    \includegraphics[width=0.45\textwidth]{img-compressed-city-gallery.png}
+  }
+  \hfill
+  \subfloat[Section of a city report\label{fig:city-report-section}]{%
+    \includegraphics[width=0.45\textwidth]{img-compressed-city-report-section.png}
+  }
+  \caption{Screenshots of the \url{https://cases.ktirio.fr} reporting website.}
+  \label{fig:ktirio-cases-report}
+\end{figure}
 

### 2024-10-26 article.hid2-ub-cicd.ppam24.tex

@@
 We now turn to describing the physical modeling of city energy simulation.
+
 To do this, we built on two main tools: Feel++ and Modelica. 
+\subsubsection{Governing equation of the simulation}
+The physical model of the city is based on a multizone model.
+One zone is allocated per building floor.
+The energy balance for each zone is calculated taking into account energy exchanges with adjacent zones and the environment.
+The energy balance is written according to the first law of thermodynamics : in an isolated system, the sum of all forms of energy is constant.
+\begin{equation}
+    C\cdot \frac{dT}{dt}=\phi_{HVAC}+\phi_{gain}-\phi_{losses}
+\end{equation}
+To give an overview of the equation's term we will give a brief summary.
+\begin{itemize}
+  \item $C\cdot \frac{dT}{dt}$ : represents the thermal inertia of the construction. 
+  This term quantifies how the temperature of the zone changes over time due to its thermal mass. 
+  \begin{itemize}
+    \item $C$ :This is a measure of how much heat a material can store and release. 
+    It combines the heat capacity of the construction (how much energy is required to change the temperature) with the rate of temperature change.
+    \item $\frac{dT}{dt}$ : This is the rate of change of temperature with respect to time. 
+    A higher thermal inertia means the construction will have a slower rate of temperature change in response to energy inputs and losses, effectively buffering temperature fluctuations.
+  \end{itemize}
+  \item $\phi_{HVAC}$ : This term represents the energy input from the Heating, Ventilation, and Air Conditioning (HVAC) systems. 
+  It includes energy added to the zone to maintain desired temperature levels.
+  \item $\phi_{gain}$ : Referred to as free energy gain, this term includes solar gains (heat from sunlight) and internal gains (heat generated by occupants and equipment).
+  \item $\phi_{losses}$ : Represents the energy lost through walls, roofs, floors, and air exchanges with the environment.
+\end{itemize}
+
+\textbf{HVAC heatflow}
+
+In this model, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.
+
+\textbf{Heat gain}
+
+Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.\\
+
+\textbf{Internal heat gain}
+
+The internal heat gain captures the heat produced by occupants inside the building. 
+It is modeled as a function of metabolic rate $Met$ and the number of inhabitants, which varies according to a timetable.
+\begin{equation}
+  \phi_{int}=Met\cdot d_{inhabitant}(timetable)
+\end{equation}
+
+\textbf{Solar heat gain}
+
+Calculate the total solar heat gain, which includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient..
+\begin{equation}
+  \phi_{solar}=\alpha\cdot S\cdot(E_{dir}+E_{diff}+E_{ref})\cdot S_C
+\end{equation}
+Direct solar radiation is the component of solar radiation that is adjusted for the angle of incidence of the sunlight.
+\begin{equation}
+  E_{dir}=F_{dir}\cdot cos(I)
+\end{equation}
+$F_{dir}$ is the direct solar radiation it is a function of the horizontal solar radiation measured by a weather station.
+\begin{equation}
+  F_{dir}=\frac{F_{dir,Hz}}{sin(H_s)}
+\end{equation}
+$Cos (I)$ : calculates the cosine of the angle of incidence of sunlight, incorporating the sun's altitude and azimuth angles as well as the building's tilt angle
+\begin{equation}
+  cos(I)=cos(H_s)\cdot sin(\beta)\cdot cos(A_{zs}-A_{z})+sin(H_s)\cdot cos(\beta)
+\end{equation}
+Diffuse solar radiation, which includes contributions from the sky dome and is adjusted for the building's tilt.
+\begin{equation}
+  E_{diff}=F_{dif,Hz}+\frac{1+cos(\beta)}{2}
+\end{equation}
+Reflected solar radiation, calculated using the total horizontal radiation and the environnement's albedo
+\begin{equation}
+  E_{ref}=[F_{dir,Hz}+F_{dif,Hz}]\cdot \frac{1+cos(\beta)}{2}\cdot albedo
+\end{equation}
+
+\textbf{Conduction losses}
+
+Energy loss through walls is computed by summing the losses across all wall segments.
+It depends on the heat transfer coefficient, the wall area, and the temperature difference between the indoor and outdoor environments.
+
+In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depends of specifics informations on the building's envelope, which we do not have.
+\begin{equation}
+  \phi_{wall}=\sum_{j} U_j\cdot S_j\cdot \Delta T
+\end{equation}
+
+The convection losses are computed differently regarding the surface of the wall they are applied to.
+
+On the interior surface we apply a constant :
+\begin{equation}
+  \phi_{conv,int}=\alpha_{conv} \cdot \Delta T
+\end{equation}
+
+On the exterior surface we use a forced convection model :
+\begin{equation}
+  \phi_{conv,ext}=(1.8+4.8\cdot v_{air}) \cdot \Delta T
+\end{equation}
+
+\textbf{Radiation losses}
+
+Radiation losses describe the heat energy lost due to thermal radiation. 
+This is an important factor in buildings as it impacts both energy efficiency and thermal comfort.
+We differentiate between the exterior of the wall that exchange with the sky and the interior where the walls exchange between each other.
+
+Exterior radiation exchange. 
+\begin{equation}
+  \phi_{net,sky} = \varepsilon_i \cdot \sigma \cdot (T_i^4-T_{sky}^4)
+\end{equation}
+Interior radiation exchange.
+\begin{equation}
+  J[i] = \varepsilon_i \cdot \sigma \cdot T_i^4 + (1.0 - \varepsilon_i) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]
+\end{equation}
+Radiative heat exchange $J[i]$ :
+\begin{itemize}
+  \item $\varepsilon_i \cdot \sigma \cdot T_i^4$ : 
+  This term calculates the heat radiated by the surface i. 
+  $\epsilon$ is a measure of how effectively the surface emit radiation.
+  The $T^4$ reflect the fact that radiative heat loss increases rapidly with temperature.
+  \item $(1.0 - \varepsilon_i) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$ : 
+  This term accounts for the heat absorbed from other surfaces $j$ within the zone.
+  The factor $(1.0 - \varepsilon_i)$ adjusts for the fraction of incoming radiation that is not emitted by surface $i$.
+\end{itemize}
+\begin{equation}
+  \phi_{net,int}[i] = S\cdot \frac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot (\sigma \cdot T_i^4 - J[i])
+\end{equation}
+Net radiation flow $Q_{flow}[i]$ :
+\begin{itemize}
+  \item $\frac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot (\sigma \cdot T_i^4 - J[i])$ :
+  This term calculate the net heat flow due to radiation for surface $i$.
+  It considers the difference between the heat emited by the surface and the heat received from other surfaces.
+  The ratio $\frac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
+\end{itemize}
+
+\textbf{Air change}
+
+This term represents the energy loss due to air exchange between the zone and the exterior.
+\begin{equation}
+  \phi_{air}=0.34\cdot Q_v\cdot \Delta T
+\end{equation}
 
@@
 
+\textbf{Nomenclature}\\
+$\alpha$ : Absorption of a material.\hfill[-]\\
+$\alpha_{conv}$=10 : heat conductance of convection\hfill[-]\\
+$\beta$ : Angle of inclination of the wall to the horizontal.\hfill[-]\\
+$\Delta T$ : Temperature difference.\hfill[K]\\
+$\epsilon$ : Emissivity of the surface.\hfill[-]\\
+$\phi_{air}$ : Air heatflow.\hfill[W]\\
+$\phi_{net}$ : radiative heatflow.\hfill[W]\\
+$\phi_{solar}$ : Solar heatflow from short wave lenght.\hfill[W]\\
+$\phi_{wall}$ : Heatflow through a wall.\hfill[W]\\
+$\sigma$ : Stefan-Boltzmann constant $5,67\cdot10^{-8}$\hfill[W$\cdot m^{-2}\cdot K^{-4}$]\\
+$albedo$ : Reflective properties of the material.\hfill[-]\\
+$A_z$ : Azimuth of the surface.\hfill[-]\\
+$A_{zs}$ : Azimuth of the sun.\hfill[-]\\
+$C$ : Heatcapacity of the zone.\hfill[W$\cdot K^{-1}$]\\
+$d_{inhabitant}(timetable)$ : density of inhabitant in a building as a function of a timetable set for the building type.\hfill[-]\\
+$E_{dir}$ : Direct solar heatflow.\hfill[W$\cdot m^{-2}$]\\
+$E_{diff}$ : Diffuse solar heatflow.\hfill[W$\cdot m^{-2}$]\\
+$E_{ref}$ : Reflected solar heatflow.\hfill[W$\cdot m^{-2}$]\\
+$F_{dir}$ : Direct solar radiation.\hfill[W$\cdot m^{-2}$]\\
+$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data.\hfill[W$\cdot m^{-2}$]\\
+$F_{ij}$ : View factor between a $surface_{(i)}$ and a $surface_{(j)}$.\hfill[-]\\
+$H_s$ : Angular height of the sun. \hfill[-]\\
+$J$ : Radiosity of a surface.\hfill[$W\cdot m^{-2}$]\\
+$Met$ : Metabolic rate\hfill[W]\\
+$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity
+
+\raggedleft{[$W\cdot K^{-1}$]}\\
+$S$ : Surface.\hfill[$m^2$]\\
+$S_C$ : Shading coefficient $\in$[0,1]\hfill[-]\\
+$U_j$ : Conductance of a $wall_j$.\hfill[$W\cdot m^{-2}\cdot K^{-1}$]\\
+$V_{air}$ : Wind speed \hfill[m$\cdot s^{-1}$]
+
 \bibliographystyle{splncs04}

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
up style and rework article model

--- 2024-10-25 article.hid2-ub-cicd.ppam24.tex
@@
 \usepackage[]{subcaption}
-
+\usepackage{multicol}
 \usepackage{url}
@@
 \usepackage{xcolor}
+\usepackage{paralist}
+\usepackage{amsmath}
 \definecolor{darkred}{rgb}{0.6, 0, 0}
@@
 \title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
-\author{Luca Berti\inst{1} \and 
-Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
-Gwennolé Chappron \inst{1}\orcidID{0009-0003-7588-3370} \and
+\author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
 Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and 
@@
 
-This paper is organized as follows: \cref{sec:kub-workflow} discusses KUB's current workflow, \cref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, \cref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.
+This paper is organized as follows: Section~\ref{sec:kub-workflow} discusses KUB's current workflow, Section~\ref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, Section~\ref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.
 
@@
 
-The Ktirio urban building workflow, see \cref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments.
+The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments.
 The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.
@@
 \subsubsection{Integration of all urban geometric components}
-
 This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation).
 Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
-\Cref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
+The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
 \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).
@@
 
-\Cref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in \cref{fig:city-ny-largescale}.
+The figure~\ref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in figure \ref{fig:city-ny-largescale}.
 This geometric model has an area of 400 $km^2$ (20 km square side of 20 km) and has generated around 450000 buildings.
@@
 \subsubsection{Conclusion on mesh construction}
+
 Our strategy aims to improve the efficiency and scalability of the mesh generation process and enhance the fidelity and accuracy of the urban models used in simulations.
@@
 To do this, we built on two main tools: Feel++ and Modelica.
+
+\subsubsection{Heat transfer model in buildings}
+\label{sec:heat-transfer-in-buildings}
+
+The physical model of city buildings is based on a multizone model.
+One zone is allocated per building floor. 
+The energy balance for each zone is calculated by taking into account energy exchanges with adjacent zones and the environment.
+
+The energy balance is written according to the first law of thermodynamics: in an isolated system, the sum of all forms of energy is constant.
+\begin{equation}
+    C \frac{dT}{dt} = \phi_{\mathrm{HVAC}} + \phi_{\mathrm{gain}} - \phi_{\mathrm{losses}}
+\end{equation}
+where
+\begin{inparaenum}[\it (i)]
+    \item $C \dfrac{dT}{dt}$ represents the thermal inertia of the construction, quantifying how the temperature of the zone changes over time due to its thermal mass. Specifically,
+    $C$ is a measure of how much heat a material can store and release, combining the heat capacity of the construction (how much energy is required to change the temperature) with the rate of temperature change and
+    $\dfrac{dT}{dt}$ is the rate of change of temperature with respect to time.
+A higher thermal inertia means the construction will have a slower rate of temperature change in response to energy inputs and losses, effectively buffering temperature fluctuations;
+    \item $\phi_{\mathrm{HVAC}}$ represents the energy input from the Heating, Ventilation, and Air Conditioning (HVAC) systems.
+It includes energy added to the zone to maintain desired temperature levels;
+    \item $\phi_{\mathrm{gain}}$, referred to as free energy gain, includes solar gains (heat from sunlight) and internal gains (heat generated by occupants and equipment);
+    \item $\phi_{\mathrm{losses}}$ represents the energy lost through walls, roofs, floors, and air exchanges with the environment.
+\end{inparaenum}
+
+\paragraph{HVAC heat flow} In the version of the model at the time of writing, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.
+
+\paragraph{Heat gain} Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.
+
+\paragraph{Internal heat gain} The internal heat gain captures the heat produced by occupants inside the building. 
+It is modeled as a function of metabolic rate $\mathrm{Met}$ and the number of inhabitants, $d_i$, which varies over time $t$:
+\begin{equation}
+  \phi_{\mathrm{int}} = \mathrm{Met} \cdot d_i(t)
+\end{equation}
+
+\paragraph{Solar heat gain} The total solar heat gain includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient:
+\begin{equation}
+  \phi_{\mathrm{solar}} = \alpha \cdot S \cdot \left( E_{\mathrm{dir}} + E_{\mathrm{diff}} + E_{\mathrm{ref}} \right) \cdot S_C
+\end{equation}
+Direct solar radiation is the component of solar radiation adjusted for the angle of incidence of the sunlight:
+\begin{equation}
+  E_{\mathrm{dir}} = F_{\mathrm{dir}} \cdot \cos(I)
+\end{equation}
+Here, $F_{\mathrm{dir}}$ is the direct solar radiation, which is a function of the horizontal solar radiation measured by a weather station:
+\begin{equation}
+  F_{\mathrm{dir}} = \dfrac{F_{\mathrm{dir,Hz}}}{\sin(H_s)}
+\end{equation}
+The term $\cos(I)$ calculates the cosine of the angle of incidence of sunlight, incorporating the sun's altitude and azimuth angles as well as the building's tilt angle:
+\begin{equation}
+  \cos(I) = \cos(H_s) \cdot \sin(\beta) \cdot \cos(A_{zs} - A_z) + \sin(H_s) \cdot \cos(\beta)
+\end{equation}
+Diffuse solar radiation includes contributions from the sky dome and is adjusted for the building's tilt:
+\begin{equation}
+  E_{\mathrm{diff}} = F_{\mathrm{dif,Hz}} \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right)
+\end{equation}
+Reflected solar radiation is calculated using the total horizontal radiation and the environment's albedo:
+\begin{equation}
+  E_{\mathrm{ref}} = \left[ F_{\mathrm{dir,Hz}} + F_{\mathrm{dif,Hz}} \right] \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right) \cdot \text{albedo}
+\end{equation}
+
+\paragraph{Conduction losses} Energy loss through walls is computed by summing the losses across all wall segments.
+It depends on the heat transfer coefficient, the wall area, and the temperature difference between the indoor and outdoor environments.
+In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depend on specific information about the building's envelope, which we do not have:
+\begin{equation}
+  \phi_{\mathrm{wall}} = \sum_{j} U_j \cdot S_j \cdot \Delta T
+\end{equation}
+The convection losses are computed differently depending on the surface of the wall to which they are applied. On the interior surface, we apply a constant:
+\begin{equation}
+  \phi_{\mathrm{conv,int}} = \alpha_{\mathrm{conv}} \cdot \Delta T
+\end{equation}
+On the exterior surface, we use a forced convection model:
+\begin{equation}
+  \phi_{\mathrm{conv,ext}} = \left( 1.8 + 4.8 \cdot v_{\mathrm{air}} \right) \cdot \Delta T
+\end{equation}
+
+\paragraph{Radiation losses} Radiation losses describe the heat energy lost due to thermal radiation, impacting both energy efficiency and thermal comfort.
+We differentiate between the exterior of the wall that exchanges with the sky and the interior where the walls exchange with each other.
+namely, for the exterior radiation exchange:
+\begin{equation}
+  \phi_{\mathrm{net,sky}} = \varepsilon_i \cdot \sigma \cdot \left( T_i^4 - T_{\mathrm{sky}}^4 \right)
+\end{equation}
+and for the interior radiation exchange:
+\begin{equation}
+  J[i] = \varepsilon_i \cdot \sigma \cdot T_i^4 + \left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]
+\end{equation}
+where the radiative heat exchange $J[i]$ includes two terms:
+\begin{inparaenum}[\it (i)]
+    \item $\varepsilon_i \cdot \sigma \cdot T_i^4$, which calculates the heat radiated by surface $i$ where $\varepsilon_i$ measures how effectively the surface emits radiation and $T_i^4$ reflects that radiative heat loss increases rapidly with temperature; and
+    \item $\left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$, which accounts for the heat absorbed from other surfaces $j$ within the zone.
+The factor $\left( 1.0 - \varepsilon_i \right)$ adjusts for the fraction of incoming radiation not emitted by surface $i$.
+\end{inparaenum}
+The net radiation flow is given by:
+\begin{equation}
+  \phi_{\mathrm{net,int}}[i] = S \cdot \dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)
+\end{equation}
+Net radiation flow $Q_{\mathrm{flow}}[i]$ considers:
+\begin{inparaenum}[\it (i)]
+    \item $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)$, which calculates the net heat flow due to radiation for surface $i$, considering the difference between the heat emitted by the surface and the heat received from other surfaces.
+The ratio $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
+\end{inparaenum}
+
+\paragraph{Air change} This term represents the energy loss due to air exchange between the zone and the exterior:
+\begin{equation}
+  \phi_{\mathrm{air}} = 0.34 \cdot Q_v \cdot \Delta T
+\end{equation}
+
+The described thermal models are implemented using the Modelica language, which is an object-oriented, equation-based language well-suited for modeling complex physical systems. 
+These models are then transformed into Functional Mock-up Units (FMUs) compliant with the Functional Mock-up Interface (FMI) standard. 
+FMUs encapsulate the models and enable them to be shared and integrated across different simulation environments.
+
+\paragraph{Conclusion}
+
+By integrating these models within a high-performance computing framework, it is possible to simulate the thermal behavior of city-scale building clusters.
+This facilitates the assessment of energy consumption, thermal comfort, and the impact of various energy-saving strategies under different environmental conditions and operational scenarios.
 
@@
 This powerful toolchain is essential for KUB.
+
+\subsubsection{Modelica for Multizone Heat Transfer}
+
+The FMUs built from \cref{sec:heat-transfer-in-buildings} are loaded by the \texttt{Feel++} environment.
+
+Input data for the models are sourced from available building information, such as geometric dimensions, material properties, and occupancy schedules.
+When specific data are unavailable, default values are assigned based on the building's construction year, referencing standard building codes or typical practices from that period.
+This approach ensures that the models can be applied to a wide range of buildings, even when detailed information is limited.
 
@@
 
-In \cref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in \cref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in \cref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in \cref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in \cref{fig:view-factor}.
+In the figure~\ref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in the panel~\ref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in the panel~\ref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in panel~\ref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in panel~\ref{fig:view-factor}.
 
@@
 \end{figure}
-The CI/CD workflow, see \cref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. 
+The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework.
 The workflow leverages various main ingredients of GitHub Actions features.
@@
 
-\Cref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++.
+Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
 \begin{figure}
     \centering
-    \includegraphics[width=\textwidth]{img-feelpp-hpcops.pdf}
+    \includegraphics[width=\textwidth]{img-compressed-feelpp-hpcops.png}
     \caption{CI/CD HPCOps for Feel++}
@@
 
-\Cref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.
+Figure~\ref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.
 
-\Cref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases.
+Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases.
 It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.
@@
 Hence, we have used the KUB application in the Strasbourg city center, with a square area of $4 \mathrm{km}^2$ (approximately 17K buildings).
-The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see \cref{fig:kub-hpcops}.
-\Cref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina.
+The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see Figure~\ref{fig:kub-hpcops}.
+Figure \ref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina.
 They present results for the total execution (end-to-end) of the KUB application and the simulation component.
@@
 
-To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in \cref{fig:execution-breakdown}. 
-\cref{fig:execution-breakdown} reports the portion of the total execution taken by:
+To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in Figure \ref{fig:execution-breakdown}.
+This figure reports the portion of the total execution taken by:
 \begin{itemize}
@@
 
+\textbf{Nomenclature}\\
+\begin{multicols}{2}
+$\alpha$ : Absorption of a material.\hfill[-]\\
+$\alpha_{conv}$=10 : Heat conductance of convection.\hfill[-]\\
+$\beta$ : Angle of inclination of the wall to the horizontal.\hfill[-]\\
+$\Delta T$ : Temperature difference.\hfill[K]\\
+$\epsilon$ : Emissivity of the surface.\hfill[-]\\
+$\phi_{air}$ : Air heat flow.\hfill[W]\\
+$\phi_{net}$ : Radiative heat flow.\hfill[W]\\
+$\phi_{solar}$ : Solar heat flow from short wavelength.\hfill[W]\\
+$\phi_{wall}$ : Heat flow through a wall.\hfill[W]\\
+$\sigma$ : Stefan-Boltzmann constant $5,67\cdot10^{-8}$.\hfill[W$\cdot m^{-2}\cdot K^{-4}$]\\
+$albedo$ : Reflective properties of the material.\hfill[-]\\
+$A_z$ : Azimuth of the surface.\hfill[-]\\
+$A_{zs}$ : Azimuth of the sun.\hfill[-]\\
+$C$ : Heat capacity of the zone.\hfill[W$\cdot K^{-1}$]\\
+$d_{inhabitant}(timetable)$ : Density of inhabitants as a function of the timetable set for the building type.\hfill[-]\\
+$E_{dir}$ : Direct solar heat flow.\hfill[W$\cdot m^{-2}$]\\
+$E_{diff}$ : Diffuse solar heat flow.\hfill[W$\cdot m^{-2}$]\\
+$E_{ref}$ : Reflected solar heat flow.\hfill[W$\cdot m^{-2}$]\\
+$F_{dir}$ : Direct solar radiation.\hfill[W$\cdot m^{-2}$]\\
+$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data.\hfill[W$\cdot m^{-2}$]\\
+$F_{ij}$ : View factor between $surface_{(i)}$ and $surface_{(j)}$.\hfill[-]\\
+$H_s$ : Angular height of the sun.\hfill[-]\\
+$J$ : Radiosity of a surface.\hfill[W$\cdot m^{-2}$]\\
+$Met$ : Metabolic rate.\hfill[W]\\
+$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity.\hfill[W$\cdot K^{-1}$]\\
+$S$ : Surface area.\hfill[m$^2$]\\
+$S_C$ : Shading coefficient $\in$ [0,1].\hfill[-]\\
+$U_j$ : Conductance of a $wall_j$.\hfill[W$\cdot m^{-2}\cdot K^{-1}$]\\
+$V_{air}$ : Wind speed.\hfill[m$\cdot s^{-1}$]
+\end{multicols}
+
 \bibliographystyle{splncs04}

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex

@@
 We now turn to describing the physical modeling of city energy simulation.
+
 To do this, we built on two main tools: Feel++ and Modelica.
@@
 The energy balance is written according to the first law of thermodynamics: in an isolated system, the sum of all forms of energy is constant.
+
 \begin{equation}

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
up section on modeling

@@
 
-\paragraph{Conclusion}
-
-By integrating these models within a high-performance computing framework, it is possible to simulate the thermal behavior of city-scale building clusters.
+\paragraph{Conclusion} By integrating these models within a high-performance computing framework, it is possible to simulate the thermal behavior of city-scale building clusters.
 This facilitates the assessment of energy consumption, thermal comfort, and the impact of various energy-saving strategies under different environmental conditions and operational scenarios.
@@
 
-Input data for the models are sourced from available building information, such as geometric dimensions, material properties, and occupancy schedules.
+Input data for the models are sourced from available building information, such as geometric dimensions and material properties.
 When specific data are unavailable, default values are assigned based on the building's construction year, referencing standard building codes or typical practices from that period.
+
+Occupancy schedules are given as input to the models using reglementary occupancy.
+We are currently working on parametrized occupancy profiles, which are adjusted based on the building's use type (e.g., residential, office, commercial).
+
 This approach ensures that the models can be applied to a wide range of buildings, even when detailed information is limited.
@@
 
-\textbf{Nomenclature}\\
+\section*{Nomenclature}
+
 \begin{multicols}{2}

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex

@@
 
-\subsubsection{Modelica for Multizone Heat Transfer}
-
-The FMUs built from \cref{sec:heat-transfer-in-buildings} are loaded by the \texttt{Feel++} environment.
-
-Input data for the models are sourced from available building information, such as geometric dimensions and material properties.
-When specific data are unavailable, default values are assigned based on the building's construction year, referencing standard building codes or typical practices from that period.
-
-Occupancy schedules are given as input to the models using reglementary occupancy.
-We are currently working on parametrized occupancy profiles, which are adjusted based on the building's use type (e.g., residential, office, commercial).
-
-This approach ensures that the models can be applied to a wide range of buildings, even when detailed information is limited.
-
 \subsubsection{Computing Shading Masks and View Factors with Feel++}
@@
 This method leverages the generation of Functional Mock-up Units (FMUs), which integrate seamlessly into larger C/C++ applications, providing a robust framework for handling complex simulations involving multiple interacting systems.
+The FMUs built from \cref{sec:heat-transfer-in-buildings} are loaded by the \texttt{Feel++} environment.
+Input data for the models are sourced from available building information, such as geometric dimensions and material properties.
+When specific data are unavailable, default values are assigned based on the building's construction year, referencing standard building codes or typical practices from that period.
+Occupancy schedules are given as input to the models using reglementary occupancy.
+We are currently working on parametrized occupancy profiles, which are adjusted based on the building's use type (e.g., residential, office, commercial).
+This approach ensures that the models can be applied to a wide range of buildings, even when detailed information is limited.
 
@@
 This approach facilitates consistent, reproducible deployments, optimizing performance and resource utilization.
+
+\subsubsection{Input data}
+
+To run a KUB simulation, several input files need to be generated.
+We have several metadata files (in JSON format), mesh data files (in MSH format), and
+meteorological measurement files (in CSV format).
+In the table \ref{tab:input-data-size-comparison}, we have listed these files
+with their corresponding sizes.
+In this comparison, we used New York City as the location
+and a duration of one year for the simulation.
+In addition, we compared the size of the input data with the size of the zone.
+
+\begin{table}[h]
+\begin{center}
+  \begin{tabular}{|c|| c | c | c|} 
+    \hline
+    Files & $4 \times 4 \mathrm{km}^2$ & $10 \times 10 \mathrm{km}^2$ & $20 \times 20 \mathrm{km}^2$ \\ [0.5ex] 
+    \hline\hline
+    geographicdata\_setup.json & 4.0 K  & 4.0 K & 4.0 K \\ 
+    \hline
+    gis.json & 23 M & 117M & 470 M \\
+    \hline
+    mesh\_lod0.msh & 17 M & 112M & 496 M \\
+    \hline
+    mesh\_lod1.msh & 44 M & 240M & 896 M \\
+    \hline
+    weather-data-0.hourly-variables.csv & 384 K  & 384 K  & 384 K  \\
+    \hline
+    weather-data.json & 4.0 K  & 4.0 K & 4.0 K  \\ [1ex] 
+    \hline
+  \end{tabular}
+\end{center}
+\caption{Size comparison of input data using New York city.}
+\label{tab:input-data-size-comparison}
+\end{table}
 

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
update input data

--- 2024-11-01 article.hid2-ub-cicd.ppam24.tex
@@
 \usepackage[]{subcaption}
-\usepackage{multicol}
+\usepackage{booktabs}
 \usepackage{url}
@@
 \usepackage{xcolor}
-\usepackage{paralist}
-\usepackage{amsmath}
 \definecolor{darkred}{rgb}{0.6, 0, 0}
@@
 This comprehensive urban scale analysis merges data from the building energy and air quality models to provide a holistic view of urban environmental quality.
-
-In addition to these exports, the simulator condenses, aggregates and saves relevant quantities on the fly to avoid having to manipulate large data volumes after the simulation.
-These metrics concern weather information, energy consumption and comfort assessment, and are exported in JSON format.
-The produced files are uploaded to a data management platform via the CI/CD pipeline (see \cref{fig:kub-devops}), who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results, as detailed in \cref{sec:cicd-framework}.
-
-Insights are presented in the form of a comprehensive report and are automatically deployed on a website built using the \textit{Antora} framework.
-End users are finally able to explore the simulation outputs in a detailed but malleable manner, for both the city and the building scales.
-
-\Cref{fig:ktirio-cases-report} presents a gallery of city reports that are taken as test cases for the Urban Building pilot, as well as an example of a city report section showing the occlusion factor and heat flow plot.
-\begin{figure}[htbp]
-  \centering
-  \subfloat[Gallery of test case cities reports\label{fig:city-gallery}]{%
-    \includegraphics[width=0.45\textwidth]{img-compressed-city-gallery.png}
-  }
-  \hfill
-  \subfloat[Section of a city report\label{fig:city-report-section}]{%
-    \includegraphics[width=0.45\textwidth]{img-compressed-city-report-section.png}
-  }
-  \caption{Screenshots of the \url{https://cases.ktirio.fr} reporting website.}
-  \label{fig:ktirio-cases-report}
-\end{figure}
 
@@
 \subsubsection{Conclusion on mesh construction}
-
 Our strategy aims to improve the efficiency and scalability of the mesh generation process and enhance the fidelity and accuracy of the urban models used in simulations.
@@
 We now turn to describing the physical modeling of city energy simulation.
-
 To do this, we built on two main tools: Feel++ and Modelica.
-
-\subsubsection{Heat transfer model in buildings}
-\label{sec:heat-transfer-in-buildings}
-
-The physical model of city buildings is based on a multizone model.
-One zone is allocated per building floor. 
-The energy balance for each zone is calculated by taking into account energy exchanges with adjacent zones and the environment.
-
-The energy balance is written according to the first law of thermodynamics: in an isolated system, the sum of all forms of energy is constant.
-
-\begin{equation}
-    C \frac{dT}{dt} = \phi_{\mathrm{HVAC}} + \phi_{\mathrm{gain}} - \phi_{\mathrm{losses}}
-\end{equation}
-where
-\begin{inparaenum}[\it (i)]
-    \item $C \dfrac{dT}{dt}$ represents the thermal inertia of the construction, quantifying how the temperature of the zone changes over time due to its thermal mass. Specifically,
-    $C$ is a measure of how much heat a material can store and release, combining the heat capacity of the construction (how much energy is required to change the temperature) with the rate of temperature change and
-    $\dfrac{dT}{dt}$ is the rate of change of temperature with respect to time.
-A higher thermal inertia means the construction will have a slower rate of temperature change in response to energy inputs and losses, effectively buffering temperature fluctuations;
-    \item $\phi_{\mathrm{HVAC}}$ represents the energy input from the Heating, Ventilation, and Air Conditioning (HVAC) systems.
-It includes energy added to the zone to maintain desired temperature levels;
-    \item $\phi_{\mathrm{gain}}$, referred to as free energy gain, includes solar gains (heat from sunlight) and internal gains (heat generated by occupants and equipment);
-    \item $\phi_{\mathrm{losses}}$ represents the energy lost through walls, roofs, floors, and air exchanges with the environment.
-\end{inparaenum}
-
-\paragraph{HVAC heat flow} In the version of the model at the time of writing, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.
-
-\paragraph{Heat gain} Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.
-
-\paragraph{Internal heat gain} The internal heat gain captures the heat produced by occupants inside the building. 
-It is modeled as a function of metabolic rate $\mathrm{Met}$ and the number of inhabitants, $d_i$, which varies over time $t$:
-\begin{equation}
-  \phi_{\mathrm{int}} = \mathrm{Met} \cdot d_i(t)
-\end{equation}
-
-\paragraph{Solar heat gain} The total solar heat gain includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient:
-\begin{equation}
-  \phi_{\mathrm{solar}} = \alpha \cdot S \cdot \left( E_{\mathrm{dir}} + E_{\mathrm{diff}} + E_{\mathrm{ref}} \right) \cdot S_C
-\end{equation}
-Direct solar radiation is the component of solar radiation adjusted for the angle of incidence of the sunlight:
-\begin{equation}
-  E_{\mathrm{dir}} = F_{\mathrm{dir}} \cdot \cos(I)
-\end{equation}
-Here, $F_{\mathrm{dir}}$ is the direct solar radiation, which is a function of the horizontal solar radiation measured by a weather station:
-\begin{equation}
-  F_{\mathrm{dir}} = \dfrac{F_{\mathrm{dir,Hz}}}{\sin(H_s)}
-\end{equation}
-The term $\cos(I)$ calculates the cosine of the angle of incidence of sunlight, incorporating the sun's altitude and azimuth angles as well as the building's tilt angle:
-\begin{equation}
-  \cos(I) = \cos(H_s) \cdot \sin(\beta) \cdot \cos(A_{zs} - A_z) + \sin(H_s) \cdot \cos(\beta)
-\end{equation}
-Diffuse solar radiation includes contributions from the sky dome and is adjusted for the building's tilt:
-\begin{equation}
-  E_{\mathrm{diff}} = F_{\mathrm{dif,Hz}} \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right)
-\end{equation}
-Reflected solar radiation is calculated using the total horizontal radiation and the environment's albedo:
-\begin{equation}
-  E_{\mathrm{ref}} = \left[ F_{\mathrm{dir,Hz}} + F_{\mathrm{dif,Hz}} \right] \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right) \cdot \text{albedo}
-\end{equation}
-
-\paragraph{Conduction losses} Energy loss through walls is computed by summing the losses across all wall segments.
-It depends on the heat transfer coefficient, the wall area, and the temperature difference between the indoor and outdoor environments.
-In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depend on specific information about the building's envelope, which we do not have:
-\begin{equation}
-  \phi_{\mathrm{wall}} = \sum_{j} U_j \cdot S_j \cdot \Delta T
-\end{equation}
-The convection losses are computed differently depending on the surface of the wall to which they are applied. On the interior surface, we apply a constant:
-\begin{equation}
-  \phi_{\mathrm{conv,int}} = \alpha_{\mathrm{conv}} \cdot \Delta T
-\end{equation}
-On the exterior surface, we use a forced convection model:
-\begin{equation}
-  \phi_{\mathrm{conv,ext}} = \left( 1.8 + 4.8 \cdot v_{\mathrm{air}} \right) \cdot \Delta T
-\end{equation}
-
-\paragraph{Radiation losses} Radiation losses describe the heat energy lost due to thermal radiation, impacting both energy efficiency and thermal comfort.
-We differentiate between the exterior of the wall that exchanges with the sky and the interior where the walls exchange with each other.
-namely, for the exterior radiation exchange:
-\begin{equation}
-  \phi_{\mathrm{net,sky}} = \varepsilon_i \cdot \sigma \cdot \left( T_i^4 - T_{\mathrm{sky}}^4 \right)
-\end{equation}
-and for the interior radiation exchange:
-\begin{equation}
-  J[i] = \varepsilon_i \cdot \sigma \cdot T_i^4 + \left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]
-\end{equation}
-where the radiative heat exchange $J[i]$ includes two terms:
-\begin{inparaenum}[\it (i)]
-    \item $\varepsilon_i \cdot \sigma \cdot T_i^4$, which calculates the heat radiated by surface $i$ where $\varepsilon_i$ measures how effectively the surface emits radiation and $T_i^4$ reflects that radiative heat loss increases rapidly with temperature; and
-    \item $\left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$, which accounts for the heat absorbed from other surfaces $j$ within the zone.
-The factor $\left( 1.0 - \varepsilon_i \right)$ adjusts for the fraction of incoming radiation not emitted by surface $i$.
-\end{inparaenum}
-The net radiation flow is given by:
-\begin{equation}
-  \phi_{\mathrm{net,int}}[i] = S \cdot \dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)
-\end{equation}
-Net radiation flow $Q_{\mathrm{flow}}[i]$ considers:
-\begin{inparaenum}[\it (i)]
-    \item $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)$, which calculates the net heat flow due to radiation for surface $i$, considering the difference between the heat emitted by the surface and the heat received from other surfaces.
-The ratio $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
-\end{inparaenum}
-
-\paragraph{Air change} This term represents the energy loss due to air exchange between the zone and the exterior:
-\begin{equation}
-  \phi_{\mathrm{air}} = 0.34 \cdot Q_v \cdot \Delta T
-\end{equation}
-
-The described thermal models are implemented using the Modelica language, which is an object-oriented, equation-based language well-suited for modeling complex physical systems. 
-These models are then transformed into Functional Mock-up Units (FMUs) compliant with the Functional Mock-up Interface (FMI) standard. 
-FMUs encapsulate the models and enable them to be shared and integrated across different simulation environments.
-
-\paragraph{Conclusion}
-
-By integrating these models within a high-performance computing framework, it is possible to simulate the thermal behavior of city-scale building clusters.
-This facilitates the assessment of energy consumption, thermal comfort, and the impact of various energy-saving strategies under different environmental conditions and operational scenarios.
 
@@
 This powerful toolchain is essential for KUB.
-
-\subsubsection{Modelica for Multizone Heat Transfer}
-
-The FMUs built from \cref{sec:heat-transfer-in-buildings} are loaded by the \texttt{Feel++} environment.
-
-Input data for the models are sourced from available building information, such as geometric dimensions, material properties, and occupancy schedules.
-When specific data are unavailable, default values are assigned based on the building's construction year, referencing standard building codes or typical practices from that period.
-This approach ensures that the models can be applied to a wide range of buildings, even when detailed information is limited.
 
@@
 
+\subsubsection{Input data}
+
+To run a KUB simulation, several input files need to be generated.
+We have several metadata files (in JSON format), mesh data files (in MSH format), and meteorological measurement files (in CSV format).
+\Cref{tab:input-data-size-comparison} lists these files with their corresponding sizes for New York City and a duration of one year for the simulation.
+In addition, we compared the size of the input data with the size of the zone.
+
+\begin{table}[h]
+\begin{center}
+  \begin{tabular}{lccc} 
+    \toprule
+    Files & $4 \times 4 \mathrm{km}^2$ & $10 \times 10 \mathrm{km}^2$ & $20 \times 20 \mathrm{km}^2$ \\ [0.5ex] 
+    geographicdata\_setup.json & 4.0 K  & 4.0 K & 4.0 K \\ 
+    gis.json & 23 M & 117M & 470 M \\
+    mesh\_lod0.msh & 17 M & 112M & 496 M \\
+    mesh\_lod1.msh & 44 M & 240M & 896 M \\
+    weather-data-0.hourly-variables.csv & 384 K  & 384 K  & 384 K  \\
+    weather-data.json & 4.0 K  & 4.0 K & 4.0 K  \\ [1ex] 
+    \bottomrule
+  \end{tabular}
+\end{center}
+\caption{Size comparison of input data using New York city.}
+\label{tab:input-data-size-comparison}
+\end{table}
+
 \section{CI/CD Framework for the Urban Building Pilot}
@@
 \end{itemize}
+
+The total elapsed time varies from 100 seconds to 1000 seconds in function of the number of Nodes.
+All machines tested have an elapsed time of the same magnitude order.
 
@@
 
-\textbf{Nomenclature}\\
-\begin{multicols}{2}
-$\alpha$ : Absorption of a material.\hfill[-]\\
-$\alpha_{conv}$=10 : Heat conductance of convection.\hfill[-]\\
-$\beta$ : Angle of inclination of the wall to the horizontal.\hfill[-]\\
-$\Delta T$ : Temperature difference.\hfill[K]\\
-$\epsilon$ : Emissivity of the surface.\hfill[-]\\
-$\phi_{air}$ : Air heat flow.\hfill[W]\\
-$\phi_{net}$ : Radiative heat flow.\hfill[W]\\
-$\phi_{solar}$ : Solar heat flow from short wavelength.\hfill[W]\\
-$\phi_{wall}$ : Heat flow through a wall.\hfill[W]\\
-$\sigma$ : Stefan-Boltzmann constant $5,67\cdot10^{-8}$.\hfill[W$\cdot m^{-2}\cdot K^{-4}$]\\
-$albedo$ : Reflective properties of the material.\hfill[-]\\
-$A_z$ : Azimuth of the surface.\hfill[-]\\
-$A_{zs}$ : Azimuth of the sun.\hfill[-]\\
-$C$ : Heat capacity of the zone.\hfill[W$\cdot K^{-1}$]\\
-$d_{inhabitant}(timetable)$ : Density of inhabitants as a function of the timetable set for the building type.\hfill[-]\\
-$E_{dir}$ : Direct solar heat flow.\hfill[W$\cdot m^{-2}$]\\
-$E_{diff}$ : Diffuse solar heat flow.\hfill[W$\cdot m^{-2}$]\\
-$E_{ref}$ : Reflected solar heat flow.\hfill[W$\cdot m^{-2}$]\\
-$F_{dir}$ : Direct solar radiation.\hfill[W$\cdot m^{-2}$]\\
-$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data.\hfill[W$\cdot m^{-2}$]\\
-$F_{ij}$ : View factor between $surface_{(i)}$ and $surface_{(j)}$.\hfill[-]\\
-$H_s$ : Angular height of the sun.\hfill[-]\\
-$J$ : Radiosity of a surface.\hfill[W$\cdot m^{-2}$]\\
-$Met$ : Metabolic rate.\hfill[W]\\
-$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity.\hfill[W$\cdot K^{-1}$]\\
-$S$ : Surface area.\hfill[m$^2$]\\
-$S_C$ : Shading coefficient $\in$ [0,1].\hfill[-]\\
-$U_j$ : Conductance of a $wall_j$.\hfill[W$\cdot m^{-2}\cdot K^{-1}$]\\
-$V_{air}$ : Wind speed.\hfill[m$\cdot s^{-1}$]
-\end{multicols}
-
 \bibliographystyle{splncs04}

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex

--- 2024-11-01 article.hid2-ub-cicd.ppam24.tex
@@
 \usepackage[]{subcaption}
+\usepackage{booktabs}
 \usepackage{multicol}
@@
 This approach facilitates consistent, reproducible deployments, optimizing performance and resource utilization.
+
+\subsubsection{Input data}
+
+To run a KUB simulation, several input files need to be generated.
+We have several metadata files (in JSON format), mesh data files (in MSH format), and meteorological measurement files (in CSV format).
+\Cref{tab:input-data-size-comparison} lists these files with their corresponding sizes for New York City and a duration of one year for the simulation.
+In addition, we compared the size of the input data with the size of the zone.
+
+\begin{table}[h]
+\begin{center}
+  \begin{tabular}{lccc} 
+    \toprule
+    Files & $4 \times 4 \mathrm{km}^2$ & $10 \times 10 \mathrm{km}^2$ & $20 \times 20 \mathrm{km}^2$ \\ [0.5ex] 
+    geographicdata\_setup.json & 4.0 K  & 4.0 K & 4.0 K \\ 
+    gis.json & 23 M & 117M & 470 M \\
+    mesh\_lod0.msh & 17 M & 112M & 496 M \\
+    mesh\_lod1.msh & 44 M & 240M & 896 M \\
+    weather-data-0.hourly-variables.csv & 384 K  & 384 K  & 384 K  \\
+    weather-data.json & 4.0 K  & 4.0 K & 4.0 K  \\ [1ex] 
+    \bottomrule
+  \end{tabular}
+\end{center}
+\caption{Size comparison of input data using New York city.}
+\label{tab:input-data-size-comparison}
+\end{table}
 

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
improve input data
describe the size of the data to be handled. #13

@@
 \usepackage{booktabs}
+\usepackage{tabularx}
+\usepackage{siunitx}
+\usepackage{ragged2e}
 \usepackage{multicol}
@@
 
-\begin{table}[h]
-\begin{center}
-  \begin{tabular}{lccc} 
+\begin{table}[ht]
+  \centering
+  \caption{Size comparison of input data files for different geographical extents in New York City}
+  \label{tab:input-data-size-comparison}
+  \begin{tabularx}{.8\linewidth}{l *{3}{>{\RaggedLeft\arraybackslash}X}} 
       \toprule
-    Files & $4 \times 4 \mathrm{km}^2$ & $10 \times 10 \mathrm{km}^2$ & $20 \times 20 \mathrm{km}^2$ \\ [0.5ex] 
-    geographicdata\_setup.json & 4.0 K  & 4.0 K & 4.0 K \\ 
-    gis.json & 23 M & 117M & 470 M \\
-    mesh\_lod0.msh & 17 M & 112M & 496 M \\
-    mesh\_lod1.msh & 44 M & 240M & 896 M \\
-    weather-data-0.hourly-variables.csv & 384 K  & 384 K  & 384 K  \\
-    weather-data.json & 4.0 K  & 4.0 K & 4.0 K  \\ [1ex] 
+      \textbf{Files} & \textbf{\text{4 $\times$ 4} \si{\kilo\meter\squared}} & \textbf{\text{10 $\times$ 10} \si{\kilo\meter\squared}} & \textbf{\text{20 $\times$ 20} \si{\kilo\meter\squared}} \\
+      \midrule
+      \texttt{geographicdata\_setup.json} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} \\ 
+      \texttt{gis.json} & \SI{23}{\mega\byte} & \SI{117}{\mega\byte} & \SI{470}{\mega\byte} \\
+      \texttt{mesh\_lod0.msh} & \SI{17}{\mega\byte} & \SI{112}{\mega\byte} & \SI{496}{\mega\byte} \\
+      \texttt{mesh\_lod1.msh} & \SI{44}{\mega\byte} & \SI{240}{\mega\byte} & \SI{896}{\mega\byte} \\
+      \texttt{weather-data-0.hourly-variables.csv} & \SI{384}{\kilo\byte} & \SI{384}{\kilo\byte} & \SI{384}{\kilo\byte} \\
+      \texttt{weather-data.json} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} \\
       \bottomrule
-  \end{tabular}
-\end{center}
-\caption{Size comparison of input data using New York city.}
-\label{tab:input-data-size-comparison}
+  \end{tabularx}
   \end{table}
+
+In the future, the input data is expected to grow even larger with the addition of new details such as roofs, building characteristics, vegetation (e.g., trees), and terrain information.
+These enhancements will increase the complexity and accuracy of the simulation and the amount of data required to accurately model the urban environment.
 

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
use paralist and description

@@
 We describe our definition of Levels of Detail for Buildings such as:
-\begin{itemize}
-    \item \textbf{LOD-0:} The most straightforward form, representing buildings as oriented bounding boxes.
-This level is typically used for large-scale preliminary analyses and quick visual assessments.
-    \item \textbf{LOD-1:} Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
-    \item \textbf{LOD-2:} At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses.
+\begin{description}
+    \item[LOD-0] The most straightforward form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
+    \item[LOD-1] Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
+    \item[LOD-2] At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses.
 This includes detailed geometries for each building entity, often using complex surface models like B-REP, swept solids, or CSG techniques.
-\end{itemize}
+\end{description}
 
@@
 For this reason, we plan to apply a mesh adaptation technique to reduce mesh density where feasible, using the following processing:
-\begin{itemize}
+\begin{inparaenum}[\it (i)]
     \item Compute an arbitrary number of isolines for elevation,
     \item Build a new terrain mesh conform with the isolines nodes and adapt to terrain elevation gradient.
-\end{itemize}
+\end{inparaenum}
 %Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible.
@@
 The current strategy is as follows:
-
-\begin{itemize}
+\begin{inparaenum}[\it (i)]
 \item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD).
@@
 \item Creating a tree geometric model using an affine transformation of the reference tree model.
-\end{itemize}
+\end{inparaenum}
 
@@
 Different partitioning strategies are considered depending on the specific requirements of the simulation use cases :
-\begin{itemize}
-\item Case 0: simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient
-\item Case 1: buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings.
-The build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately.
-\item Case 2: for full interaction models, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead.
-\item Case 3: Regarding scenarios with extreme partitioning needs, Test Case 3 employs a multi-grid approach, defining coarse and fine meshes to manage computational resources efficiently.
-This multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
-\end{itemize}
+\begin{inparadesc}
+\item[Case 0] simulate simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient;
+\item[Case 1] simulate buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings; the build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately;
+\item[Case 2] simulate full interaction models where the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead;
+\item[Case 3] simulate scenarios with extreme partitioning and employ a multi-grid approach to  define coarse and fine meshes and manage computational resources efficiently; this multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
+\end{inparadesc}
 
@@
 We now turn to describing the physical modeling of city energy simulation.
-
 To do this, we built on two main tools: Feel++ and Modelica.
@@
 
-The physical model of city buildings is based on a multizone model.
+The physical model of city buildings is currently based on a multizone model.
 One zone is allocated per building floor. 
@@
 
-\paragraph{HVAC heat flow} In the version of the model at the time of writing, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.
-
-\paragraph{Heat gain} Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.
-
-\paragraph{Internal heat gain} The internal heat gain captures the heat produced by occupants inside the building. 
+\begin{description}
+  \item[HVAC heat flow] In the version of the model at the time of writing, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.
+  \item[Heat gain] Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.
+  \item[Internal heat gain] The internal heat gain captures the heat produced by occupants inside the building. 
   It is modeled as a function of metabolic rate $\mathrm{Met}$ and the number of inhabitants, $d_i$, which varies over time $t$:
@@
 
-\paragraph{Solar heat gain} The total solar heat gain includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient:
+\item[Solar heat gain] The total solar heat gain includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient:
 \begin{equation}
@@
 
-\paragraph{Conduction losses} Energy loss through walls is computed by summing the losses across all wall segments.
+\item[Conduction losses] Energy loss through walls is computed by summing the losses across all wall segments.
 It depends on the heat transfer coefficient, the wall area, and the temperature difference between the indoor and outdoor environments.
@@
 
-\paragraph{Radiation losses} Radiation losses describe the heat energy lost due to thermal radiation, impacting both energy efficiency and thermal comfort.
+\item[Radiation losses] Radiation losses describe the heat energy lost due to thermal radiation, impacting both energy efficiency and thermal comfort.
 We differentiate between the exterior of the wall that exchanges with the sky and the interior where the walls exchange with each other.
@@
 
-\paragraph{Air change} This term represents the energy loss due to air exchange between the zone and the exterior:
+\item[Air change] This term represents the energy loss due to air exchange between the zone and the exterior:
 \begin{equation}
@@
 \end{equation}
-
+\end{description}
 The described thermal models are implemented using the Modelica language, which is an object-oriented, equation-based language well-suited for modeling complex physical systems. 
@@
 Despite being purely geometric quantities, these calculations face significant challenges such as:
-\begin{itemize}
+\begin{inparaenum}[\it (i)]
     \item Efficient computation of integrals for view factors, especially when considering specular surfaces that require multiple ray bounces.
     \item Managing large-scale mesh computations and data storage, particularly when detailed urban environments are modeled.
-\end{itemize}
+\end{inparaenum}
 
@@
 We have several metadata files (in JSON format), mesh data files (in MSH format), and meteorological measurement files (in CSV format).
-\Cref{tab:input-data-size-comparison} lists these files with their corresponding sizes for New York City and a duration of one year for the simulation.
+\Cref{tab:input-data-size-comparison} lists these files with their corresponding sizes for New York City, see~\cref{fig:city-ny-largescale}, and a duration of one year for the simulation.
 In addition, we compared the size of the input data with the size of the zone.
@@
 The workflow leverages various main ingredients of GitHub Actions features.
-\begin{enumerate}
+\begin{inparaenum}[\it (1)]
     \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
@@
     \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
-\end{enumerate}
+\end{inparaenum}
 
@@
 \cref{fig:execution-breakdown} reports the portion of the total execution taken by:
-\begin{itemize}
-\item Pre-processing (Pre-proc): The time elapsed in initialization before entering the time loop of the simulation
-\item Simulation (Simulation): The cumulative time spent calculating the new solution at each time step
-\item Post-processing (Post-proc): The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
-\end{itemize}
+\begin{description}
+\item[Pre-processing (Pre-proc)] The time elapsed in initialization before entering the time loop of the simulation
+\item[Simulation (Simulation)] The cumulative time spent calculating the new solution at each time step
+\item[Post-processing (Post-proc)] The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
+\end{description}
 

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
add  information of required supercomputing environments #16

@@
 This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying and running these simulations at multiple scales. 
-Integrating EuroHPC JU infrastructures represents a significant advancement in making high-performance computing resources accessible for urban simulation studies.
+By leveraging containerized environments, we ensure that all dependencies are encapsulated, making the simulations portable and reproducible across different supercomputing resources. 
+These containers are deployed on EuroHPC JU infrastructures, which represents a significant advancement in making high-performance computing resources accessible for urban simulation studies. 
+The use of containers also simplifies software management and ensures consistency in the deployment process, enabling seamless scalability and reliability across EuroHPC systems.
 
@@
 The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment.
+A critical component for both Feel++ and KUB is the use of containerized environments, which encapsulate all necessary dependencies and configurations.
+
 %This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.
@@
 It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.
-
 \Cref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.
-
 \Cref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases.

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
remove real-time., real-time is not important here and might confuse the reader
explanation how important real-time processing is for this project is required #15

@@
 Thanks to synergies with other CoE HiDALGO2 pilots, the KUB project is set to integrate building simulations with Urban Air Pollution (UAP) pilot models to comprehensively assess the environmental impact of building stocks soon.
-This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.
+This integration improves the predictive accuracy of the simulations by incorporating data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.
 
@@
 The development and deployment of KUB builds on top of the Feel++ CI/CD framework.
-It employs GitHub Actions and Docker: GitHub Actions automate real-time workflows to compile, test, and validate code changes, facilitating rapid development cycles and ensuring code quality.
+It employs GitHub Actions and Docker: GitHub Actions automate workflows to compile, test, and validate code changes, facilitating rapid development cycles and ensuring code quality.
 On the other hand, Docker provides a containerized environment that encapsulates Feel++ and its dependencies, ensuring consistent operations across diverse computing environments.

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
add information of total elapsed time in Fig.11 #17
Explain what is presented by the grey scales Fig. 6 a,b: #8

@@
 
-In \cref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in \cref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in \cref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in \cref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in \cref{fig:view-factor}.
+In \cref{fig:solar-masks-vf}, we illustrate several aspects of solar masks: \textit{(i)} the solar masks of a building face oriented eastward, showing a discretization of the sun's position in \cref{fig:sm-building-east}; \textit{(ii)} the solar masks for an entire building, representing a detailed discretization of the sun's position throughout the day in \cref{fig:sm-whole-building}; \textit{(iii)} a visualization of the solar mask in the early morning for the city center of Strasbourg in \cref{fig:sm-strasbourg}; and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} used for the computation of view factors and solving heat transfer problems between three building blocks in 2D in \cref{fig:view-factor}.
+
+The grayscale values in each solar mask represent varying levels of solar obstruction for different azimuth and altitude angles.
+In these masks, the scale ranges from 0 to 1, where 0 (white) indicates no obstruction and full exposure to sunlight, and 1 (black) represents full obstruction, meaning no sunlight reaches that part of the building face for the given sun position.
+Intermediate shades of gray indicate partial obstruction, where a portion of sunlight is blocked by surrounding buildings or other urban features.
+The level of detail in the solar mask depends on the chosen level of discretization (LOD), as illustrated in \cref{fig:sm-building-east} and \cref{fig:sm-whole-building}.
+
+%In \cref{fig:sm-building-east} (LOD-0), we see a coarser discretization with larger, generalized angular segments, leading to more abrupt transitions between obstructed and non-obstructed areas.
+In contrast, \cref{fig:sm-whole-building} (LOD-1) provides a finer level of detail, capturing more granular variations in solar accessibility across different sun angles.
+These masks help quantify the solar exposure of building surfaces over time, which is critical for accurately modeling heat gains and understanding the thermal dynamics of urban environments.
 
@@
 
-The total elapsed time varies from 100 seconds to 1000 seconds in function of the number of Nodes.
+In~\cref{fig:combined-metrics}, the total elapsed time varies from 100 seconds to 1000 seconds in function of the number of nodes.
 All machines tested have an elapsed time of the same magnitude order.

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
Explain what is presented by the grey scales Fig. 6 a,b: #8
fill in a space between the captions to make it more readable in Fig 2c,d #10

@@
 \subfloat[LOD-0: a building is represented by its bounding box]{%
-  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod0.png}
+  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod0.png}
   \label{fig:building-lod0}
-}
+}\hspace{0.05\linewidth}
 %\hfill % This ensures that the images are placed side by side
 \subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
-  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod1.png}
+  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod1.png}
   \label{fig:building-lod1}
@@
 \subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
-  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2.png}
+  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod2.png}
   \label{fig:building-lod2}
-}
+}\hspace{0.05\linewidth}
 %\hfill
 \subfloat[LOD-2: A zoom on the LOD-2 building.]{%
-  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2-zoom.png}
+  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod2-zoom.png}
   \label{fig:building-lod2-zoom}
@@
 Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
-\begin{wrapfigure}{R}{0.6\textwidth}
+\begin{wrapfigure}{R}{0.7\textwidth}
 \centering
 \subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
-  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod0-parts.png}
-}
+  \includegraphics[width=0.46\linewidth]{img-compressed-city-strasbourg-lod0-parts.png}
+}\hspace{0.02\linewidth}
 %\hfill % Ensures that the images are placed side by side
 \subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
-  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod1-parts.png}
+  \includegraphics[width=0.46\linewidth]{img-compressed-city-strasbourg-lod1-parts.png}
 }

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
summarize the most computing intensive algorithms with their parallelization strategy. #18

@@
 \item[Pre-processing (Pre-proc)] The time elapsed in initialization before entering the time loop of the simulation
-\item[Simulation (Simulation)] The cumulative time spent calculating the new solution at each time step
+\item[Simulation (Simulation)] The cumulative time spent calculating the new solution at each time step of the simulation described in \cref{sec:heat-transfer-in-buildings}.
 \item[Post-processing (Post-proc)] The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
@@
 
-Pre-processing does not scale.
-However, it occupies only a small part of the total execution, and thus it is not performance-critical.
-On the other hand, as more nodes are employed and the time spent in the actual simulation is decreased, the post-processing stage dominates the execution.
-It becomes the main bottleneck, causing the previously observed performance degradation.
-This behavior is caused by the multiple files being written in parallel on the shared file system.
-More specifically, most of the writing time is spent in opening and closing files in parallel.
-We are investigating potential solutions, such as asynchronous writes, data caching, etc.
-Finally, as the project progresses, we expect the urban building models used in the simulation to become more complex, leading to an increase in the time occupied by the simulation part and, hence, to a reduction of the impact of post-processing on the total execution time of the pilot.
+Pre-processing does not scale efficiently, but it occupies only a small portion of the total execution time and is therefore not performance-critical.
+As more nodes are employed and the actual simulation time decreases, the post-processing stage becomes the dominant component of execution, posing a potential bottleneck and causing the previously observed performance degradation.
+This behavior is primarily due to multiple files being written in parallel to the shared file system, with a significant portion of time spent opening and closing files simultaneously.
+
+However, our end-user approach focuses not on the complete solution fields, unlike this benchmark, but rather on outputs of interest and automatically generated analysis reports, which occupy only a small fraction of the typical post-processing time.
+By targeting specific metrics and reports, we minimize the post-processing overhead and reduce data transfer and storage demands (see \cref{sec:final-analysis} for more information).
+
+We are nevertheless actively exploring potential solutions to further streamline the processing of solution fields, such as asynchronous writes, data caching, and other strategies to mitigate the impact of file operations.
+As the project progresses, we anticipate that the urban building models used in the simulation will grow in complexity, leading to increased time spent in the simulation itself (\cref{sec:heat-transfer-in-buildings}) and subsequently reducing the relative impact of post-processing on the overall execution time of the pilot.
 

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex

@@
 The CoE HiDALGO2 supports this initiative by developing high-performance computing solutions, specifically through the Urban Building pilot application, which utilizes advanced CI/CD methodologies to streamline simulation and deployment across various computational platforms, such as the EuroHPC JU supercomputers.
-The present work provides an overview of the Ktirio Urban Building framework (KUB), starting with an overview of the workflow and a description of some of the main ingredients of the software stack and discusses some current results performed on EuroHPC JU supercomputers using an innovative CI/CD pipeline.
+The present work provides an overview of the Ktirio Urban Building framework (KUB), starting with its workflow and a description of some of the main ingredients of the software stack, it then discusses some results performed on EuroHPC JU supercomputers using an innovative CI/
 
@@
 
-This paper is organized as follows: \cref{sec:kub-workflow} discusses KUB's current workflow, \cref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, \cref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.
+This paper is organized as follows: 
+\begin{inparaenum}[\it (i)]
+    \item \cref{sec:kub-workflow} presents the KUB workflow, detailing the data handling and simulation processes, and the final analysis and urban scale energy evaluation;
+    \item \cref{sec:urban-building} provides an overview of the geometrical and physical modeling components of the urban building application;
+    \item \cref{sec:cicd-framework} delves into the CI/CD processes tailored for EuroHPC environments;
+    \item \cref{sec:conclusion} concludes the paper.
 
+\end{inparaenum}
 %Feel++\cite{christophe_prudhomme_feelppfeelpp_2024}
@@
 \end{figure}
-
-The described streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting our application's broader objectives of improving urban living conditions and environmental impact.
 
@@
 \begin{inparadesc}
-\item[Case 0] simulate simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient;
-\item[Case 1] simulate buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings; the build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately;
-\item[Case 2] simulate full interaction models where the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead;
-\item[Case 3] simulate scenarios with extreme partitioning and employ a multi-grid approach to  define coarse and fine meshes and manage computational resources efficiently; this multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
+\item[Case 0] simulates simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient;
+\item[Case 1] simulates buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings; the build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately;
+\item[Case 2] simulates full interaction models where the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead;
+\item[Case 3] simulates scenarios with extreme partitioning and employ a multi-grid approach to  define coarse and fine meshes and manage computational resources efficiently; this multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
 \end{inparadesc}
@@
 \section{Conclusion}
+\label{sec:conclusion}
 

### 2024-11-06 article.hid2-ub-cicd.ppam24.tex
Updates from Overleaf

--- 2024-11-01 article.hid2-ub-cicd.ppam24.tex
@@
 \usepackage[]{subcaption}
-\usepackage{booktabs}
-\usepackage{tabularx}
-\usepackage{siunitx}
-\usepackage{ragged2e}
-\usepackage{multicol}
+
 \usepackage{url}
@@
 This environment enhances our ability to develop and test simulations rapidly and provides a robust platform for deploying and running these simulations at multiple scales.
-By leveraging containerized environments, we ensure that all dependencies are encapsulated, making the simulations portable and reproducible across different supercomputing resources. 
-These containers are deployed on EuroHPC JU infrastructures, which represents a significant advancement in making high-performance computing resources accessible for urban simulation studies. 
-The use of containers also simplifies software management and ensures consistency in the deployment process, enabling seamless scalability and reliability across EuroHPC systems.
+Integrating EuroHPC JU infrastructures represents a significant advancement in making high-performance computing resources accessible for urban simulation studies.
 
 Thanks to synergies with other CoE HiDALGO2 pilots, the KUB project is set to integrate building simulations with Urban Air Pollution (UAP) pilot models to comprehensively assess the environmental impact of building stocks soon.
-This integration improves the predictive accuracy of the simulations by incorporating data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.
+This integration improves the predictive accuracy of the simulations by incorporating real-time data such as wind speed and solar radiation, enhancing the models' responsiveness and forecasts to environmental conditions.
 
@@
 
-In addition to these exports, the simulator condenses, aggregates and saves relevant quantities on the fly to avoid having to manipulate large data volumes after the simulation.
-These metrics concern weather information, energy consumption and comfort assessment, and are exported in JSON format.
-The produced files are uploaded to a data management platform via the CI/CD pipeline (see \cref{fig:kub-devops}), who is then in charge of notifying a different workflow in order to render insightful figures that showcase the simulation results, as detailed in \cref{sec:cicd-framework}.
-
-Insights are presented in the form of a comprehensive report and are automatically deployed on a website built using the \textit{Antora} framework.
-End users are finally able to explore the simulation outputs in a detailed but malleable manner, for both the city and the building scales.
-
-\Cref{fig:ktirio-cases-report} presents a gallery of city reports that are taken as test cases for the Urban Building pilot, as well as an example of a city report section showing the occlusion factor and heat flow plot.
-\begin{figure}[htbp]
-  \centering
-  \subfloat[Gallery of test case cities reports\label{fig:city-gallery}]{%
-    \includegraphics[width=0.45\textwidth]{img-compressed-city-gallery.png}
-  }
-  \hfill
-  \subfloat[Section of a city report\label{fig:city-report-section}]{%
-    \includegraphics[width=0.45\textwidth]{img-compressed-city-report-section.png}
-  }
-  \caption{Screenshots of the \url{https://cases.ktirio.fr} reporting website.}
-  \label{fig:ktirio-cases-report}
-\end{figure}
-
 The described streamlined workflow is critical for accurately simulating and understanding urban sustainability challenges, supporting our application's broader objectives of improving urban living conditions and environmental impact.
@@
 We describe our definition of Levels of Detail for Buildings such as:
-\begin{description}
-    \item[LOD-0] The most straightforward form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
-    \item[LOD-1] Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
-    \item[LOD-2] At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses.
+\begin{itemize}
+    \item \textbf{LOD-0:} The most straightforward form, representing buildings as oriented bounding boxes.
+This level is typically used for large-scale preliminary analyses and quick visual assessments.
+    \item \textbf{LOD-1:} Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
+    \item \textbf{LOD-2:} At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses.
 This includes detailed geometries for each building entity, often using complex surface models like B-REP, swept solids, or CSG techniques.
-\end{description}
+\end{itemize}
 
@@
 \subfloat[LOD-0: a building is represented by its bounding box]{%
-  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod0.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod0.png}
   \label{fig:building-lod0}
-}\hspace{0.05\linewidth}
+}
 %\hfill % This ensures that the images are placed side by side
 \subfloat[LOD-1: a building is represented by its ground footprint elevated to its height]{%
-  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod1.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod1.png}
   \label{fig:building-lod1}
@@
 \subfloat[LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.]{%
-  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod2.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2.png}
   \label{fig:building-lod2}
-}\hspace{0.05\linewidth}
+}
 %\hfill
 \subfloat[LOD-2: A zoom on the LOD-2 building.]{%
-  \includegraphics[width=0.45\linewidth]{img-compressed-buildings-lod2-zoom.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-buildings-lod2-zoom.png}
   \label{fig:building-lod2-zoom}
@@
 For this reason, we plan to apply a mesh adaptation technique to reduce mesh density where feasible, using the following processing:
-\begin{inparaenum}[\it (i)]
+\begin{itemize}
     \item Compute an arbitrary number of isolines for elevation,
     \item Build a new terrain mesh conform with the isolines nodes and adapt to terrain elevation gradient.
-\end{inparaenum}
+\end{itemize}
 %Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible.
@@
 The current strategy is as follows:
-\begin{inparaenum}[\it (i)]
+\begin{itemize}
 \item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD).
@@
 \item Creating a tree geometric model using an affine transformation of the reference tree model.
-\end{inparaenum}
+\end{itemize}
 
 \subsubsection{Integration of all urban geometric components}
-
 This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation).
 Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh.
-\Cref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
+The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling).
 \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).
@@
 The current strategy for mesh generation employs multi-threading (MT) to handle various stages of the mesh construction process.
-Initially, the tiles used are determined based on the specified location, a task performed sequentially.
+Initially, the used tiles are determined based on the specified location, a task performed sequentially.
 Following this, GIS data, including buildings and elevation information, is downloaded in parallel.
@@
 Different partitioning strategies are considered depending on the specific requirements of the simulation use cases :
-\begin{inparadesc}
-\item[Case 0] simulate simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient;
-\item[Case 1] simulate buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings; the build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately;
-\item[Case 2] simulate full interaction models where the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead;
-\item[Case 3] simulate scenarios with extreme partitioning and employ a multi-grid approach to  define coarse and fine meshes and manage computational resources efficiently; this multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
-\end{inparadesc}
+\begin{itemize}
+\item Case 0: simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient
+\item Case 1: buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings.
+The build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately.
+\item  Case 2: for full interaction models, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead.
+\item Case 3: Regarding scenarios with extreme partitioning needs, Test Case 3 employs a multi-grid approach, defining coarse and fine meshes to manage computational resources efficiently.
+This multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
+\end{itemize}
 
@@
 Moreover, these partitioning strategies are costly, so we have planned to use other third-party tools, such as Zoltan2~\cite{the_zoltan2_team_zoltan2_nodate}, to improve efficiency.
-\begin{wrapfigure}{R}{0.7\textwidth}
+\begin{wrapfigure}{R}{0.6\textwidth}
 \centering
 \subfloat[Partitioning Case 0\label{fig:city-strasbourg-lod0-parts}]{%
-  \includegraphics[width=0.46\linewidth]{img-compressed-city-strasbourg-lod0-parts.png}
-}\hspace{0.02\linewidth}
+  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod0-parts.png}
+}
 %\hfill % Ensures that the images are placed side by side
 \subfloat[Partitioning Case 1\label{fig:city-strasbourg-lod1-parts}]{%
-  \includegraphics[width=0.46\linewidth]{img-compressed-city-strasbourg-lod1-parts.png}
+  \includegraphics[width=0.48\linewidth]{img-compressed-city-strasbourg-lod1-parts.png}
 }
@@
 To do this, we built on two main tools: Feel++ and Modelica.
-
-\subsubsection{Heat transfer model in buildings}
-\label{sec:heat-transfer-in-buildings}
-
-The physical model of city buildings is currently based on a multizone model.
-One zone is allocated per building floor. 
-The energy balance for each zone is calculated by taking into account energy exchanges with adjacent zones and the environment.
-
-The energy balance is written according to the first law of thermodynamics: in an isolated system, the sum of all forms of energy is constant.
-
-\begin{equation}
-    C \frac{dT}{dt} = \phi_{\mathrm{HVAC}} + \phi_{\mathrm{gain}} - \phi_{\mathrm{losses}}
-\end{equation}
-where
-\begin{inparaenum}[\it (i)]
-    \item $C \dfrac{dT}{dt}$ represents the thermal inertia of the construction, quantifying how the temperature of the zone changes over time due to its thermal mass. Specifically,
-    $C$ is a measure of how much heat a material can store and release, combining the heat capacity of the construction (how much energy is required to change the temperature) with the rate of temperature change and
-    $\dfrac{dT}{dt}$ is the rate of change of temperature with respect to time.
-A higher thermal inertia means the construction will have a slower rate of temperature change in response to energy inputs and losses, effectively buffering temperature fluctuations;
-    \item $\phi_{\mathrm{HVAC}}$ represents the energy input from the Heating, Ventilation, and Air Conditioning (HVAC) systems.
-It includes energy added to the zone to maintain desired temperature levels;
-    \item $\phi_{\mathrm{gain}}$, referred to as free energy gain, includes solar gains (heat from sunlight) and internal gains (heat generated by occupants and equipment);
-    \item $\phi_{\mathrm{losses}}$ represents the energy lost through walls, roofs, floors, and air exchanges with the environment.
-\end{inparaenum}
-
-\begin{description}
-  \item[HVAC heat flow] In the version of the model at the time of writing, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.
-  \item[Heat gain] Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.
-  \item[Internal heat gain] The internal heat gain captures the heat produced by occupants inside the building. 
-  It is modeled as a function of metabolic rate $\mathrm{Met}$ and the number of inhabitants, $d_i$, which varies over time $t$:
-  \begin{equation}
-    \phi_{\mathrm{int}} = \mathrm{Met} \cdot d_i(t)
-  \end{equation}
-
-\item[Solar heat gain] The total solar heat gain includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient:
-\begin{equation}
-  \phi_{\mathrm{solar}} = \alpha \cdot S \cdot \left( E_{\mathrm{dir}} + E_{\mathrm{diff}} + E_{\mathrm{ref}} \right) \cdot S_C
-\end{equation}
-Direct solar radiation is the component of solar radiation adjusted for the angle of incidence of the sunlight:
-\begin{equation}
-  E_{\mathrm{dir}} = F_{\mathrm{dir}} \cdot \cos(I)
-\end{equation}
-Here, $F_{\mathrm{dir}}$ is the direct solar radiation, which is a function of the horizontal solar radiation measured by a weather station:
-\begin{equation}
-  F_{\mathrm{dir}} = \dfrac{F_{\mathrm{dir,Hz}}}{\sin(H_s)}
-\end{equation}
-The term $\cos(I)$ calculates the cosine of the angle of incidence of sunlight, incorporating the sun's altitude and azimuth angles as well as the building's tilt angle:
-\begin{equation}
-  \cos(I) = \cos(H_s) \cdot \sin(\beta) \cdot \cos(A_{zs} - A_z) + \sin(H_s) \cdot \cos(\beta)
-\end{equation}
-Diffuse solar radiation includes contributions from the sky dome and is adjusted for the building's tilt:
-\begin{equation}
-  E_{\mathrm{diff}} = F_{\mathrm{dif,Hz}} \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right)
-\end{equation}
-Reflected solar radiation is calculated using the total horizontal radiation and the environment's albedo:
-\begin{equation}
-  E_{\mathrm{ref}} = \left[ F_{\mathrm{dir,Hz}} + F_{\mathrm{dif,Hz}} \right] \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right) \cdot \text{albedo}
-\end{equation}
-
-\item[Conduction losses] Energy loss through walls is computed by summing the losses across all wall segments.
-It depends on the heat transfer coefficient, the wall area, and the temperature difference between the indoor and outdoor environments.
-In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depend on specific information about the building's envelope, which we do not have:
-\begin{equation}
-  \phi_{\mathrm{wall}} = \sum_{j} U_j \cdot S_j \cdot \Delta T
-\end{equation}
-The convection losses are computed differently depending on the surface of the wall to which they are applied. On the interior surface, we apply a constant:
-\begin{equation}
-  \phi_{\mathrm{conv,int}} = \alpha_{\mathrm{conv}} \cdot \Delta T
-\end{equation}
-On the exterior surface, we use a forced convection model:
-\begin{equation}
-  \phi_{\mathrm{conv,ext}} = \left( 1.8 + 4.8 \cdot v_{\mathrm{air}} \right) \cdot \Delta T
-\end{equation}
-
-\item[Radiation losses] Radiation losses describe the heat energy lost due to thermal radiation, impacting both energy efficiency and thermal comfort.
-We differentiate between the exterior of the wall that exchanges with the sky and the interior where the walls exchange with each other.
-namely, for the exterior radiation exchange:
-\begin{equation}
-  \phi_{\mathrm{net,sky}} = \varepsilon_i \cdot \sigma \cdot \left( T_i^4 - T_{\mathrm{sky}}^4 \right)
-\end{equation}
-and for the interior radiation exchange:
-\begin{equation}
-  J[i] = \varepsilon_i \cdot \sigma \cdot T_i^4 + \left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]
-\end{equation}
-where the radiative heat exchange $J[i]$ includes two terms:
-\begin{inparaenum}[\it (i)]
-    \item $\varepsilon_i \cdot \sigma \cdot T_i^4$, which calculates the heat radiated by surface $i$ where $\varepsilon_i$ measures how effectively the surface emits radiation and $T_i^4$ reflects that radiative heat loss increases rapidly with temperature; and
-    \item $\left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$, which accounts for the heat absorbed from other surfaces $j$ within the zone.
-The factor $\left( 1.0 - \varepsilon_i \right)$ adjusts for the fraction of incoming radiation not emitted by surface $i$.
-\end{inparaenum}
-The net radiation flow is given by:
-\begin{equation}
-  \phi_{\mathrm{net,int}}[i] = S \cdot \dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)
-\end{equation}
-Net radiation flow $Q_{\mathrm{flow}}[i]$ considers:
-\begin{inparaenum}[\it (i)]
-    \item $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)$, which calculates the net heat flow due to radiation for surface $i$, considering the difference between the heat emitted by the surface and the heat received from other surfaces.
-The ratio $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
-\end{inparaenum}
-
-\item[Air change] This term represents the energy loss due to air exchange between the zone and the exterior:
-\begin{equation}
-  \phi_{\mathrm{air}} = 0.34 \cdot Q_v \cdot \Delta T
-\end{equation}
-\end{description}
-The described thermal models are implemented using the Modelica language, which is an object-oriented, equation-based language well-suited for modeling complex physical systems. 
-These models are then transformed into Functional Mock-up Units (FMUs) compliant with the Functional Mock-up Interface (FMI) standard. 
-FMUs encapsulate the models and enable them to be shared and integrated across different simulation environments.
-
-\paragraph{Conclusion} By integrating these models within a high-performance computing framework, it is possible to simulate the thermal behavior of city-scale building clusters.
-This facilitates the assessment of energy consumption, thermal comfort, and the impact of various energy-saving strategies under different environmental conditions and operational scenarios.
 
@@
 Despite being purely geometric quantities, these calculations face significant challenges such as:
-\begin{inparaenum}[\it (i)]
+\begin{itemize}
     \item Efficient computation of integrals for view factors, especially when considering specular surfaces that require multiple ray bounces.
     \item Managing large-scale mesh computations and data storage, particularly when detailed urban environments are modeled.
-\end{inparaenum}
+\end{itemize}
 
@@
 
-In \cref{fig:solar-masks-vf}, we illustrate several aspects of solar masks: \textit{(i)} the solar masks of a building face oriented eastward, showing a discretization of the sun's position in \cref{fig:sm-building-east}; \textit{(ii)} the solar masks for an entire building, representing a detailed discretization of the sun's position throughout the day in \cref{fig:sm-whole-building}; \textit{(iii)} a visualization of the solar mask in the early morning for the city center of Strasbourg in \cref{fig:sm-strasbourg}; and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} used for the computation of view factors and solving heat transfer problems between three building blocks in 2D in \cref{fig:view-factor}.
-
-The grayscale values in each solar mask represent varying levels of solar obstruction for different azimuth and altitude angles.
-In these masks, the scale ranges from 0 to 1, where 0 (white) indicates no obstruction and full exposure to sunlight, and 1 (black) represents full obstruction, meaning no sunlight reaches that part of the building face for the given sun position.
-Intermediate shades of gray indicate partial obstruction, where a portion of sunlight is blocked by surrounding buildings or other urban features.
-The level of detail in the solar mask depends on the chosen level of discretization (LOD), as illustrated in \cref{fig:sm-building-east} and \cref{fig:sm-whole-building}.
-
-%In \cref{fig:sm-building-east} (LOD-0), we see a coarser discretization with larger, generalized angular segments, leading to more abrupt transitions between obstructed and non-obstructed areas.
-In contrast, \cref{fig:sm-whole-building} (LOD-1) provides a finer level of detail, capturing more granular variations in solar accessibility across different sun angles.
-These masks help quantify the solar exposure of building surfaces over time, which is critical for accurately modeling heat gains and understanding the thermal dynamics of urban environments.
+In the figure~\ref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in the panel~\ref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in the panel~\ref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in panel~\ref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in panel~\ref{fig:view-factor}.
 
@@
 This method leverages the generation of Functional Mock-up Units (FMUs), which integrate seamlessly into larger C/C++ applications, providing a robust framework for handling complex simulations involving multiple interacting systems.
-The FMUs built from \cref{sec:heat-transfer-in-buildings} are loaded by the \texttt{Feel++} environment.
-Input data for the models are sourced from available building information, such as geometric dimensions and material properties.
-When specific data are unavailable, default values are assigned based on the building's construction year, referencing standard building codes or typical practices from that period.
-Occupancy schedules are given as input to the models using reglementary occupancy.
-We are currently working on parametrized occupancy profiles, which are adjusted based on the building's use type (e.g., residential, office, commercial).
-This approach ensures that the models can be applied to a wide range of buildings, even when detailed information is limited.
 
@@
 
-\subsubsection{Input data}
-
-To run a KUB simulation, several input files need to be generated.
-We have several metadata files (in JSON format), mesh data files (in MSH format), and meteorological measurement files (in CSV format).
-\Cref{tab:input-data-size-comparison} lists these files with their corresponding sizes for New York City, see~\cref{fig:city-ny-largescale}, and a duration of one year for the simulation.
-In addition, we compared the size of the input data with the size of the zone.
-
-\begin{table}[ht]
-  \centering
-  \caption{Size comparison of input data files for different geographical extents in New York City}
-  \label{tab:input-data-size-comparison}
-  \begin{tabularx}{.8\linewidth}{l *{3}{>{\RaggedLeft\arraybackslash}X}} 
-      \toprule
-      \textbf{Files} & \textbf{\text{4 $\times$ 4} \si{\kilo\meter\squared}} & \textbf{\text{10 $\times$ 10} \si{\kilo\meter\squared}} & \textbf{\text{20 $\times$ 20} \si{\kilo\meter\squared}} \\
-      \midrule
-      \texttt{geographicdata\_setup.json} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} \\ 
-      \texttt{gis.json} & \SI{23}{\mega\byte} & \SI{117}{\mega\byte} & \SI{470}{\mega\byte} \\
-      \texttt{mesh\_lod0.msh} & \SI{17}{\mega\byte} & \SI{112}{\mega\byte} & \SI{496}{\mega\byte} \\
-      \texttt{mesh\_lod1.msh} & \SI{44}{\mega\byte} & \SI{240}{\mega\byte} & \SI{896}{\mega\byte} \\
-      \texttt{weather-data-0.hourly-variables.csv} & \SI{384}{\kilo\byte} & \SI{384}{\kilo\byte} & \SI{384}{\kilo\byte} \\
-      \texttt{weather-data.json} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} & \SI{4.0}{\kilo\byte} \\
-      \bottomrule
-  \end{tabularx}
-  \end{table}
-
-In the future, the input data is expected to grow even larger with the addition of new details such as roofs, building characteristics, vegetation (e.g., trees), and terrain information.
-These enhancements will increase the complexity and accuracy of the simulation and the amount of data required to accurately model the urban environment.
-
 \section{CI/CD Framework for the Urban Building Pilot}
@@
 The Urban Building pilot utilizes the Feel++ framework, supported by a robust CI/CD framework that facilitates efficient development and deployment.
-A critical component for both Feel++ and KUB is the use of containerized environments, which encapsulate all necessary dependencies and configurations.
-
 %This section outlines how GitHub Actions and Docker streamline the entire process, ensuring the robustness and productivity of the software development lifecycle.
@@
 The development and deployment of KUB builds on top of the Feel++ CI/CD framework.
-It employs GitHub Actions and Docker: GitHub Actions automate workflows to compile, test, and validate code changes, facilitating rapid development cycles and ensuring code quality.
+It employs GitHub Actions and Docker: GitHub Actions automate real-time workflows to compile, test, and validate code changes, facilitating rapid development cycles and ensuring code quality.
 On the other hand, Docker provides a containerized environment that encapsulates Feel++ and its dependencies, ensuring consistent operations across diverse computing environments.
@@
 \end{figure}
-The CI/CD workflow, see \cref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. 
+The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework.
 The workflow leverages various main ingredients of GitHub Actions features.
-\begin{inparaenum}[\it (1)]
+\begin{enumerate}
     \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
@@
     \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
-\end{inparaenum}
+\end{enumerate}
 
@@
 It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.
-\Cref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.
-\Cref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases.
+
+Figure~\ref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.
+
+Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases.
 It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.
@@
 
-To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in \cref{fig:execution-breakdown}. 
-\cref{fig:execution-breakdown} reports the portion of the total execution taken by:
-\begin{description}
-\item[Pre-processing (Pre-proc)] The time elapsed in initialization before entering the time loop of the simulation
-\item[Simulation (Simulation)] The cumulative time spent calculating the new solution at each time step
-\item[Post-processing (Post-proc)] The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
-\end{description}
-
-In~\cref{fig:combined-metrics}, the total elapsed time varies from 100 seconds to 1000 seconds in function of the number of nodes.
-All machines tested have an elapsed time of the same magnitude order.
+To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in Figure \ref{fig:execution-breakdown}.
+This figure reports the portion of the total execution taken by:
+\begin{itemize}
+\item Pre-processing (Pre-proc): The time elapsed in initialization before entering the time loop of the simulation
+\item Simulation (Simulation): The cumulative time spent calculating the new solution at each time step
+\item Post-processing (Post-proc): The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
+\end{itemize}
 
@@
 
-\section*{Nomenclature}
-
-\begin{multicols}{2}
-$\alpha$ : Absorption of a material.\hfill[-]\\
-$\alpha_{conv}$=10 : Heat conductance of convection.\hfill[-]\\
-$\beta$ : Angle of inclination of the wall to the horizontal.\hfill[-]\\
-$\Delta T$ : Temperature difference.\hfill[K]\\
-$\epsilon$ : Emissivity of the surface.\hfill[-]\\
-$\phi_{air}$ : Air heat flow.\hfill[W]\\
-$\phi_{net}$ : Radiative heat flow.\hfill[W]\\
-$\phi_{solar}$ : Solar heat flow from short wavelength.\hfill[W]\\
-$\phi_{wall}$ : Heat flow through a wall.\hfill[W]\\
-$\sigma$ : Stefan-Boltzmann constant $5,67\cdot10^{-8}$.\hfill[W$\cdot m^{-2}\cdot K^{-4}$]\\
-$albedo$ : Reflective properties of the material.\hfill[-]\\
-$A_z$ : Azimuth of the surface.\hfill[-]\\
-$A_{zs}$ : Azimuth of the sun.\hfill[-]\\
-$C$ : Heat capacity of the zone.\hfill[W$\cdot K^{-1}$]\\
-$d_{inhabitant}(timetable)$ : Density of inhabitants as a function of the timetable set for the building type.\hfill[-]\\
-$E_{dir}$ : Direct solar heat flow.\hfill[W$\cdot m^{-2}$]\\
-$E_{diff}$ : Diffuse solar heat flow.\hfill[W$\cdot m^{-2}$]\\
-$E_{ref}$ : Reflected solar heat flow.\hfill[W$\cdot m^{-2}$]\\
-$F_{dir}$ : Direct solar radiation.\hfill[W$\cdot m^{-2}$]\\
-$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data.\hfill[W$\cdot m^{-2}$]\\
-$F_{ij}$ : View factor between $surface_{(i)}$ and $surface_{(j)}$.\hfill[-]\\
-$H_s$ : Angular height of the sun.\hfill[-]\\
-$J$ : Radiosity of a surface.\hfill[W$\cdot m^{-2}$]\\
-$Met$ : Metabolic rate.\hfill[W]\\
-$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity.\hfill[W$\cdot K^{-1}$]\\
-$S$ : Surface area.\hfill[m$^2$]\\
-$S_C$ : Shading coefficient $\in$ [0,1].\hfill[-]\\
-$U_j$ : Conductance of a $wall_j$.\hfill[W$\cdot m^{-2}\cdot K^{-1}$]\\
-$V_{air}$ : Wind speed.\hfill[m$\cdot s^{-1}$]
-\end{multicols}
-
 \bibliographystyle{splncs04}
